### 2015-04-21 paper/paper.tex
Updating

%
% RELATED NOTES (Richard)
%    PersonalJBArchive
%    PSnucleosynthesis/Branch-GalaxyAssemblyAndZDistribution 
%        */bhmetals   : paper.tex, paper-shorter.tex
\documentclass[nofootinbib,twocolumn,prd]{emulateapj}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{color}
\usepackage{ifpdf}
%\usepackage{eps2pdf}

\newcommand\mc{{\cal M}_c{}}
\newcommand\editremark[1]{{\color{red}#1}}
\newcommand\unit[1]{\text{#1}}
\newcommand\abbrvPSgrb{PSG}
\newcommand\abbrvPSellipticals{PSE}
\newcommand\abbrvKBLowZa{BD2010}
\newcommand\ForInternalReference[1]{}
\newcommand\modelDefault{A}
\newcommand\modelNiino{A'}
\newcommand\modelKW{D}
\newcommand\modelMannucci{D'}
\newcommand\modelKB{B}
\newcommand\modelPanter{C}
%\newcommand\aap{A\&A}
%\newcommand\apss{APSS}
%\newcommand\aaps{AAPS}
%% \newcommand\apjs{ApJ S}
%% \newcommand\aj{AJ}
%% \newcommand\apjl{ApJL}
%% \newcommand\mnras{MNRAS}
%% \newcommand\pasp{PASP}
%% \newcommand\pasj{PASJ}
%% \newcommand\araa{ARAA}
%% \newcommand\physrep{Phys. Rep.}

\begin{document}
\title{Details matter: Similar-looking host galaxies can produce different merging compact binary populations} 
\author{R.\ O'Shaughnessy}
\affiliation{Center for Computational Relativity and Gravitation, Rochester Institute of Technology, Rochester, NY 14623, USA}
\email{oshaughn@mail.rit.edu}
\author{ J. Bellovary}
\affiliation{Department of Physics and Astronomy, Vanderbilt University, Nashville TN 37235}
\email{jillian.bellovary@vanderbilt.edu}
\begin{abstract}
% POINT:
% - existence proof by example .. not an attempt to solve the general problem we raise
Galaxy formation
simulations can reproduce present-day galaxies with notably different assembly and star formation histories.  
Recent binary evolution simulations suggest the compact binary merger rate depends
sensitively on the progentior's metallicity, to the extent that rare low-metallicity star formation during galaxy
assembly can produce more detected compact binaries than typical star formation.   
Using detailed simulations of galaxy and chemical evolution, we demonstrate by example that galaxies with similar present-day appearance can host distinctly different
compact binary populations.
We discuss the implications for transient multimessenger astronomy with compact binary sources. 
%% Present and future observations of  merging compact binaries can provide valuable constraints on their birthrate
%%  and formation scenarios.  However, recent binary evolution simulations suggest the compact binary merger rate depends
%% sensitively on the progentior's metallicity, to the extent that rare low-metallicity star formation during galaxy
%% assembly can produce more detected compact binaries than typical star formation.    Additionally, galaxy formation
%% simulations can reproduce present-day galaxies with notably different assembly and star formation histories, with
%% corresponding different present-day merger rates.  
%% % POINT 0: Gasoline + popsyn: real work was done
%% Using existing simulations of the assembly,  chemical evolution, and compact-object formation rate of a single halo
%% Milky Way-like galaxy with Gasoline, we construct present-day compact binary merger rates using a simple semianalytic
%% compact binary formation model ($dP/dt \propto Z^\alpha/t $) motivated by detailed calculations in the literature. 
%% % POINT 1: Observations
%% %   - difficult to reconstruct f
%% %   - local particle far away
%% As expected, we show the present-day galactic state can be only weakly correlated with the dominant compact binary
%% fomation rate: the galaxy could form in several ways, including epochs of low-metallicity star formation through major
%% mergers; and present-day mergers rarely occur near gas with their progenitor metallicity, even when not kicked.  
%% %  - but the galaxy 
%% By contrast,  detailed studies which reconstruct the galaxy's star formation history and metallicity evolution could,
%% when stacked, pinpoint the dominant formation process \editremark{need more than handwaving}.
% POINT 2: Revised merger rates
%% Averaging over the cosmological star formation history and galaxy mass-metallicity relation, we demonstrate low
%% metallicity star formation can produce much of the detected population of short GRBs and nearly all gravitatational-wave
%% sources. 
%% % POINT 3: Challenge for observations
%% Therefore,  though a potentially large fraction of binaries formed from low-metallicity gas,  their birth metallicity
%% cannot be identified directly, even with spatially resolved observations. 
%% %
%% We discuss the extent to which observations can distinguish between different scenarios for  low-metallicity compact
%% binary formation.
%
%\textbf{say something using GRBs in paragraph; perhaps mention relative bias in $p(M_g|GRB)$ relative to prior?}
%% \textbf{say something about different SFR histories making present galaxies -- can do more if we can distinguish history
%% of the galaxy}

\end{abstract}

\maketitle

\section{Introduction}

\section{Cosmological simulations produce two distinct Milky-Way-like galaxies}

\subsection{Simulating galaxy evolution}
To thoroughly examine the significance of low metallicity star
formation, we have run a cosmological smoothed particle hydrodynamics
(SPH) $N$-body simulation of a Milky Way-like galaxy with GASOLINE
\citep{Stadel01,Wadsley04}.  This simulation allows us to analyze both
spatially and temporally resolved star formation, and determine not
only the metallicity history of compact object progenitors, but also
their dynamical evolution.  The simulation we report here, $h258$,
involves the formation of a Milky Way-like disk galaxy whose
progenitors undergo major mergers at $z = 2$ and $z = 0.8$.  This
simulation has been previously discussed by
\citet{Governato09,Bellovary10,Bellovary11,Brooks11}; however we have
re-run the simulation at a factor of two higher in spatial resolution
and additionally included new physics including a prescription for
cooling by molecular hydrogen (Christensen et al. in prep).

We selected our simulated region of interest from a 50 Mpc volume of
uniform resolution, and resampled the region of interest at very high
resolution using the volume renormalization technique \citep{Katz93}.
This technique allows us to follow the detailed physical processes
involved in galaxy evolution in our selected region while still
including large-scale torques from cosmic structure.  We use {\bf
WMAPX} cosmology \citep{WMAP} and model the ionizing UV background
with the prescription from \citet{Haardt96}.  Stars form
probabilistically from gas particles which meet density ($n_{min} =
10$ amu cm$^{-3}$) and temperature ($T_{max} = 10^4$ K) thresholds
{\bf (additional description needed for H2 SF prescription)}. If a gas
particle meets these criteria, it has a likelihood of forming a star
particle (representing a simple stellar population with a Kroupa IMF
\citep{Kroupa}) which is given by

\begin{equation}
p = \frac{m_{\rm gas}}{m_{\rm star}} (1 - e^{c^*\Delta t/t_{\rm form}})
\end{equation}

\noindent
where the star formation efficiency parameter $c^*$ is set to 0.1 such
that our galaxies match the observed Kennicutt-Schmidt law
\citep{Kennicutt89}; $m_{star}$ and $m_{gas}$ are the star and gas
particle masses;\footnote{In our high-resolution simulations \textbf{ROS-check!}, each gas particle starts with a mass
  $m_{gas,0}=26,676 M_\odot$, gaining mass from feedback and losing it to star formation.  Each star particle, when
  formed, has $1/3$ of the progenitor mass of the forming gas particle.  See \cite{2010ApJ...717..121C} for a discussion
of resolution issues in these SPH simulations.} $t_{form}$ is the dynamical time for the gas
particle; and $\Delta t$ is the time between star formation episodes,
which we set to 1 Myr.  We model supernova feedback using the
blastwave formalism described in \citet{McKee77} and implemented in
our simulations as in \citet{Stinson06}.  Each supernova releases
$E_{SN} = 10^{51}$ erg into the surrounding gas with a radius
determined by the blastwave equations.  These particles are not
allowed to cool for the duration of the blastwave, mimicking the
snowplow phase of a supernova explosion.  Previous works have found
that this set of parameters results in realistic galaxies which obey a
number of observed relations such as the mass-metallicity relation
\citep{Brooks07}, the Tully-Fisher relation \citep{Governato09}, and
the size-luminosity relation \citep{Brooks11}, as well as reproduce
the detailed characteristics of bulgeless dwarf galaxies
\citep{Governato10} and the Milky Way \citep{Guedes11}.

Also included in our simulations is a scheme for turbulent metal
diffusion \citep{Shen10}.  Metals are created in supernova explosions
and deposited directly to the gas within the blast radius.  Stellar
masses are converted to ages as described by \citet{Raiteri96}, and
stars more massive than 8 M$_\odot$ are able to undergo a Type II
supernova.  We follow metal enrichment from both Type II and Type 1a
supernova, with metal yields derived from \citet{Weaver93} and
\citet{Thielemann86} respectively.  From this point onwards metals
diffuse through the surrounding gas, according to 
\begin{equation}
\frac{dZ}{dt}|_{diff} = \nabla (D \nabla {Z}) \\
\end{equation}
%
where the diffusion paremeter $D$ is given by
%
\begin{equation}
D = C_{diff} |S_{ij}| h
\end{equation}
%
and $h$ is the SPH smoothing length, $S_{ij}$ is the trace-free shear
tensor, and $C_{diff}$ is a dimensionless constant which we set to
{\bf something.  Reasons for setting it are good, let's have some.
Sijing finds that C = 0.05 makes for a good comparison to clusters, we
tend to use something more conservative}.

We identify individual galaxies using the halo finder $AHF$
\citep{Gill04,Knollmann09}, which identifies halos based on an
overdensity criterion for a flat universe \citep{Gross97}.  For this
work, we are focusing on the primary (i.e. most massive) galaxy at any
given redshift, which serves as the progenitor to our $z = 0$ Milky
Way-like galaxy.

\subsection{Two Milky-Way-like galaxies with }

\begin{figure}
\caption{\textbf{Star formation and metallicity versus time}: \editremark{writeme}
}
\end{figure}

\section{Results}

\section{Conclusions}

\appendix

\section{Outline }
\begin{verbatim}

Intro
  -Important (edo/Brian)
  - More important soon (LIGO; IFU's give detail)
    because these galaxies are local and spatially resolved
    at 400 Mpc distance
  - The question: can we learn about things from detailed host galaxy 
    observations, and if so what?
    Obviously yes (cf. SN Ia, short GRB, etc)
  - Specific questions of interest, particularly for BH-NS origin for short GRBs:
    is there dependence of the event rate and BH mass on the source metallicity

  - Not clear because of kicks, mixing
  - Goal of paper: address this challenge via simulations

Methods
  - JB: specifically target two 'identical' MW galaxies (and their subhalo population)
  - Postproces JB: rhodot; Z of star forming gas
  - Model:
      - predict present-day number (and mass distribution) by formula

Results:
  - Different histories which look the same now can produce different answers
  - 
\end{verbatim}
%1 Kilo Parsec/(400 Mega Parsec)
%Convert[%, Milli ArcSecond] // N
\bibliography{bhmetals}
\end{document}

### 2015-04-21 paper/paper.tex

@@
 \newcommand\modelPanter{C}
+\newcommand\cqg{CQG}
 %\newcommand\aap{A\&A}
@@
 \section{Introduction}
+% POINT: LIGO soon will detect compact binary mergers....
+%     ... and possibly EM counter part too
+%     ... which will enable new physics
+In the next few years, ground-based gravitational wave detectors like LIGO 
+and Virgo  should detect the gravitational
+wave signal from merging compact binaries, including  binary  neutron stars and black hole-neutron star binaries; see,
+e.g., \cite{LIGO-Inspiral-Rates} and references therein.
+In addition to the strong gravitational wave signal, mergers of neutron stars is expected to  frequently be accompanied by detectable
+electromagnetic radiation  via a number of  mechanisms, including a strong but tightly beamed
+ultrarelativistic jet \citep{2013PhRvL.111r1101C} and weakly-beamed but more isotropic thermal radiation from an expanding hot shell
+\citep{short-grb-GWCoincidenceEM-MetzgerBerger2011}.  
+% People we can't afford the space to cite, alas:
+%    - 2015arXiv150101986H
+In addition to providing a wealth of information about the merger event itself, a multimessenger detection will pin down
+the sky position and therefore approximate birthplace of each merging binary.    
+As with supernovae and  GRBs, these host galaxy associations   are expected to tightly constrain models for compact binary
+formation; see, for comparison,  \citet{2011MNRAS.412.1508M}, \citet{long-grb-GuettaPiran2007},
+\citet{2014ARAA..52...43B}, and references therein. %2010ApJ...722.1879M,2010MNRAS.407.1314M}.     
+%
+These associations will be particularly valuable because of the relative proximity of LIGO sources, expected to short GRB host
+
+% POOINT: Huge detail possible
+The host galaxies of distant short GRBs have already been extensively investigated, with the associations being used to
+draw conclusions about their progentitors  \cite{2014ARAA..52...43B}.   Of necessity, these analyses  relied largely on
+bulk correlations, often stacked to increase significance across multiple sources \editremark{clean up/don't piss off
+  Edo}.  
+Unlike GRBs, detected gravitational wave sources will be limited by the range of LIGO to the local universe; for
+example,  binary neutron star sources should be closer than $400\unit{Mpc}$.  Due to their proximity, each host galaxy
+can be explored at great depth and detail via  position-resolved spectroscopy, enabling detailed position-resolved star-formation
+and chemical evolution histories \editremark{citation: need better ones} \cite{2009MNRAS.396..462K,2014MNRAS.444..336C}.
+% POINT: But is it useful?
+In this work, we demonstrate by concrete example that detailed analysis of individual galaxies can be essential to
+investigate key physical questions about the origin of compact binary mergers.
+
+%% %   - Delay  time only: 
+%% For example, the lag between transients' redshift distribution and the past star formation rate has shown long GRBs are
+%% associated with short-lived progenitors (see, e.g., \cite{long-grb-GuettaPiran2007} \cite{grb-long-Virgili2011-TryingEverything} and
+%% references therein) and that SNIa merge long after their formation
+%% \citep{sn1a-DelayTimeDistribution-Cosmological-Graur2011}. \editremark{other cites}
+%% % * \cite{YoungLongGRBHostPredictions2007,FryerGRBProgenitorConstraints2007} : Long bursts.
+%% By contrast, short GRBs noticably lag cosmological star formation  \editremark{Berger; }\cite{2007ApJ...665.1220Z,Nakar}
 
@@
 
+\section{Implications for transient multimessenger astronomy}
+
+* ascertain properties of hosts critical..
+
+% POINT: Observations provide sample of extragalactic  binaries at merger, and  host galaxies.  Possible to mine large archive of events
+% to deduce correlations
+
+On the one hand,  relatively few formation scenarios will correctly reproduce the observed mass and spin distributions
+\citep{2004MNRAS.352.1372B,2003ApJ...589L..37B,gwastro-Ilya-ConfProc-NRDA-2010}.  
+% POINT: Value of associations
+%% Green's function connecting the merger
+%% rate $dN/dt$ to the star formation rate host galaxy star formation history and metallicity,
+%% both the delay time distribution and correlation any preference for different metallicities can be determined
+On the other hand, each host galaxy associates a merger to a unique star formation history and metallicity distribution.
+With many events, these associations can potentially determine the ``response function'' for compact binaries: how often star forming gas of a given metallicity evolves into
+merging compact binaries;  see, e.g., studies of
+
+%
+Highly atypical formation scenarios seemingly should produce events in or near atypical hosts.  
+% POINT: Introduce *idea* of comparison: refs for mass-metallicity relation
+For example, in the local universe galaxies lie along mass-metallicity  (\cite{2004ApJ...613..898T}; see also
+\cite{sfr-ZEvolution-ByGalaxy-Panter2008})
+or mass-metallicity-star formation rate  correlations (e.g., \cite{2010MNRAS.408.2115M}).
+% POINT: Evolution tricky
+[The change in these correlations with redshift is still being investigated; see, e.g., \editremark{citation: Panter;
+    Mannucci; }, \cite{2011ApJ...739....1L} and references therein.]
+% POINT: previous studies
+Based on these correlations, both short  and long GRBs seem to arise from
+relatively typical hosts at their redshift; see, e.g., \cite{grb-short-Hosts-Berger2008} and \cite{grb-long-HostMetallicityVsTrend-Mannucci2010}.
+
+%  - Host associations: lots of information
+Host galaxy associations provide rich information about a transient's present and past environment.
+%
+For example, in several cases the metallicity of gas neighboring a long GRB (\citet{ 2008AJ....135.1136M}; \citet{2010AJ....140.1557L}
+\editremark{links}), short GRB (\editremark{XXX}), or SN has been directly measured.
+%
+The precise host offset can be compared to the distribution of light and star formation  \citep{2010ApJ...708....9F}.
+%
+Finally,  on a host-by-host basis, the delay time between birth and merger has been constrained for long GRBs (\editremark{XXX}), short GRBs \citep{2010ApJ...725.1202L}, and
+  SN Ia \citep{2011MNRAS.412.1508M}.
+%
+
+Biases towards low-metallicity star formation have been extensively studied in the context of long GRBs and their host galaxies.
+%
+For example, \cite{2009ApJ...702..377K} demonstrated that a sufficiently strong bias towards low-metallicity star formation would predict
+most  events in the local universe occur low-mass and dwarf galaxies.
+%<
+For less extreme metallicity biases, subsequent calculations by  \citet{2011MNRAS.417..567N} demonstrated that the
+metallicity distribution within galaxies will usually lead to events in a wide range of host galaxies in the local universe.
+
+\subsection{Local metallicity measurements?}
+To this point, we have emphasized \emph{global} measurements of the galactic star formation history.  With the advent of
+IFUs and position-resolved spectroscopy, observers can now probe the star formation history and metallicity of
+individual gas packets at different points in a galaxy.  
+%
+These highly-detailed probes will be essential tools to develop a comprehensive model of the galaxy's merger and
+chemical evolution history.  That said, the metallicity of stars and gas adjacent to a specific merger event provides
+few direct, unambiguous clues to a compact binary merger's progenitors.  
+On the one hand, compact binaries are kicked by supernovae, moving substantially away from their birth position
+%  2014arXiv1407.3796S : implications for nucleosynthesis
+\cite{2013ApJ...776...18F,2014ARAA..52...43B}. 
+On the other hand, particularly during the epoch of galaxy formation, galaxies are well-mixed: stars and adjacent gas generally do not have
+similar chemical composition.  
+% POINT: Host tracer gas --we are optimistically assuming the metallicity 
+%  can be measured.  A seperate question is whether you can measure Z in the local environment at all.
+These mixing effects have been previously recognized as an obstacle to interpreting transient event spectra.  For
+example,   \cite{2010MNRAS.402.1523P} previously demonstrated that absorbing gas neighboring transient events (there, long GRBs)
+would generally have high metallicity, even for low-metallicity progenitors.   
+%
+\citet{2010MNRAS.402.1523P} have previously used hydrodynamical simulations to demonstrate that observed ambient
+metallicities (there, using damped Lyman $\alpha$ absorbers in the host) do not tightly constrain the metallicity
+distribution of the progenitor; see, e.g., their Fig 3.
+%
+
 \section{Conclusions}
+
+% POINT: Future directions
 

### 2015-04-21 paper/paper.tex
Changes

@@
 e.g., \cite{LIGO-Inspiral-Rates} and references therein.
-In addition to the strong gravitational wave signal, mergers of neutron stars is expected to  frequently be accompanied by detectable
+In addition to the strong gravitational wave signal, mergers of neutron stars are expected to  frequently be accompanied by detectable
 electromagnetic radiation  via a number of  mechanisms, including a strong but tightly beamed
-ultrarelativistic jet \citep{2013PhRvL.111r1101C} and weakly-beamed but more isotropic thermal radiation from an expanding hot shell
-\citep{short-grb-GWCoincidenceEM-MetzgerBerger2011}.  
+ultrarelativistic jet and weakly-beamed but more isotropic thermal radiation from an expanding hot shell
+\citep[see,e.g.,][and references therein]{2013PhRvL.111r1101C,short-grb-GWCoincidenceEM-MetzgerBerger2011}.  
 % People we can't afford the space to cite, alas:
-%    - 2015arXiv150101986H
+%    - 2015arXiv150101986H   -
+%    - 2013MNRAS.430.2121P - Rosswog recent
+%    - Shibata group/Koutarou
 In addition to providing a wealth of information about the merger event itself, a multimessenger detection will pin down
@@
 %
-These associations will be particularly valuable because of the relative proximity of LIGO sources, expected to short GRB host
 
-% POOINT: Huge detail possible
+% POINT: Huge detail possible
 The host galaxies of distant short GRBs have already been extensively investigated, with the associations being used to
-draw conclusions about their progentitors  \cite{2014ARAA..52...43B}.   Of necessity, these analyses  relied largely on
-bulk correlations, often stacked to increase significance across multiple sources \editremark{clean up/don't piss off
-  Edo}.  
+draw preliminary conclusions about their progentitors  \cite{2014ARAA..52...43B}.   
+%Of necessity, these analyses  on bulk correlations, often stacked to increase significance across multiple sources
+%\editremark{clean up/don't piss off   Edo}.  
 Unlike GRBs, detected gravitational wave sources will be limited by the range of LIGO to the local universe; for
@@
 can be explored at great depth and detail via  position-resolved spectroscopy, enabling detailed position-resolved star-formation
-and chemical evolution histories \editremark{citation: need better ones} \cite{2009MNRAS.396..462K,2014MNRAS.444..336C}.
+and chemical evolution histories \editremark{citation: need better ones} \citep[see,e.g.][]{2009MNRAS.396..462K,2014MNRAS.444..336C}.
 % POINT: But is it useful?
@@
 investigate key physical questions about the origin of compact binary mergers.
+
+This paper is organized as follows. 
+In \S \ref{sec:sims}, we describe detailed hydrodynamical simulations of  two galaxies.  Though these two
+galaxies are at  present similar to the Milky Way, we
+show that their star formation and chemical evolution history have subtle but important differences due to their
+distinctive merger histories.   To demonstrate
+these differences have a significant practical impact,  in \S \ref{sec:model}, we introduce a simple,
+metallicity-dependent  phenomenological model to calculate the present-day rate and mass distribution of compact binary
+mergers from  a galaxy's known history.  
+In \S \ref{sec:results} we show that while these two galaxy formation models should produce comparable detectable binary neutron star
+populations, these two scenarios could produce dramatically different populations of electromagnetically detectable
+merging black hole-neutron star binaries. 
+%
 
@@
 \section{Cosmological simulations produce two distinct Milky-Way-like galaxies}
+\label{sec:sims}
 
@@
 only the metallicity history of compact object progenitors, but also
-their dynamical evolution.  The simulation we report here, $h258$,
+their dynamical evolution.  One simulation we report here, $h258$,
 involves the formation of a Milky Way-like disk galaxy whose
@@
 
-\subsection{Two Milky-Way-like galaxies with }
+\subsection{Two Milky-Way-like galaxies with distinct histories }
+
+Figure \ref{fig:TwoGalaxies} shows the history of
 
 \begin{figure}
-\caption{\textbf{Star formation and metallicity versus time}: \editremark{writeme}
+\includegraphics[width=\columnwidth]{Figures/zvst}
+\caption{\label{fig:TwoGalaxies}\textbf{Star formation and metallicity versus time}:  \emph{Left panel}: Star formation history $\dot{M}_{*}$
+  versus time.  Red corresponds to galaxy A (``boring'') and blue to gaalxy B (``exciting'').  
+\emph{Right panel}: A plot of the  metallicity $Z$ of recently-formed stars versus time.  Solid red and black lines show
+the mean metallicity; dotted lines correspond to  90\% of newly-born stars have lower metallicity,   or 10\% of
+newly-born stars have greater metallicity.
 }
@@
 
+\section{Model for compact binary formation}
+\label{sec:model}
+
+Binary evolution calculations suggest the detection rate depends sensitively on the assumed metallicity, in conjuction
+with other parameters \citep[see,\,e.g.][and references
+  therein]{popsyn-LowMetallicityImpact-Chris2008,popsyn-LIGO-SFR-2008}.\editremark{New dominik et al}
+% POINT: 
+%   - final BH spin, mass can change number favored
+%   - of course
+The detected population of compact binary mergers can further favor low-metallicity environments, e.g. through the total
+mass of merging binaries.
+% POINT: Simple model to encompass all
+To explore plausible binary detection scenarios, we adopt a parameterized formalism for binary evolution and event detection, motivated by
+the detailed studies of  \abbrvPSgrb{} and \abbrvPSellipticals.  Specifically, we encapsulate all information about
+ binary evolution into two  parameterized response functions.  The funciton ${\cal G}(t| Z) =
+dN/dt dM_*$ describes how many mergers per unit initial mass occur after a time $t$ since a starburst,
+given ambient metallicity $Z$.  The function $p(m_1,m_2|Z)$ is a metallicity-dependent mass distribution for binaries
+formed in a metallicity $Z$.
+%
+Finally, we account for the substantially increased sensitivity of gravitational wave detectors to binaries of larger
+chirp mass $\mc=(m_1 m_2)^{3/5}/(m_1+m_2)^{1/5}$; see \abbrvPSellipticals.
+%
+In terms of this response function, we can therefore calculate the relative contribution to the LIGO  event rate $r_D$
+due to any individual galaxy via the following formula 
+\begin{widetext}
+\begin{subequations}
+\label{eq:RatePerGalaxy}
+\begin{eqnarray}
+r_D  &\equiv& \int^{0}_{-T_{univ}} dt' d\log Z  \, [\dot{M}_*(t') p(\log Z|t) ] \times \; {\cal G}(0-t' | Z)  p(\mc|Z) (\mc/1.2 M_\odot)^{15/6}
+%\\
+%% {\cal R}(z)&\equiv &  \int dx {\cal R} p(z)
+\end{eqnarray}
+\end{subequations}
+\end{widetext}
+In this expression, the galactic star formation rate
+$\dot{M}_*$ and star formation metallicity distribution $p(\log Z|t)$ are galaxy-dependent and drawn from our
+simulations.
+
+We parameterize the response function ${\cal G}(t|Z)$ with two factors: (a) an overall efficiency $\lambda$ for forming
+binaries;  and (b) a
+cumulative delay time distribution $P_t(<t|Z)$, describing the fraction of binaries born at $t=0$ that merge in less
+than time $t$ from a population of binaries $Z$:\footnote{For simplicity, we assume the mass and delay time
+  distributions are uncorrelated.  Figure A9 in \abbrvPSgrb{} shows this approximation, while not strictly true, is an
+  excellent approximation for merging BH-BH binaries at solar metallicity.  }
+\begin{eqnarray}
+G(t,x|Z) &=& \lambda(Z) p_x(x|Z) \frac{dP_t}{dt}(t) 
+\end{eqnarray}
+Previous studies suggest the number of merging compact binaries $\lambda \delta M_*$ produced by a starburst depends
+as a power law on metallicity:
+\begin{eqnarray}
+\label{eq:LambdaVersusZModel}
+\lambda(Z) &=& \lambda_o \text{max}[(Z/Z_\odot)^{-a}, F_{max}] 
+\end{eqnarray}
+with $a\in [0,3]$ and $F_{max}<10^3$
+%$\lambda_o F_{max} < 3\times 10^{-4}/M_\odot$
+ (see, e.g.\cite{popsyn-LIGO-SFR-2008}, \abbrvKBLowZa).
+In this paper we only investigate the dependence of rates with metallicity; we therefore  adopt 
+\[
+\lambda_0 = 10^{-3}/M_\odot
+\]
+as a typical value for neutron star compact binaries (see \abbrvPSgrb{}, \abbrvPSellipticals, and \abbrvKBLowZa).
+%
+Finally, for simplicity we adopt the universal delay time distribution
+%% Finally, we parameterize the delay time distribution by  either
+%% \begin{eqnarray}
+%% P_t(<t) &=& \begin{cases}
+%% 0 & t<10 \unit{Myr} \\
+%% (t/13\unit{Gyr})^{b}& t \in [10\unit{Myr},t_H]
+%% \end{cases} 
+%% \end{eqnarray}
+%% with $b> 0$ or as the special case
+\begin{eqnarray}
+\frac{dP_t(<t)}{dt} =  \begin{cases}
+0 & t<10 \unit{Myr} \\
+\frac{1}{t \ln (13 \unit{Gyr}/10\unit{Myr})} & t \in [10\unit{Myr},13\unit{Gyr}]
+\end{cases} 
+\end{eqnarray}
+\abbrvPSgrb{} and \abbrvPSellipticals{} show this distribution is reasonable approximations to compact binary delay
+time distributions.\footnote{Simulations suggest the delay time distribution varies from model to model and with mass.
+  These variations have less impact on our results than the evolving metallicity distribution of star forming gas.}
+%
+For suitable choices of parameter, our phenomenological response function is qualitatively consistent with the results of detailed simulations of binary
+evolution  \citep{2010ApJ...715L.138B,popsyn-LowMetallicityImpact2c-StarTrackRevised-2014,popsyn-LowMetallicityImpact2b-StarTrackRevised-2013,popsyn-LowMetallicityImpact2-StarTrackRevised-2012}.
+
 \section{Results}
+\label{sec:results}
+
+\section{Conclusions}
+
+% POINT: Future directions
+
+\begin{acknowledgements}
+ROS acknowledges support from NSF award AST-1412449, via subcontract from the University of Wisconsin-Milwaukee.
+%
+JB acknolwedges support  from \editremark{writeme}
+\end{acknowledgements}
+
+\appendix
+
+\section{Outline }
+\begin{verbatim}
+
+Intro
+  -Important (edo/Brian)
+  - More important soon (LIGO; IFU's give detail)
+    because these galaxies are local and spatially resolved
+    at 400 Mpc distance
+  - The question: can we learn about things from detailed host galaxy 
+    observations, and if so what?
+    Obviously yes (cf. SN Ia, short GRB, etc)
+  - Specific questions of interest, particularly for BH-NS origin for short GRBs:
+    is there dependence of the event rate and BH mass on the source metallicity
+
+  - Not clear because of kicks, mixing
+  - Goal of paper: address this challenge via simulations
+
+Methods
+  - JB: specifically target two 'identical' MW galaxies (and their subhalo population)
+  - Postproces JB: rhodot; Z of star forming gas
+  - Model:
+      - predict present-day number (and mass distribution) by formula
+
+Results:
+  - Different histories which look the same now can produce different answers
+     - key issue: impact of past mergers
+  -
+
+Stuff to skip
+  - (spin-dependent) tidal disruption threshold: assume all BH-NS disrupt, for simplicity
+\end{verbatim}
+%1 Kilo Parsec/(400 Mega Parsec)
+%Convert[%, Milli ArcSecond] // N
+
+\section{Other discussion}
 
 \section{Implications for transient multimessenger astronomy}
-
-* ascertain properties of hosts critical..
 
@@
 
-\section{Conclusions}
-
-% POINT: Future directions
-
-\appendix
-
-\section{Outline }
-\begin{verbatim}
-
-Intro
-  -Important (edo/Brian)
-  - More important soon (LIGO; IFU's give detail)
-    because these galaxies are local and spatially resolved
-    at 400 Mpc distance
-  - The question: can we learn about things from detailed host galaxy 
-    observations, and if so what?
-    Obviously yes (cf. SN Ia, short GRB, etc)
-  - Specific questions of interest, particularly for BH-NS origin for short GRBs:
-    is there dependence of the event rate and BH mass on the source metallicity
-
-  - Not clear because of kicks, mixing
-  - Goal of paper: address this challenge via simulations
-
-Methods
-  - JB: specifically target two 'identical' MW galaxies (and their subhalo population)
-  - Postproces JB: rhodot; Z of star forming gas
-  - Model:
-      - predict present-day number (and mass distribution) by formula
-
-Results:
-  - Different histories which look the same now can produce different answers
-  - 
-\end{verbatim}
-%1 Kilo Parsec/(400 Mega Parsec)
-%Convert[%, Milli ArcSecond] // N
 \bibliography{bhmetals}

### 2015-04-21 python/sfr_to_rate_nobins.py
Updating

@@ -1,0 +1,48 @@
+#! /usr/bin/env python
+#  sfr_to_rate_nobins.py 
+#  GOAL
+#      Take SFR history and spit out an event rate, using different response functions
+#      --time-exponent 0   : use uniform in time, starting after 10 Myr and running to 
+#      --time-exponent 1   : use 1/t delay time, start (DEFAULT)
+#      --time-max    100    : time max in Gyr for response function (DEFAULT).  If time-exponent<1, time-max=10Gyr
+# 
+#      --starmetal-file
+#      --Z-exponent 0
+#
+#  USAGE
+#    python sfr_to_rate.py --starmetal-file ~/PersonalJBArchive/boring-galaxy/sfrhist_metalbin_boring.txt --plot
+#
+# PLOTS
+#    Third plot is money plot: shows you where the mergers are coming from, for different exponent choices.
+
+import numpy as np
+
+import bisect
+from scipy.interpolate import griddata
+
+import ParseStars
+
+import argparse
+parser = argparse.ArgumentParser()
+parser.add_argument("--starmetal-file", default=None)
+parser.add_argument("--time-exponent",default=1,type=float)
+parser.add_argument("--Z-exponent",default=0,type=float)
+opts = parser.parse_args()
+if not opts.starmetal_file:
+    print "  Please specify an SFR file "
+
+
+# SFR files:
+#    - not guaranteed to have same # per Z bin ! 
+dat = np.loadtxt(opts.starmetal_file,skiprows=1)
+lambda0 = 1e-3
+
+if opts.Z_exponent:
+    # print a specific value
+    weights = np.minimum(np.power((1e-8+dat[:,0])/0.02,-1.*opts.Z_exponent), 1e3*np.ones(len(dat))) *1./np.power(0.01+dat[:,2], opts.time_exponent)
+    print opts.starmetal_file, opts.Z_exponent,  len(dat)*ParseStars.jbStarMass/1e10, np.sum(weights)*lambda0*ParseStars.jbStarMass/1e10, np.sum(weights)/len(dat)
+else:
+    # Loop over all from 0 to 3 in steps of 0.1
+    for Zexp in np.linspace(0,3, 30):
+        weights = np.minimum(np.power((1e-8+dat[:,0])/0.02,-1.*Zexp), 1e3*np.ones(len(dat))) *1./np.power(0.01+dat[:,2], opts.time_exponent)
[…]

### 2015-04-21 paper/paper.tex
Draft minor changes on action items

@@
 \begin{eqnarray}
-r_D  &\equiv& \int^{0}_{-T_{univ}} dt' d\log Z  \, [\dot{M}_*(t') p(\log Z|t) ] \times \; {\cal G}(0-t' | Z)  p(\mc|Z) (\mc/1.2 M_\odot)^{15/6}
+r_D  &\equiv& \int^{0}_{-T_{univ}} dt' d\log Z  \, [\dot{M}_*(t') p(\log Z|t) ] \times \; {\cal G}(0-t' | Z)  
+ [\int d\mc p(\mc|Z) (\mc/1.2 M_\odot)^{15/6}]
 %\\
@@
 $\dot{M}_*$ and star formation metallicity distribution $p(\log Z|t)$ are galaxy-dependent and drawn from our
-simulations.
+simulations.   \editremark{rewrite this to be average chirp mass at a given metallicity}
 
@@
 
+\subsection{Tidal disruption and black hole mass versus metallicity}
+At merger, black holes may promptly engulf a companion neutron star \editremark{same papers as for Brandon:Foucart,
+  etc}.  Without  a tidal disruption event prior to merger, the prospects for associated electromagnetic counterparts
+are severely diminished.  
+To quantify this effect
+
+DISCUSSION: could we explain the redshift distribution of short GRBs this way?
+
 \section{Results}
 \label{sec:results}
+
+\begin{verbatim}
+ACTION ITEMS AND STATUS
+
+* Result script looks good (\texttt{sfr\_to\_rate.py}).  Follow instructions
+
+** May want more Z bins to make sure we resolve it. Our differences between predictions are not huge
+
+*** or rewrite script to use numpy on raw star data.  Use 'starmetal.dat': last colum is age.
+
+** Clear that low-Z matters a lot
+
+*
+
+* Do we get to different answers?  Are they different ENOUGH?
+
+** Overall event rate: different by 20\% between two types. Largely similar.
+   - plot versus z_exponent.  Is there a trend
+
+** mass-cut-dependent event rate -- will be more sensitive (e.g., if there
+  is a hard cutoff on some masses, as having no EM counterpart)
+\end{verbatim}
 

### 2015-04-22 paper/paper.tex
paper.tex: updating caption and action items

@@
 
-\begin{figure}
+\begin{figure*}
+\includegraphics[width=\columnwidth]{Figures/sfh}
 \includegraphics[width=\columnwidth]{Figures/zvst}
 \caption{\label{fig:TwoGalaxies}\textbf{Star formation and metallicity versus time}:  \emph{Left panel}: Star formation history $\dot{M}_{*}$
-  versus time.  Red corresponds to galaxy A (``boring'') and blue to gaalxy B (``exciting'').  
+  versus time.  Black corresponds to galaxy A (``boring'') and red to gaalxy B (``exciting'').  
 \emph{Right panel}: A plot of the  metallicity $Z$ of recently-formed stars versus time.  Solid red and black lines show
 the mean metallicity; dotted lines correspond to  90\% of newly-born stars have lower metallicity,   or 10\% of
-newly-born stars have greater metallicity.
+newly-born stars have greater metallicity.  When these two galaxies are $2-3\unit{Gyr}$ old, prior to the first major
+merger of  near the peak of their
+star-forming history, newly-born stars are created with significantlydifferent metallicity.  Additionally, prior to the
+second major merger of galaxy B at $\simeq 6\unit{Gyr}$, stars form in the ``exciting'' galaxy at a systematically lower
+metallicity than in the ``boring'' counterpart.
 }
-\end{figure}
+\end{figure*}
 
@@
 At merger, black holes may promptly engulf a companion neutron star \editremark{same papers as for Brandon:Foucart,
-  etc}.  Without  a tidal disruption event prior to merger, the prospects for associated electromagnetic counterparts
+  etc}, unless they have sufficiently small mass and sufficiently large spin.  Without  a tidal disruption event prior to merger, the prospects for associated electromagnetic counterparts
 are severely diminished.  
-To quantify this effect
+%
+The black hole mass and possibly spin in black hole-neutron star binaries can depend sensitively on binary formation
+channels.  Because of the extremely narrow range of masses that permit tidal disruption in BH-NS binaries, small changes
+in the mass distribution can produce significant changes in the electromagnetically detected population.
+%
+To quantify this effect, we adopt a simple formula for tidal disruption of neutron stars in BH-NS binaries and a simple
+phenomenological model for the metallicity-dependent mass distribution of BHs in BH-NS binaries
 
+\editremark{calibrate mass distribution to synthetic universe/Dominik - but also allow reversed trend}
 DISCUSSION: could we explain the redshift distribution of short GRBs this way?
@@
 
-** May want more Z bins to make sure we resolve it. Our differences between predictions are not huge
+** Modify script to include tidal disruption options for BHs
 
-*** or rewrite script to use numpy on raw star data.  Use 'starmetal.dat': last colum is age.
+** plot 'stanard' results for NS-NS
 
-** Clear that low-Z matters a lot
+** set scale to be physical units -- some ad-hoc factors used
 

### 2015-04-22 python/sfr_to_rate_nobins.py
python: updating bin-free script

@@ -10,7 +10,8 @@
 #      --Z-exponent 0
 #
 #  USAGE
-#    python sfr_to_rate.py --starmetal-file ~/PersonalJBArchive/boring-galaxy/sfrhist_metalbin_boring.txt --plot
+#    python sfr_to_rate_nobins.py --starmetal-file ~/PersonalJBArchive/boring-galaxy/z0.016.starmetal.dat --Z-exponent 2
+#    python sfr_to_rate_nobins.py --starmetal-file ~/PersonalJBArchive/boring-galaxy/z0.016.starmetal.dat
 #
 # PLOTS
 #    Third plot is money plot: shows you where the mergers are coming from, for different exponent choices.

### 2015-04-23 paper/paper.tex
wrote some galaxy descriptions.

--- 2015-04-21 paper/paper.tex
@@
 
-Figure \ref{fig:TwoGalaxies} shows the history of
+{\bf Richard go ahead and edit this however is needed.}  The evolution
+of a galaxy, in terms of its stellar mass and metallicity evolution,
+depends strongly on its interaction history.  Galaxies which look
+similar at the present day may have had drastically different
+histories, which may result in differences in compact object merger
+rates.  To investigate whether galaxy history affects the GRB event
+rate, we have chosen two simulations which are extremely similar at $z
+= 0$ but differ strongly in their merger histories.
+
+The simulation h277 (Boring Galaxy) is a Milky Way analog with a
+quiescent merger history.  It experiences its last major merger at $z
+= 3$, after which a small number of minor interactions permeate its
+life.  This simulation has been shown to emulate several Milky Way
+properties, including stellar dynamics
+\citep{Loebman12,Loebman14,Kassin14}, baryon fraction
+\citep{Munshi13}, halo properties \citep{Zolotov09,Zolotov10), and
+  disk properties \citep{Brooks11}.  It has a virial mass of $M_{vir}
+  = 6.79 \times 10^{11}$ \msun, stellar mass $M_* = 4.24 \times
+  10^{10}$ \msun, and circular velocity $v_{circ} = xx$ km s$^{-1}$.
+
+  The simulation h258 (Exciting Galaxy), on the other hand, has a much
+  more active merger history.  At $z = 1$ there is a 1:1 merger event;
+  a gas disk rapidly reforms following the collision (see
+  \citet{Governato09}), resulting in a massive disk galaxy at $z = 0$
+  which looks remarkably similar to the Milky Way and to the other
+  simulation, h277.  Prior to the $z = 1$ merger, each of the two
+  progenitor galaxies actually experiences its own additional major
+  merger events around $z = 2.5$ ({\bf check!}).  The combination of
+  the series of major mergers, plus a number of minor interactions and
+  flybys, gives a stark contrast to the relatively quiescent history
+  of h277.  At $z = 0$, h258 has a virial mass of $M_{vir} = 7.74
+  \times 10^{11}$ \msun, stellar mass $M_* = 4.46 \times 10^{10}$
+  \msun, and circular velocity $v_{circ} = xx$ km s$^{-1}$.
+
+  Due to the differences in merger histories, the metallicity
+  evolution of h258 and h277 also differ at early times.  Figure
+  \ref{fig:TwoGalaxies} shows the history of the mean metallicty of
+  recently formed stars vs time (thick solid lines), where we define
+  recent as within the past 50 Myr.  The shaded regions correspond to
+  one standard devation of the mean, while the thick dashed lines
+  represent the top and bottom 90\%.  We see that {\bf different things happen at different times.}
 

### 2015-05-26 paper/paper.tex
paper.tex: More editing

@@
 \newcommand\editremark[1]{{\color{red}#1}}
+\newcommand\msun{M_\odot}
 \newcommand\unit[1]{\text{#1}}
@@
 \citep{Loebman12,Loebman14,Kassin14}, baryon fraction
-\citep{Munshi13}, halo properties \citep{Zolotov09,Zolotov10), and
+\citep{Munshi13}, halo properties \citep{Zolotov09,Zolotov10}, and
   disk properties \citep{Brooks11}.  It has a virial mass of $M_{vir}
-  = 6.79 \times 10^{11}$ \msun, stellar mass $M_* = 4.24 \times
-  10^{10}$ \msun, and circular velocity $v_{circ} = xx$ km s$^{-1}$.
+  = 6.79 \times 10^{11}  \msun$, stellar mass $M_* = 4.24 \times
+  10^{10} \msun$, and circular velocity $v_{circ} = \editremark{xx}$ km s$^{-1}$.
 
@@
   of h277.  At $z = 0$, h258 has a virial mass of $M_{vir} = 7.74
-  \times 10^{11}$ \msun, stellar mass $M_* = 4.46 \times 10^{10}$
-  \msun, and circular velocity $v_{circ} = xx$ km s$^{-1}$.
+  \times 10^{11} \msun$, stellar mass $M_* = 4.46 \times 10^{10}$
+  \msun, and circular velocity $v_{circ} = \editremark{xx}$ km s$^{-1}$.
 
@@
 %
-The black hole mass and possibly spin in black hole-neutron star binaries can depend sensitively on binary formation
-channels.  Because of the extremely narrow range of masses that permit tidal disruption in BH-NS binaries, small changes
-in the mass distribution can produce significant changes in the electromagnetically detected population.
+A neutron star  (NS) coalescing with a black hole (BH) will be tidally disrupted prior to merger if and only if the component
+masses, spins, and equation of state permit it.  As described below, only a small fraction of all  possible coalescing
+BH-NS binaries have parameters consistent with tidal disruption.  
+%
+Stellar evolution and hence supernovae remnants are expected to evolve
+substantially with birth metallicity, the black hole mass and possibly spin in black hole-neutron star binaries can depend sensitively on binary formation
+channels and the fraction of coalescing NS-BH binaries which are tidally disrupted will vary
+over cosmic time. 
 %
@@
 phenomenological model for the metallicity-dependent mass distribution of BHs in BH-NS binaries
+
+\begin{figure}
+\includegraphics{Figures/fig-mma-TidalDisrupt-MbhA-VersusTheta}
+\caption{\label{fig:TidalDisrupt}\textbf{Tidal disruption}:  Following  \citet{2012PhRvD..86l4007F}, a plot of
+  the critical spin needed for tidal disruption versus black hole mass and inclination (solid black, dotted black,
+  dashed black, solid blue, and dotted blue are $\theta_{LS}=\pi/2,3\pi/8,\pi/4, \pi/8,0$ respectively).  Specifically,
+  this figure corresponds to $M_{\rm disk}=0$ in Eq. (\ref{eq:Mdisk}), assuming  a $1.4 M_\odot$ neutron star with compactness ${\cal
+    C}=1.66$ in inclined orbit around a spinning black hole of mass $m_{bh}$ and dimensionless spin $\chi_{bh}$.
+  Parameters consistent with tidal disruption are above the curves; prompt capture occurs below the
+  curve.
+}
+\end{figure}
+
+% POINT: Trend versus mass and opening angle.  [Be careful: disruption time will depend on opening angle]
+To estimate whether a specific compact binary will be tidally disrupted prior to merger, we employ the
+following procecure to identify posterior samples consistent with tidal disruption of a neutron star.  First, the
+smaller mass must lie within the range of masses allowed by our fiducial NS equation of state (\textbf{MPA1 from Ben}), here
+between $0.5 M_\odot$ and $2.5 M_\odot$.  Second, the disruption process must leave behind a remnant disk with nonzero
+mass, as estimated using Foucart's expression \cite{2012PhRvD..86l4007F} (his Eqs. (6,12-13)):
+\begin{align}
+\frac{M_{disk}}{M_{NS}} &=
+ 0.288 (3 m_{bh}/m_{ns})^{1/3}[1-2 {\cal C}] 
+\nonumber \\
+&
+ -0.148 (m_{bh}/m_{ns})  {\cal C} R_{isco}(a)/m_{bh} 
+\label{eq:Mdisk}
+\end{align}
+where $q=m_{bh}/m_{NS}$ is the binary mass ratio; $a=S_{bh}/m_{bh}^2$ is a dimensionless measure of the black hole spin;
+and  where ${\cal C}(m_{ns})=m_{ns}/R_{ns}$ is a mass- and equation-of-state dependent  measure of the neutron star
+compactness.  In Foucart's expression, shown above, $R_{isco}(a)$ is the radius of the  innermost stable equitorial circular orbit  of a test particle
+about a Kerr black hole  \cite{1972ApJ...178..347B}. % Brandon:  [their Eq. 2.21].   
+When the black hole spin is not aligned with the orbit, we use the aligned component of the black hole spin magnitude $a\rightarrow a \cos \theta_{LS}$ in this
+expression.   Fixing the neutron star mass $m_{ns}=1.4 M_\odot$ and hence compactness to ${\cal C}=1.66$, this expression implies a two-dimensional surface in
+the three-dimensional parameter space $m_{bh},a,\theta_{LS}$ seperates parameters corresponding to tidal disruption to
+parameters corresponding to prompt coalescence.
+%
+After coalescence, the remnant disk generates a tightly beamed electromagnetic counterpart.  For simplicity, we assume
+beaming angle is independent of the disruption process or progenitor parameters, so a constant beaming correction factor $f_b$ enters into all
+subsequent calculations and can hence be omitted.  
+%
+Figure \ref{fig:TidalDisrupt} shows contours of this expression for different values of $\theta_{LS}$.
+
+\begin{figure}
+\caption{\textbf{Disruption fraction}: Approximate tidal disrpution fraction}
+\end{figure}
+
+% POINT: Distribution of tilt angles
+Based on Monte Carlo simulations of supernova kicks \editremark{citations:Eggleton,Kalogera,IhmXXX}, we approximate the tilt angle distribution $p(\theta)$ of bound,
+coalescing BH-NS binaries by the positive half of a normal distribution
+\[
+p(\theta)\simeq e^{-\theta^2/2\sigma_\theta^2} \frac{2}{\sqrt{2\pi \sigma_\theta^2}}
+\]
+where $\sigma_{\theta}\simeq 1$ is a characteristic angular width that varies relatively weakly with the black hole mass
+and supernova kick velocity, for velocities consistent with pulsar recoil velocities \editremark{citations}.
+This simple distribution is consistent with some detailed population synthesis simulations by
+\texttt{StarTrack}. \editremark{validate with more modern startrack}  
+For simplicity, in this work we adopt $\sigma_{\theta}=1$.   
+%  POINT Average over spin distributions
+Using this approximate distribution of misalignment angles, Figure  assumed black hole mass and spin we calculate the
+fraction of coalescing binaries consistent with
+
+% POINT: Average over distributions
+
+The relative probability of a given tilt angle
+
+- first aproximations: tilt angle independent of merger time
+
+% POINT: Include delay time: get examples of disruption fraction versus time
+
+------
 
@@
 \appendix
+\section{Tidal disruption probability}
 

### 2015-05-28 paper/paper.tex
paper and bib: editing to add in theory of BH mass and spin distributions

@@
 \newcommand\cqg{CQG}
+\newcommand\E[1]{\left<#1\right>}
 %\newcommand\aap{A\&A}
@@
   of h277.  At $z = 0$, h258 has a virial mass of $M_{vir} = 7.74
-  \times 10^{11} \msun$, stellar mass $M_* = 4.46 \times 10^{10}$
-  \msun, and circular velocity $v_{circ} = \editremark{xx}$ km s$^{-1}$.
+  \times 10^{11} \msun$, stellar mass $M_* = 4.46 \times 10^{10} \msun$, and circular velocity $v_{circ} = \editremark{xx}$ km s$^{-1}$.
 
@@
 between $0.5 M_\odot$ and $2.5 M_\odot$.  Second, the disruption process must leave behind a remnant disk with nonzero
-mass, as estimated using Foucart's expression \cite{2012PhRvD..86l4007F} (his Eqs. (6,12-13)):
+mass, as estimated using the expression in \cite{2012PhRvD..86l4007F} (his Eqs. (6,12-13)):
 \begin{align}
@@
 compactness.  In Foucart's expression, shown above, $R_{isco}(a)$ is the radius of the  innermost stable equitorial circular orbit  of a test particle
-about a Kerr black hole  \cite{1972ApJ...178..347B}. % Brandon:  [their Eq. 2.21].   
+about a Kerr black hole  \citep{1972ApJ...178..347B}. % Brandon:  [their Eq. 2.21].   
 When the black hole spin is not aligned with the orbit, we use the aligned component of the black hole spin magnitude $a\rightarrow a \cos \theta_{LS}$ in this
@@
 \begin{figure}
-\caption{\textbf{Disruption fraction}: Approximate tidal disrpution fraction}
+\includegraphics{Figures/fig-mma-PrecomputeDisrupt}
+\caption{\label{fig:TidalDisrupt:Probability}\textbf{Disruption fraction}: Contour plot of the fraction
+  $P_{dis}(m_{bh},\chi_{bh})$ of BH-NS binaries with BH mass and spin $m_{bh},\chi_{bh}$ that are expected to tidally
+  disrupt using the assumptions in the text.  Contours are shown at $0.1, 1/3, 0.5, 0.9$.}
 \end{figure}
@@
 % POINT: Distribution of tilt angles
-Based on Monte Carlo simulations of supernova kicks \editremark{citations:Eggleton,Kalogera,IhmXXX}, we approximate the tilt angle distribution $p(\theta)$ of bound,
+Based on Monte Carlo simulations of supernova kicks as described in the Appendix, we approximate the
+cumulative tilt angle distribution $P(<\theta)$ of bound,
 coalescing BH-NS binaries by the positive half of a normal distribution
-\[
-p(\theta)\simeq e^{-\theta^2/2\sigma_\theta^2} \frac{2}{\sqrt{2\pi \sigma_\theta^2}}
-\]
-where $\sigma_{\theta}\simeq 1$ is a characteristic angular width that varies relatively weakly with the black hole mass
-and supernova kick velocity, for velocities consistent with pulsar recoil velocities \editremark{citations}.
-This simple distribution is consistent with some detailed population synthesis simulations by
-\texttt{StarTrack}. \editremark{validate with more modern startrack}  
+\begin{eqnarray}
+P(<\theta)\simeq \int_0^\theta e^{-\theta^2/2\sigma_\theta^2} \frac{2}{\sqrt{2\pi \sigma_\theta^2}} d\theta
+\end{eqnarray}
+where $\sigma_{\theta}\simeq 1$ is a characteristic angular width that varies relatively weakly with the black hole mass,
+ supernova kick velocity, and compact binary formation channel.  This simple distribution is consistent with some detailed population synthesis simulations by
+\texttt{StarTrack}.
 For simplicity, in this work we adopt $\sigma_{\theta}=1$.   
 %  POINT Average over spin distributions
-Using this approximate distribution of misalignment angles, Figure  assumed black hole mass and spin we calculate the
-fraction of coalescing binaries consistent with
+Using this approximate distribution of misalignment angles, Figure \ref{fig:TidalDisrupt:Probability} estimates the fraction
+$P_{dis}(m_{bh},\chi_{bh})$ of coalescing binaries with a given black hole mass and spin that should tidally disrupt.  
+For simplicity assuming detection weighting does not strongly favor specific relative orientations $\theta$, this
+distribution determines the relative likelihood that a gravitational wave event with a given BH mass and spin produces
+is consistent with an electromagnetic counterpart.
 
 % POINT: Average over distributions
-
-The relative probability of a given tilt angle
-
-- first aproximations: tilt angle independent of merger time
+The relative event rate of electromagnetic counterparts to BH-NS disruptions therefore depends on the intrinsic
+distribution $p_d(m_{bh},\chi_{bh})$ of black hole mass and spin among GW-detected BH-NS mergers and the probability
+that an event is detected via electromagnetic emission and GW: 
+\begin{eqnarray}
+p_{em}(m_{bh},\chi_{bh}) = \frac{P_{dis}(m_{bh},\chi_{bh}) p_d(m_{bh},\chi_{bh})}{\int dm_{bh} d\chi_{bh}P_{dis}(m_{bh},\chi_{bh}) p_d(m_{bh},\chi_{bh})}
+\end{eqnarray}
+where the constant beaming factor cancels.  
+%
+Because black holes in BH-NS binaries are currently expected to accrete relatively little mass, the spin distribution at merger
+should be close to their birth spin distribution.   This distribution is entirely unknown but likely significant, given
+tidally-induced spinup prior to merger\editremark{Ott}; we will assume the spin distribution to be uniform between $0.7$
+and $1$, independent of formation channel or birth conditions: \editremark{change: make this one Z dependent}
+\begin{eqnarray}
+p(\chi_{bh}) = \frac{1}{0.3} \theta(\chi_{bh}-0.7)\theta(1-\chi_{bh})
+\end{eqnarray}
+As discussed in \cite{popsyn-LowMetallicityImpact2-StarTrackRevised-2012},  the black hole mass distribution depends
+sensitively on the birth environment and coalescing binary formation channels; see their Tables 7 and 9 and their Figures 6,9, 11, and 13,
+reconstructing the BH mass from the reported chirp masses (red curves).  
+Omitting formation channels that predict implausibly high compact binary formation rates (their model A), the
+distribution of $m_{bh}$ in BH-NS binaries extends over a wide range.  As a first approximation, the BH mass
+distribution in BH-NS binaries does not depend on composition, favoring BH-NS binaries with relatively low BH masses
+$m_{bh}\lesssim 5-9 M_\odot$ independent of birth composition.  
+% \cite{2012ApJ...749...91F}  : physics of SN explosions used in these mechanisms. Rapid engine needed for mass gap, but
+% is there one? 
+% mc[m1_, m2_] := (m1 m2)^(3/5)/(m1 + m2)^(1/5)
+% Solve[mc[m1, 1.4] == 2.5]
+For simplicity, we will adopt a uniform mass distribution between $5$ and $9 M_\odot$:
+\begin{eqnarray}
+p(m_{bh}) = \frac{1}{4 M_\odot} \theta(m_{bh}-4 M_\odot)\theta(9 M_\odot-m_{bh})
+\end{eqnarray}
 
 % POINT: Include delay time: get examples of disruption fraction versus time
-
-------
-
-\editremark{calibrate mass distribution to synthetic universe/Dominik - but also allow reversed trend}
-DISCUSSION: could we explain the redshift distribution of short GRBs this way?
 
@@
   is a hard cutoff on some masses, as having no EM counterpart)
+
+* Aside: BBH distribution the most sensitive, but not relevant for EM followup
 \end{verbatim}
@@
 \appendix
-\section{Tidal disruption probability}
+\section{Binary evolution and spin-orbit misalignment}
+
+\editremark{ROS to do} -- find python/C code (Davide?) for simple MC; mine old resuts from startrack
+
+%% POINT: Other reference
+% 2014arXiv1401.3032W  - fallback details
+
+The progenitors of both components of a BH-NS binary undergo supernova, whose associated asymmetric mass loss and
+supernova kicks significantly perturb the orbit  \citep{2013PhRvD..87j4028G,2002MNRAS.329..897H,2000ApJ...541..319K}.   Assuming progeniror stellar spins are
+aligned with the orbital plane (e.g., due to strong tides), only asymmetric supernova kicks can change
+the orbital plane and introduce misalignment between the BH spin and the orbit.   The distribution of spin-orbit
+misalignments expected in any specific binary depends strongly on weakly-constrained binary evolution physics, the
+treatment of which is beyond the scope of this article.  Previous detailed calculations have reported on spin-orbit
+misalignment \citep{2010ApJ...719L..79F,2008ApJ...682..474B,2004PhRvD..69j2002G}.  That said, relatively simple order-of-magnitude calculations
+can explain the typical small misalignment angles expected among merging BH-NS binaries.
+% POINT: Small angle tilt forma (follows from simple considerations of angular momentum)
+Specifically, in the limit of a small supernova kick $\vec{v}_K$, the orbital plane  change by an angle $\theta \simeq \vec{v}_K \cdot
+\hat{z}/v_{orb}$ where $\hat{z}$ is the direction perpendicular to the (circular) orbital plane.  The black hole forms first and cannot
+significantly change its spin magnitude or direction through accretion; therefore the two supernovae kicks produced by
+forming the black hole and then neutron star add (in quadrature) to produce a characteristic RMS misalignment error
+$\E{\theta^2}$.
+%
+For simplicity, we will adopt the model used in the \texttt{StarTrack} binary evolution code \citep{StarTrack2}: binaries
+prior to each supernovae can be approximated as in circular orbits;  supernova kicks on neutron stars produce a Maxwellian
+distribution of velocities with 1d velocity dispersion $\sigma_v=265$ \citep{HobbsKicks};  supernova kicks on black holes
+$v_{bh}$ are suppressed by fallback, with velocities  $\vec{v}_{K,BH} = (1-f_b)v_{NS}$ suppressed by fallback accretion
+onto the black hole; and the dominant formation channels for BH-NS binaries involve common
+envelope accretion after the first supernova forms a black hole.   Combining these expressions under these assumptions, we expect the net misalignment  $\theta$ due to both supernova
+explosions will have zero mean and variance
+\begin{eqnarray}
+\label{eq:MisalignmentOrderOfMagnitude}
+\E{\theta^2} = \frac{\E{v^2}}{3}\left[ \frac{(1-f_b)^2\epsilon_1}{v_{orb,1}^2}+\frac{\epsilon_2}{v_{orb,2}^2} \right]
+\end{eqnarray}
+where $v_{orb,1}$ and $v_{orb,2}$ are the orbital velocities at the first and second supernova and where
+$\epsilon_1,\epsilon_2$ are factors between 0 and 1 which account for the fact that the average is taken over binaries which \emph{survive} and are not
+disrupted by the kick.  Because the second supernova  occurs in a tight orbit (post common
+envelope),  the orbital velocity $v_{orb,2}$ at the supernova producing the neutron
+star will be  large:  if $M_2$ and $r_2$ are the total mass and orbital separation, $v_{orb,2}=\sqrt{GM_{2}/r}\simeq
+440\unit{km/s} \sqrt{M/M_\odot/(r_2/R_\odot)}$, 
+% Convert[Sqrt[  GravitationalConstant (mbh SolarMass)/(r SolarRadius)], (Kilo Meter/    Second)]
+comparable to or
+significantly in excess of the typical supernova kick velocity for massive black holes orbiting the stripped progenitors of
+neutron stars at seperations of a few $R_\odot$.  Conversely, at birth the black hole will often capture a significant
+amount of the stellar envelope (``fallback'' accretion or prompt collapse) with $f_b\simeq 1$.  Therefore, even though
+the initial orbit is wide, orbital  velocity is very small, and hence the orbit can be easily strongly misaligned by
+supernova kicks,  the first kick when acting on a massive black hole can produce little to  modest amounts orbital
+misalignment.
+
+% POINT: Second term of order unity
+For exceptional models of binary evolution, the population of coalescing BH-NS binaries will depend extremely critically on the
+a finely-tuned second supernova.  In this case, only a small fraction of surviving BH-NS binaries merge; the BH-NS merger rate will be extremely low and  depend extremely sensitively on
+the magnitude of supernova kicks; and the misalignment produced by the second supernova can frequently be very large.  More typically, however, a significant fraction of surviving BH-NS binaries merge
+\citep{2008ApJ...675..566O,popsyn-LowMetallicityImpact2-StarTrackRevised-2012,popsyn-LowMetallicityImpact2b-StarTrackRevised-2013,popsyn-LowMetallicityImpact2c-StarTrackRevised-2014}; in these cases, the  second supernova's kick does not require fine-tuning to guarantee
+coalescence.   In these most common scenarios, the second term in Eq. (\ref{eq:MisalignmentOrderOfMagnitude}) is of
+order unity.
+
+% POINT:
+As a result, the process of surviving two supernova kicks generally produces a wide  distribution of misalignment
+angles concentrated near $\theta\simeq 0$.  This wide distribution is expected to be relatively robust.  Extremely wide
+distributions are disfavored kinematically and by the requirement that sufficiently many binaries survive to coalesce.
+Conversely, the width of the distribution is bounded below by the contribution from the second supernova kick.\footnote{For simplicity and brevity, we neglect the
+  possibility of different modes of supernova explosions and hence kicks, notably via electron capture supernovae \citep{2012ARNPS..62..407J,2004ApJ...612.1044P,2010MNRAS.406..656K,2015ApJ...801...32A}.
+That said, small supernova kicks in NS
+  birth would further minimize any spin-orbit misaligment and hence further favor the strong dependence of tidal disruption probability on the black hole mass and spin
+  distribution described in the text.} 
+As a first approximation,  the cumulative distribution of misalignment angles should agree with direct calculations \cite{2010ApJ...719L..79F,2008ApJ...682..474B,2004PhRvD..69j2002G}.
+
+% POINT: 
+%% To calculate the necessary inputs to this expression, we adopt one particular family of supernova mechanism:  Fryer et al 
+%% \cite{2012ApJ...749...91F}, the model adopted in \texttt{StarTrack} and applied in detailed calculations of binary
+%% evolution
+%% \cite{popsyn-LowMetallicityImpact2-StarTrackRevised-2012,popsyn-LowMetallicityImpact2b-StarTrackRevised-2013,popsyn-LowMetallicityImpact2c-StarTrackRevised-2014}.
+%% Because of significant residual uncertainty in the supernova mechanism, our results are proof-of-concept calculations
+%% intended to illustrate plausible effects of composition on remnant masses, spins, and hence misalignments.  Other models
+%% for supernovae produce dramatically different initial-final mass relations \cite{2012ApJ...757...69U} and are
+%% anticipated to produce equally different different amounts of spin-orbit
+%% misalignment in BH-NS binaries.  
+%% %
+%% Observations of isolated pulsar
+%% recoils \cite{1997MNRAS.291..569H,Ar} and binary pulsars \cite{psr-kicks-WongWillemsKalogera2010}
+%% strongly constrain the action of random supernova kicks on neutron stars.
 

### 2015-05-28 paper/paper.tex
paper.tex: notes for later
paper.tex: More notes on BH birth spin and prompt collapse

@@
 
+\section{Black hole spins in BH-NS binaries}
+
+* References: review in Fragos and McClintock \cite{2015ApJ...800...17F}  and references therein (LMXBs) -- low birth
+spins, because of stripped companions; for more on measurement, see \cite{2011CQGra..28k4009M}
+
+* References on BH spin versus mass: angular momentum capture in prompt collapse: O'Connor and Ott and references
+therein (note no fallback); note Ugliano has a differen result. See also Clausen et
+al (probability of BH vs mass) for more recent
+%O'Connor and Ott: a criteria for explosions http://arxiv.org/pdf/1010.5550v2.pdf...note they don't have fallback.
+%Clausen et al: trying to find formation probability vs mass http://arxiv.org/pdf/1406.4869v2.pdf (assuming no binaries)
+%...note also http://adsabs.harvard.edu/abs/2012ApJ...757...69U (which is complicated)
+
+%* References: \cite{2013ApJ...762..104S}
+
 \section{Outline }

### 2015-05-29 paper/paper.tex
new edits yay

@@
 \subsection{Simulating galaxy evolution}
-To thoroughly examine the significance of low metallicity star
-formation, we have run a cosmological smoothed particle hydrodynamics
-(SPH) $N$-body simulation of a Milky Way-like galaxy with GASOLINE
-\citep{Stadel01,Wadsley04}.  This simulation allows us to analyze both
+To thoroughly study the significance of low metallicity star
+formation, we examine cosmological smoothed particle hydrodynamics
+(SPH) $N$-body simulations of Milky Way-like galaxies with GASOLINE
+\citep{2001PhDT........21S,2004NewA....9..137W}.  These simulations allow us to analyze both
 spatially and temporally resolved star formation, and determine not
 only the metallicity history of compact object progenitors, but also
-their dynamical evolution.  One simulation we report here, $h258$,
+their dynamical evolution.  
+%maybe move the below section to later and/or consolidate
+One simulation we report here, $h258$,
 involves the formation of a Milky Way-like disk galaxy whose
@@
 simulation has been previously discussed by
-\citet{Governato09,Bellovary10,Bellovary11,Brooks11}; however we have
+\citet{2009MNRAS.398..312G,2010ApJ...721L.148B,2011ApJ...742...13B,2011ApJ...728...51B}; however we have
 re-run the simulation at a factor of two higher in spatial resolution
 and additionally included new physics including a prescription for
-cooling by molecular hydrogen (Christensen et al. in prep).
+cooling by molecular hydrogen \citet{2012MNRAS.425.3058C}.
 
 We selected our simulated region of interest from a 50 Mpc volume of
-uniform resolution, and resampled the region of interest at very high
-resolution using the volume renormalization technique \citep{Katz93}.
+uniform resolution, and resampled the region at very high
+resolution using the volume renormalization technique \citep{1993ApJ...412..455K}.
 This technique allows us to follow the detailed physical processes
 involved in galaxy evolution in our selected region while still
-including large-scale torques from cosmic structure.  We use {\bf
-WMAPX} cosmology \citep{WMAP} and model the ionizing UV background
-with the prescription from \citet{Haardt96}.  Stars form
+including large-scale torques from cosmic structure.  We use
+WMAP3 cosmology \citep{WMAP} and model the ionizing UV background
+with the prescription from \citet{1996ApJ...461...20H}.  Stars form
 probabilistically from gas particles which meet density ($n_{min} =
-10$ amu cm$^{-3}$) and temperature ($T_{max} = 10^4$ K) thresholds
-{\bf (additional description needed for H2 SF prescription)}. If a gas
+10$ amu cm$^{-3}$) and temperature ($T_{max} = 10^4$ K) thresholds. If a gas
 particle meets these criteria, it has a likelihood of forming a star
 particle (representing a simple stellar population with a Kroupa IMF
-\citep{Kroupa}) which is given by
+\citep{2001MNRAS.322..231K}) which is given by
 
 \begin{equation}
-p = \frac{m_{\rm gas}}{m_{\rm star}} (1 - e^{c^*\Delta t/t_{\rm form}})
+p = \frac{m_{\rm gas}}{m_{\rm star}} (1 - e^{c^*\rm X_{\rm H_2} \Delta t/t_{\rm form}})
 \end{equation}
@@
 that our galaxies match the observed Kennicutt-Schmidt law
-\citep{Kennicutt89}; $m_{star}$ and $m_{gas}$ are the star and gas
-particle masses;\footnote{In our high-resolution simulations \textbf{ROS-check!}, each gas particle starts with a mass
+\citep{1989ApJ...344..685K};  X$_{\rm H_2}$ is the molecular hydrogen fraction of the gas particle; $m_{star}$ and $m_{gas}$ are the star and gas
+particle masses;\footnote{In our high-resolution simulations \textbf{ROS-check!}\editremark{this number is correct, is that what you want to check? - JMB}, each gas particle starts with a mass
   $m_{gas,0}=26,676 M_\odot$, gaining mass from feedback and losing it to star formation.  Each star particle, when
@@
 which we set to 1 Myr.  We model supernova feedback using the
-blastwave formalism described in \citet{McKee77} and implemented in
-our simulations as in \citet{Stinson06}.  Each supernova releases
+blastwave formalism described in \citet{1977ApJ...218..148M} and implemented in
+our simulations as in \citet{2006MNRAS.373.1074S}.  Each supernova releases
 $E_{SN} = 10^{51}$ erg into the surrounding gas with a radius
@@
 number of observed relations such as the mass-metallicity relation
-\citep{Brooks07}, the Tully-Fisher relation \citep{Governato09}, and
-the size-luminosity relation \citep{Brooks11}, as well as reproduce
+\citep{2007ApJ...655L..17B}, the Tully-Fisher relation \citep{2009MNRAS.398..312G}, and
+the size-luminosity relation \citep{2011ApJ...728...51B}, as well as reproduce
 the detailed characteristics of bulgeless dwarf galaxies
-\citep{Governato10} and the Milky Way \citep{Guedes11}.
+\citep{2010Natur.463..203G} and the Milky Way \citep{2011ApJ...742...76G}.
 
 Also included in our simulations is a scheme for turbulent metal
-diffusion \citep{Shen10}.  Metals are created in supernova explosions
+diffusion \citep{2010MNRAS.407.1581S}.  Metals are created in supernova explosions
 and deposited directly to the gas within the blast radius.  Stellar
-masses are converted to ages as described by \citet{Raiteri96}, and
+masses are converted to ages as described by \citet{1996A&A...315..105R}, and
 stars more massive than 8 M$_\odot$ are able to undergo a Type II
 supernova.  We follow metal enrichment from both Type II and Type 1a
-supernova, with metal yields derived from \citet{Weaver93} and
-\citet{Thielemann86} respectively.  From this point onwards metals
+supernova, with metal yields derived from \citet{1993PhR...227...65W} and
+\citet{1986A&A...158...17T} respectively.  From this point onwards metals
 diffuse through the surrounding gas, according to 
@@
 and $h$ is the SPH smoothing length, $S_{ij}$ is the trace-free shear
-tensor, and $C_{diff}$ is a dimensionless constant which we set to
-{\bf something.  Reasons for setting it are good, let's have some.
-Sijing finds that C = 0.05 makes for a good comparison to clusters, we
-tend to use something more conservative}.
+tensor, and $C_{diff}$ is a dimensionless constant which we set to a conservative value of 0.03.
+
+%Sijing finds that C = 0.05 makes for a good comparison to clusters, and that C = 0.05 - 0.1 is expected from turbulence theory.
 
 We identify individual galaxies using the halo finder $AHF$
-\citep{Gill04,Knollmann09}, which identifies halos based on an
-overdensity criterion for a flat universe \citep{Gross97}.  For this
+\citep{2004MNRAS.351..399G,2009ApJS..182..608K}, which identifies halos based on an
+overdensity criterion for a flat universe \citep{1997PhDT........14G}.  For this
 work, we are focusing on the primary (i.e. most massive) galaxy at any
@@
 of a galaxy, in terms of its stellar mass and metallicity evolution,
-depends strongly on its interaction history.  Galaxies which look
+depends strongly on its interaction history.  Galaxies which appear
 similar at the present day may have had drastically different
@@
 properties, including stellar dynamics
-\citep{Loebman12,Loebman14,Kassin14}, baryon fraction
-\citep{Munshi13}, halo properties \citep{Zolotov09,Zolotov10}, and
-  disk properties \citep{Brooks11}.  It has a virial mass of $M_{vir}
-  = 6.79 \times 10^{11}  \msun$, stellar mass $M_* = 4.24 \times
-  10^{10} \msun$, and circular velocity $v_{circ} = \editremark{xx}$ km s$^{-1}$.
+\citep{2012ApJ...758L..23L,2014ApJ...794..151L,2014ApJ...790...89K}, baryon fraction
+\citep{2013ApJ...766...56M}, halo properties \citep{2009ApJ...702.1058Z,2010ApJ...721..738Z}, and
+disk properties \citep{2011ApJ...728...51B}.  It has a virial mass of $M_{vir} =
+6.79 \times 10^{11} \msun$, stellar mass $M_* = 4.24 \times 10^{10}
+\msun$, and maximum circular velocity $v_{circ} = 235$ km s$^{-1}$.
 
@@
   a gas disk rapidly reforms following the collision (see
-  \citet{Governato09}), resulting in a massive disk galaxy at $z = 0$
+  \citet{2009MNRAS.398..312G}), resulting in a massive disk galaxy at $z = 0$
   which looks remarkably similar to the Milky Way and to the other
@@
   progenitor galaxies actually experiences its own additional major
-  merger events around $z = 2.5$ ({\bf check!}).  The combination of
+  merger events around $z = 2$.  The combination of
   the series of major mergers, plus a number of minor interactions and
@@
   of h277.  At $z = 0$, h258 has a virial mass of $M_{vir} = 7.74
-  \times 10^{11} \msun$, stellar mass $M_* = 4.46 \times 10^{10} \msun$, and circular velocity $v_{circ} = \editremark{xx}$ km s$^{-1}$.
+  \times 10^{11} \msun$, stellar mass $M_* = 4.46 \times 10^{10}
+  \msun$, and maximum circular velocity $v_{circ} = 242$ km s$^{-1}$.  \editremark{Might we want to show the images of these galaxies?}
 
@@
   one standard devation of the mean, while the thick dashed lines
-  represent the top and bottom 90\%.  We see that {\bf different things happen at different times.}
+  represent the top and bottom 90\%.  We see that the early evolution
+  of the metal properties of these galaxies does differ - between 0.5
+  and 6 Gyr, h277 hosts a {\bf modestly} more metal-rich population than
+  h258. \editremark{The difference isn't all that big, I want to address it without sounding foolish.}
 

### 2015-06-02 paper/paper.tex
more edits

@@
 \newcommand\editremark[1]{{\color{red}#1}}
+\newcommand\jillianremark[1]{{\color{blue}#1}}
 \newcommand\msun{M_\odot}
@@
 \begin{document}
-\title{Details matter: Similar-looking host galaxies can produce different merging compact binary populations} 
+\title{Details matter: Similar host galaxies can harbor different merging compact binary populations} 
 \author{R.\ O'Shaughnessy}
@@
 simulations can reproduce present-day galaxies with notably different assembly and star formation histories.  
-Recent binary evolution simulations suggest the compact binary merger rate depends
+Recent simulations of compact binary evolution suggest the compact object merger rate depends
 sensitively on the progentior's metallicity, to the extent that rare low-metallicity star formation during galaxy
@@
 compact binary populations.
-We discuss the implications for transient multimessenger astronomy with compact binary sources. 
+We discuss the implications for transient multimessenger astronomy with compact binary sources. \jillianremark{Add quantifiable stuff when we have it.}
 %% Present and future observations of  merging compact binaries can provide valuable constraints on their birthrate
@@
 and chemical evolution histories \editremark{citation: need better ones} \citep[see,e.g.][]{2009MNRAS.396..462K,2014MNRAS.444..336C}.
+\jillianremark{Do you want citations of GRB host observations or just general galaxy stuff?}
 % POINT: But is it useful?
@@
 \citep{1989ApJ...344..685K};  X$_{\rm H_2}$ is the molecular hydrogen fraction of the gas particle; $m_{star}$ and $m_{gas}$ are the star and gas
-particle masses;\footnote{In our high-resolution simulations \textbf{ROS-check!}\editremark{this number is correct, is that what you want to check? - JMB}, each gas particle starts with a mass
+particle masses;\footnote{In our high-resolution simulations \textbf{ROS-check!}\jillianremark{this number is correct, is that what you want to check? - JMB}, each gas particle starts with a mass
   $m_{gas,0}=26,676 M_\odot$, gaining mass from feedback and losing it to star formation.  Each star particle, when
@@
 mass of merging binaries.
+\jillianremark{The previous sentence is confusing - rephrase?
+I have trouble with ``the detected population can further favor low-Z environments'' because that makes no sense.}
 % POINT: Simple model to encompass all
@@
 %
-Stellar evolution and hence supernovae remnants are expected to evolve
+\jillianremark{Grammatical nightmare ahead: }Stellar evolution and hence supernovae remnants are expected to evolve
 substantially with birth metallicity, the black hole mass and possibly spin in black hole-neutron star binaries can depend sensitively on binary formation
@@
 Figure \ref{fig:TidalDisrupt} shows contours of this expression for different values of $\theta_{LS}$.
+\jillianremark{Add a sentence here describing the significance of the plot.
+e.g.
+low-mass BHs can have a range of spins, regardless of angle, but high mass BHs always get high spins yay.}
 

### 2016-07-11 paper/paper-extra.tex
Lots of stuff

--- 2015-06-02 paper/paper.tex
@@
 
+\editremark{We will be very careful to specify how SFR and metallicity are measured, backtracking}
+
+Add me: \cite{2013ApJ...779..102K}
+Add me but note conflict \cite{2015MNRAS.453.4337S}, etc
+
+Add me: \citet{2014ARAA..52..415M}
+
+Add me: Hopkins et al  \cite{2016arXiv160508783L} (in context of similar model, building off my prior work)
+
 \section{Introduction}
@@
 %     ... which will enable new physics
-In the next few years, ground-based gravitational wave detectors like LIGO 
+Gravitational waves have been detected from  coalescing  black hole binaries \citep{DetectionPaper,LIGO-O1-BBH}. 
+Over the next few years, ground-based gravitational wave detectors like LIGO 
 and Virgo  should detect the gravitational
-wave signal from merging compact binaries, including  binary  neutron stars and black hole-neutron star binaries; see,
-e.g., \cite{LIGO-Inspiral-Rates} and references therein.
-In addition to the strong gravitational wave signal, mergers of neutron stars are expected to  frequently be accompanied by detectable
+wave signal from many more similar merging compact binaries \citep{LIGO-O1-BBH,RatesPaper,gwastro-EventPopsynPaper-2016}, as well as  binary  neutron stars and black hole-neutron star binaries \citep{LIGO-Inspiral-Rates,popsyn-LowMetallicityImpact2c-StarTrackRevised-2014}.
+%
+The host galaxies of gravitational wave sources will identified, either directly or statistically.  
+On the one hand, addition to the strong gravitational wave signal, mergers of neutron stars are expected to  frequently be accompanied by detectable
 electromagnetic radiation  via a number of  mechanisms, including a strong but tightly beamed
@@
 the sky position and therefore approximate birthplace of each merging binary.    
+%
+On the other hand, gravitational wave detectors can perform high-precision sky and volumetric localization \cite{2016LRR....19....1A,2016arXiv160307333S}.  As GW detector
+networks increase in sensitivity, these localizations will allow statistical and, eventually, unique identification of
+host galaxies directly, even without associated electromagnetic emission.
+%
 As with supernovae and  GRBs, these host galaxy associations   are expected to tightly constrain models for compact binary
@@
 metallicity-dependent  phenomenological model to calculate the present-day rate and mass distribution of compact binary
-mergers from  a galaxy's known history.  
+mergers from  a galaxy's known history.   In \S \ref{sec:results:BBH}, we use this model to demonstrate the binary black hole coalescence rate
+depends sensitively on the galaxy's assembly history, in a manner which is far from apparent from its present-day
+properties.  
 In \S \ref{sec:results} we show that while these two galaxy formation models should produce comparable detectable binary neutron star
@@
 \begin{figure*}
+\includegraphics[width=\columnwidth]{Figures/boring}
+\includegraphics[width=\columnwidth]{Figures/exciting}
+\caption{\textbf{Two fiducial galaxies}
+}
+\end{figure*}
+
+\begin{figure*}
 \includegraphics[width=\columnwidth]{Figures/sfh}
@@
 %
-Finally, for simplicity we adopt the universal delay time distribution
+
+For binaries containing neutron stars, for simplicity we adopt the universal delay time distribution
 %% Finally, we parameterize the delay time distribution by  either
@@
 
+\editremark{Note}:
+
+\section{Formation rate for binary black holes}
+\label{sec:results:BBH}
+
+\section{Model for electromagnetic counterparts}
 \subsection{Tidal disruption and black hole mass versus metallicity}
@@
 \section{Conclusions}
+
+* BBH properties far from apparent.
+No surprise: delays can be long \cite{PSellipticals,popsyn-LowMetallicityImpact2b-StarTrackRevised-2013,gwastro-EventPopsynPaper-2016}, particularly because formation in low Z favored,
+so system changes significantly from assembly conditions
+
+* EM counterpart properties: delay times are shorter, so more of a surprise that formation scenario matters.  However,
+BH properties depend on $Z$, which can influence the mass and spin of BHs that produce EM counterparts.
+
+* Detailed analysis of one host galaxy presented in this work is complementary to the population-based approach used in
+\cite{2016arXiv160508783L}, which favored formation in a wide range of galaxies and event times.   % that analysis also
+                                % used a poor input from BSE, about the coalescence delay
 

### 2016-07-11 paper/paper.tex
Draft

@@
 
+%% absolutely critical vs optional
+%
+% critical
+%  -write paper as is, minmal
+% optional
+%  - add dwarfs. They are important
+%  - add ems counterparts. They are important
+%  - discussion of multimessenger astro
+
 \maketitle
+
+\editremark{We will be very careful to specify how SFR and metallicity are measured, backtracking}
+
+Add me: \cite{2013ApJ...779..102K}
+Add me but note conflict \cite{2015MNRAS.453.4337S}, etc
+
+Add me: \citet{2014ARAA..52..415M}
+
+Add me: Hopkins et al  \cite{2016arXiv160508783L} (in context of similar model, building off my prior work)
 
@@
 
-\subsection{Tidal disruption and black hole mass versus metallicity}
-At merger, black holes may promptly engulf a companion neutron star \editremark{same papers as for Brandon:Foucart,
-  etc}, unless they have sufficiently small mass and sufficiently large spin.  Without  a tidal disruption event prior to merger, the prospects for associated electromagnetic counterparts
-are severely diminished.  
-%
-A neutron star  (NS) coalescing with a black hole (BH) will be tidally disrupted prior to merger if and only if the component
-masses, spins, and equation of state permit it.  As described below, only a small fraction of all  possible coalescing
-BH-NS binaries have parameters consistent with tidal disruption.  
-%
-\jillianremark{Grammatical nightmare ahead: }Stellar evolution and hence supernovae remnants are expected to evolve
-substantially with birth metallicity, the black hole mass and possibly spin in black hole-neutron star binaries can depend sensitively on binary formation
-channels and the fraction of coalescing NS-BH binaries which are tidally disrupted will vary
-over cosmic time. 
-%
-To quantify this effect, we adopt a simple formula for tidal disruption of neutron stars in BH-NS binaries and a simple
-phenomenological model for the metallicity-dependent mass distribution of BHs in BH-NS binaries
+For binary black holes formed near solar metallicity, the delay time distribution can favor long delays between birth
+and merger, as demonstrated in \abbrvPSellipticals{}.
 
-\begin{figure}
-\includegraphics{Figures/fig-mma-TidalDisrupt-MbhA-VersusTheta}
-\caption{\label{fig:TidalDisrupt}\textbf{Tidal disruption}:  Following  \citet{2012PhRvD..86l4007F}, a plot of
-  the critical spin needed for tidal disruption versus black hole mass and inclination (solid black, dotted black,
-  dashed black, solid blue, and dotted blue are $\theta_{LS}=\pi/2,3\pi/8,\pi/4, \pi/8,0$ respectively).  Specifically,
-  this figure corresponds to $M_{\rm disk}=0$ in Eq. (\ref{eq:Mdisk}), assuming  a $1.4 M_\odot$ neutron star with compactness ${\cal
-    C}=1.66$ in inclined orbit around a spinning black hole of mass $m_{bh}$ and dimensionless spin $\chi_{bh}$.
-  Parameters consistent with tidal disruption are above the curves; prompt capture occurs below the
-  curve.
-}
-\end{figure}
+Figure 2 of  \cite{2016arXiv160508783L} is an extreme example of this well-known trend
 
-% POINT: Trend versus mass and opening angle.  [Be careful: disruption time will depend on opening angle]
-To estimate whether a specific compact binary will be tidally disrupted prior to merger, we employ the
-following procecure to identify posterior samples consistent with tidal disruption of a neutron star.  First, the
-smaller mass must lie within the range of masses allowed by our fiducial NS equation of state (\textbf{MPA1 from Ben}), here
-between $0.5 M_\odot$ and $2.5 M_\odot$.  Second, the disruption process must leave behind a remnant disk with nonzero
-mass, as estimated using the expression in \cite{2012PhRvD..86l4007F} (his Eqs. (6,12-13)):
-\begin{align}
-\frac{M_{disk}}{M_{NS}} &=
- 0.288 (3 m_{bh}/m_{ns})^{1/3}[1-2 {\cal C}] 
-\nonumber \\
-&
- -0.148 (m_{bh}/m_{ns})  {\cal C} R_{isco}(a)/m_{bh} 
-\label{eq:Mdisk}
-\end{align}
-where $q=m_{bh}/m_{NS}$ is the binary mass ratio; $a=S_{bh}/m_{bh}^2$ is a dimensionless measure of the black hole spin;
-and  where ${\cal C}(m_{ns})=m_{ns}/R_{ns}$ is a mass- and equation-of-state dependent  measure of the neutron star
-compactness.  In Foucart's expression, shown above, $R_{isco}(a)$ is the radius of the  innermost stable equitorial circular orbit  of a test particle
-about a Kerr black hole  \citep{1972ApJ...178..347B}. % Brandon:  [their Eq. 2.21].   
-When the black hole spin is not aligned with the orbit, we use the aligned component of the black hole spin magnitude $a\rightarrow a \cos \theta_{LS}$ in this
-expression.   Fixing the neutron star mass $m_{ns}=1.4 M_\odot$ and hence compactness to ${\cal C}=1.66$, this expression implies a two-dimensional surface in
-the three-dimensional parameter space $m_{bh},a,\theta_{LS}$ seperates parameters corresponding to tidal disruption to
-parameters corresponding to prompt coalescence.
-%
-After coalescence, the remnant disk generates a tightly beamed electromagnetic counterpart.  For simplicity, we assume
-beaming angle is independent of the disruption process or progenitor parameters, so a constant beaming correction factor $f_b$ enters into all
-subsequent calculations and can hence be omitted.  
-%
-Figure \ref{fig:TidalDisrupt} shows contours of this expression for different values of $\theta_{LS}$.
-\jillianremark{Add a sentence here describing the significance of the plot.
-e.g.
-low-mass BHs can have a range of spins, regardless of angle, but high mass BHs always get high spins yay.}
+\editremark{Note}:
 
-\begin{figure}
-\includegraphics{Figures/fig-mma-PrecomputeDisrupt}
-\caption{\label{fig:TidalDisrupt:Probability}\textbf{Disruption fraction}: Contour plot of the fraction
-  $P_{dis}(m_{bh},\chi_{bh})$ of BH-NS binaries with BH mass and spin $m_{bh},\chi_{bh}$ that are expected to tidally
-  disrupt using the assumptions in the text.  Contours are shown at $0.1, 1/3, 0.5, 0.9$.}
-\end{figure}
-
-% POINT: Distribution of tilt angles
-Based on Monte Carlo simulations of supernova kicks as described in the Appendix, we approximate the
-cumulative tilt angle distribution $P(<\theta)$ of bound,
-coalescing BH-NS binaries by the positive half of a normal distribution
-\begin{eqnarray}
-P(<\theta)\simeq \int_0^\theta e^{-\theta^2/2\sigma_\theta^2} \frac{2}{\sqrt{2\pi \sigma_\theta^2}} d\theta
-\end{eqnarray}
-where $\sigma_{\theta}\simeq 1$ is a characteristic angular width that varies relatively weakly with the black hole mass,
- supernova kick velocity, and compact binary formation channel.  This simple distribution is consistent with some detailed population synthesis simulations by
-\texttt{StarTrack}.
-For simplicity, in this work we adopt $\sigma_{\theta}=1$.   
-%  POINT Average over spin distributions
-Using this approximate distribution of misalignment angles, Figure \ref{fig:TidalDisrupt:Probability} estimates the fraction
-$P_{dis}(m_{bh},\chi_{bh})$ of coalescing binaries with a given black hole mass and spin that should tidally disrupt.  
-For simplicity assuming detection weighting does not strongly favor specific relative orientations $\theta$, this
-distribution determines the relative likelihood that a gravitational wave event with a given BH mass and spin produces
-is consistent with an electromagnetic counterpart.
-
-% POINT: Average over distributions
-The relative event rate of electromagnetic counterparts to BH-NS disruptions therefore depends on the intrinsic
-distribution $p_d(m_{bh},\chi_{bh})$ of black hole mass and spin among GW-detected BH-NS mergers and the probability
-that an event is detected via electromagnetic emission and GW: 
-\begin{eqnarray}
-p_{em}(m_{bh},\chi_{bh}) = \frac{P_{dis}(m_{bh},\chi_{bh}) p_d(m_{bh},\chi_{bh})}{\int dm_{bh} d\chi_{bh}P_{dis}(m_{bh},\chi_{bh}) p_d(m_{bh},\chi_{bh})}
-\end{eqnarray}
-where the constant beaming factor cancels.  
-%
-Because black holes in BH-NS binaries are currently expected to accrete relatively little mass, the spin distribution at merger
-should be close to their birth spin distribution.   This distribution is entirely unknown but likely significant, given
-tidally-induced spinup prior to merger\editremark{Ott}; we will assume the spin distribution to be uniform between $0.7$
-and $1$, independent of formation channel or birth conditions: \editremark{change: make this one Z dependent}
-\begin{eqnarray}
-p(\chi_{bh}) = \frac{1}{0.3} \theta(\chi_{bh}-0.7)\theta(1-\chi_{bh})
-\end{eqnarray}
-As discussed in \cite{popsyn-LowMetallicityImpact2-StarTrackRevised-2012},  the black hole mass distribution depends
-sensitively on the birth environment and coalescing binary formation channels; see their Tables 7 and 9 and their Figures 6,9, 11, and 13,
-reconstructing the BH mass from the reported chirp masses (red curves).  
-Omitting formation channels that predict implausibly high compact binary formation rates (their model A), the
-distribution of $m_{bh}$ in BH-NS binaries extends over a wide range.  As a first approximation, the BH mass
-distribution in BH-NS binaries does not depend on composition, favoring BH-NS binaries with relatively low BH masses
-$m_{bh}\lesssim 5-9 M_\odot$ independent of birth composition.  
-% \cite{2012ApJ...749...91F}  : physics of SN explosions used in these mechanisms. Rapid engine needed for mass gap, but
-% is there one? 
-% mc[m1_, m2_] := (m1 m2)^(3/5)/(m1 + m2)^(1/5)
-% Solve[mc[m1, 1.4] == 2.5]
-For simplicity, we will adopt a uniform mass distribution between $5$ and $9 M_\odot$:
-\begin{eqnarray}
-p(m_{bh}) = \frac{1}{4 M_\odot} \theta(m_{bh}-4 M_\odot)\theta(9 M_\odot-m_{bh})
-\end{eqnarray}
-
-% POINT: Include delay time: get examples of disruption fraction versus time
-
-\section{Results}
-\label{sec:results}
-
-\begin{verbatim}
-ACTION ITEMS AND STATUS
-
-* Result script looks good (\texttt{sfr\_to\_rate.py}).  Follow instructions
-
-** Modify script to include tidal disruption options for BHs
-
-** plot 'stanard' results for NS-NS
-
-** set scale to be physical units -- some ad-hoc factors used
-
-*
-
-* Do we get to different answers?  Are they different ENOUGH?
-
-** Overall event rate: different by 20\% between two types. Largely similar.
-   - plot versus z_exponent.  Is there a trend
-
-** mass-cut-dependent event rate -- will be more sensitive (e.g., if there
-  is a hard cutoff on some masses, as having no EM counterpart)
-
-* Aside: BBH distribution the most sensitive, but not relevant for EM followup
-\end{verbatim}
-
-\section{Conclusions}
-
-% POINT: Future directions
-
-\begin{acknowledgements}
-ROS acknowledges support from NSF award AST-1412449, via subcontract from the University of Wisconsin-Milwaukee.
-%
-JB acknolwedges support  from \editremark{writeme}
-\end{acknowledgements}
-
-\appendix
-\section{Binary evolution and spin-orbit misalignment}
-
-\editremark{ROS to do} -- find python/C code (Davide?) for simple MC; mine old resuts from startrack
-
-%% POINT: Other reference
-% 2014arXiv1401.3032W  - fallback details
-
-The progenitors of both components of a BH-NS binary undergo supernova, whose associated asymmetric mass loss and
-supernova kicks significantly perturb the orbit  \citep{2013PhRvD..87j4028G,2002MNRAS.329..897H,2000ApJ...541..319K}.   Assuming progeniror stellar spins are
-aligned with the orbital plane (e.g., due to strong tides), only asymmetric supernova kicks can change
-the orbital plane and introduce misalignment between the BH spin and the orbit.   The distribution of spin-orbit
-misalignments expected in any specific binary depends strongly on weakly-constrained binary evolution physics, the
-treatment of which is beyond the scope of this article.  Previous detailed calculations have reported on spin-orbit
-misalignment \citep{2010ApJ...719L..79F,2008ApJ...682..474B,2004PhRvD..69j2002G}.  That said, relatively simple order-of-magnitude calculations
-can explain the typical small misalignment angles expected among merging BH-NS binaries.
-% POINT: Small angle tilt forma (follows from simple considerations of angular momentum)
-Specifically, in the limit of a small supernova kick $\vec{v}_K$, the orbital plane  change by an angle $\theta \simeq \vec{v}_K \cdot
-\hat{z}/v_{orb}$ where $\hat{z}$ is the direction perpendicular to the (circular) orbital plane.  The black hole forms first and cannot
-significantly change its spin magnitude or direction through accretion; therefore the two supernovae kicks produced by
-forming the black hole and then neutron star add (in quadrature) to produce a characteristic RMS misalignment error
-$\E{\theta^2}$.
-%
-For simplicity, we will adopt the model used in the \texttt{StarTrack} binary evolution code \citep{StarTrack2}: binaries
-prior to each supernovae can be approximated as in circular orbits;  supernova kicks on neutron stars produce a Maxwellian
-distribution of velocities with 1d velocity dispersion $\sigma_v=265$ \citep{HobbsKicks};  supernova kicks on black holes
-$v_{bh}$ are suppressed by fallback, with velocities  $\vec{v}_{K,BH} = (1-f_b)v_{NS}$ suppressed by fallback accretion
-onto the black hole; and the dominant formation channels for BH-NS binaries involve common
-envelope accretion after the first supernova forms a black hole.   Combining these expressions under these assumptions, we expect the net misalignment  $\theta$ due to both supernova
-explosions will have zero mean and variance
-\begin{eqnarray}
-\label{eq:MisalignmentOrderOfMagnitude}
-\E{\theta^2} = \frac{\E{v^2}}{3}\left[ \frac{(1-f_b)^2\epsilon_1}{v_{orb,1}^2}+\frac{\epsilon_2}{v_{orb,2}^2} \right]
-\end{eqnarray}
-where $v_{orb,1}$ and $v_{orb,2}$ are the orbital velocities at the first and second supernova and where
-$\epsilon_1,\epsilon_2$ are factors between 0 and 1 which account for the fact that the average is taken over binaries which \emph{survive} and are not
-disrupted by the kick.  Because the second supernova  occurs in a tight orbit (post common
-envelope),  the orbital velocity $v_{orb,2}$ at the supernova producing the neutron
-star will be  large:  if $M_2$ and $r_2$ are the total mass and orbital separation, $v_{orb,2}=\sqrt{GM_{2}/r}\simeq
-440\unit{km/s} \sqrt{M/M_\odot/(r_2/R_\odot)}$, 
-% Convert[Sqrt[  GravitationalConstant (mbh SolarMass)/(r SolarRadius)], (Kilo Meter/    Second)]
-comparable to or
-significantly in excess of the typical supernova kick velocity for massive black holes orbiting the stripped progenitors of
-neutron stars at seperations of a few $R_\odot$.  Conversely, at birth the black hole will often capture a significant
-amount of the stellar envelope (``fallback'' accretion or prompt collapse) with $f_b\simeq 1$.  Therefore, even though
-the initial orbit is wide, orbital  velocity is very small, and hence the orbit can be easily strongly misaligned by
-supernova kicks,  the first kick when acting on a massive black hole can produce little to  modest amounts orbital
-misalignment.
-
-% POINT: Second term of order unity
-For exceptional models of binary evolution, the population of coalescing BH-NS binaries will depend extremely critically on the
-a finely-tuned second supernova.  In this case, only a small fraction of surviving BH-NS binaries merge; the BH-NS merger rate will be extremely low and  depend extremely sensitively on
-the magnitude of supernova kicks; and the misalignment produced by the second supernova can frequently be very large.  More typically, however, a significant fraction of surviving BH-NS binaries merge
-\citep{2008ApJ...675..566O,popsyn-LowMetallicityImpact2-StarTrackRevised-2012,popsyn-LowMetallicityImpact2b-StarTrackRevised-2013,popsyn-LowMetallicityImpact2c-StarTrackRevised-2014}; in these cases, the  second supernova's kick does not require fine-tuning to guarantee
-coalescence.   In these most common scenarios, the second term in Eq. (\ref{eq:MisalignmentOrderOfMagnitude}) is of
-order unity.
-
-% POINT:
-As a result, the process of surviving two supernova kicks generally produces a wide  distribution of misalignment
-angles concentrated near $\theta\simeq 0$.  This wide distribution is expected to be relatively robust.  Extremely wide
-distributions are disfavored kinematically and by the requirement that sufficiently many binaries survive to coalesce.
-Conversely, the width of the distribution is bounded below by the contribution from the second supernova kick.\footnote{For simplicity and brevity, we neglect the
-  possibility of different modes of supernova explosions and hence kicks, notably via electron capture supernovae \citep{2012ARNPS..62..407J,2004ApJ...612.1044P,2010MNRAS.406..656K,2015ApJ...801...32A}.
-That said, small supernova kicks in NS
-  birth would further minimize any spin-orbit misaligment and hence further favor the strong dependence of tidal disruption probability on the black hole mass and spin
-  distribution described in the text.} 
-As a first approximation,  the cumulative distribution of misalignment angles should agree with direct calculations \cite{2010ApJ...719L..79F,2008ApJ...682..474B,2004PhRvD..69j2002G}.
-
-% POINT: 
-%% To calculate the necessary inputs to this expression, we adopt one particular family of supernova mechanism:  Fryer et al 
-%% \cite{2012ApJ...749...91F}, the model adopted in \texttt{StarTrack} and applied in detailed calculations of binary
-%% evolution
-%% \cite{popsyn-LowMetallicityImpact2-StarTrackRevised-2012,popsyn-LowMetallicityImpact2b-StarTrackRevised-2013,popsyn-LowMetallicityImpact2c-StarTrackRevised-2014}.
-%% Because of significant residual uncertainty in the supernova mechanism, our results are proof-of-concept calculations
-%% intended to illustrate plausible effects of composition on remnant masses, spins, and hence misalignments.  Other models
-%% for supernovae produce dramatically different initial-final mass relations \cite{2012ApJ...757...69U} and are
-%% anticipated to produce equally different different amounts of spin-orbit
-%% misalignment in BH-NS binaries.  
-%% %
-%% Observations of isolated pulsar
-%% recoils \cite{1997MNRAS.291..569H,Ar} and binary pulsars \cite{psr-kicks-WongWillemsKalogera2010}
-%% strongly constrain the action of random supernova kicks on neutron stars.
-
-\section{Black hole spins in BH-NS binaries}
-
-* References: review in Fragos and McClintock \cite{2015ApJ...800...17F}  and references therein (LMXBs) -- low birth
-spins, because of stripped companions; for more on measurement, see \cite{2011CQGra..28k4009M}
-
-* References on BH spin versus mass: angular momentum capture in prompt collapse: O'Connor and Ott and references
-therein (note no fallback); note Ugliano has a differen result. See also Clausen et
-al (probability of BH vs mass) for more recent
-%O'Connor and Ott: a criteria for explosions http://arxiv.org/pdf/1010.5550v2.pdf...note they don't have fallback.
-%Clausen et al: trying to find formation probability vs mass http://arxiv.org/pdf/1406.4869v2.pdf (assuming no binaries)
-%...note also http://adsabs.harvard.edu/abs/2012ApJ...757...69U (which is complicated)
-
-%* References: \cite{2013ApJ...762..104S}
-
-\section{Outline }
-\begin{verbatim}
-
-Intro
-  -Important (edo/Brian)
-  - More important soon (LIGO; IFU's give detail)
-    because these galaxies are local and spatially resolved
-    at 400 Mpc distance
-  - The question: can we learn about things from detailed host galaxy 
-    observations, and if so what?
-    Obviously yes (cf. SN Ia, short GRB, etc)
-  - Specific questions of interest, particularly for BH-NS origin for short GRBs:
-    is there dependence of the event rate and BH mass on the source metallicity
-
-  - Not clear because of kicks, mixing
-  - Goal of paper: address this challenge via simulations
-
-Methods
-  - JB: specifically target two 'identical' MW galaxies (and their subhalo population)
-  - Postproces JB: rhodot; Z of star forming gas
-  - Model:
-      - predict present-day number (and mass distribution) by formula
-
-Results:
-  - Different histories which look the same now can produce different answers
-     - key issue: impact of past mergers
-  -
-
-Stuff to skip
-  - (spin-dependent) tidal disruption threshold: assume all BH-NS disrupt, for simplicity
-\end{verbatim}
-%1 Kilo Parsec/(400 Mega Parsec)
-%Convert[%, Milli ArcSecond] // N
-
-\section{Other discussion}
+\section{Formation rate for binary black holes}
+\label{sec:results:BBH}
 
@@
 
+\section{Conclusions}
+
+* BBH properties far from apparent.
+No surprise: delays can be long \cite{PSellipticals,popsyn-LowMetallicityImpact2b-StarTrackRevised-2013,gwastro-EventPopsynPaper-2016}, particularly because formation in low Z favored,
+so system changes significantly from assembly conditions
+
+* EM counterpart properties: delay times are shorter, so more of a surprise that formation scenario matters.  However,
+BH properties depend on $Z$, which can influence the mass and spin of BHs that produce EM counterparts.
+
+* Detailed analysis of one host galaxy presented in this work is complementary to the population-based approach used in
+\cite{2016arXiv160508783L}, which favored formation in a wide range of galaxies and event times.   % that analysis also
+                                % used a poor input from BSE, about the coalescence delay
+
+% POINT: Future directions
+
+\begin{acknowledgements}
+ROS acknowledges support from NSF award AST-1412449, via subcontract from the University of Wisconsin-Milwaukee.
+%
+JB acknolwedges support  from \editremark{writeme}
+\end{acknowledgements}
+
+\appendix
+
 \bibliography{bhmetals}

### 2016-07-11 paper/paper.tex
jillian edits, conclusion

@@
 \author{ J. Bellovary}
-\affiliation{Department of Physics and Astronomy, Vanderbilt University, Nashville TN 37235}
-\email{jillian.bellovary@vanderbilt.edu}
+\affiliation{Department of Physics, Queensborough Community College, Bayside, NY 11364}
+\email{jbellovary@qcc.cuny.edu}
 \begin{abstract}
@@
 
+We present a model for binary black hole \jillianremark {and other binary compact object formation?} based on models of binary formation and properties over cosmic time.
+We fold these models with star formation histories and metallicity distributions taken from state of the art cosmological simulations of Milky Way-like galaxies.
+We demonstrate that galaxies which appear similar at $z = 0$ but have differing merger histories will have different rates of BBH mergers detectable by LIGO.
+\jillianremark{sentence detailing the specifics of this prediction, once we know what it is.}
+
+One result of our conclusions is that we can learn about the past assembly history of a galaxy from its LIGO event rate, \jillianremark{ that's really cool.
+}  Also we can use resolved star formation histories of nearby galaxies {\bf (citations)} to predict likelihoods for LIGO events.
+\jillianremark { what else}\\
+
 * BBH properties far from apparent.
@@
 %
-JB acknolwedges support  from \editremark{writeme}
+JB acknowledges generous support  from the Helen Gurley Brown Trust.
 \end{acknowledgements}

### 2016-07-11 paper/paper.tex
Commit changes

@@
 
-\section{Model for compact binary formation}
+\section{Detection-weighted compact binary formation}
 \label{sec:model}
 
-Binary evolution calculations suggest the detection rate depends sensitively on the assumed metallicity, in conjuction
+To explore plausible binary detection scenarios, we adopt a parameterized formalism for binary evolution and event
+detection in an individual galaxy, motivated by
+the detailed studies of  \abbrvPSgrb{} and \abbrvPSellipticals; similar approaches have been used by
+\cite{2016arXiv160508783L} and others.
+
+Binary evolution calculations suggest the binary compact object formation rate rate depends sensitively on the assumed metallicity, in conjuction
 with other parameters \citep[see,\,e.g.][and references
-  therein]{popsyn-LowMetallicityImpact-Chris2008,popsyn-LIGO-SFR-2008}.\editremark{New dominik et al}
+  therein]{popsyn-LowMetallicityImpact-Chris2008,popsyn-LIGO-SFR-2008,gwastro-EventPopsynPaper-2016}.
 % POINT: 
@@
 %   - of course
-The detected population of compact binary mergers can further favor low-metallicity environments, e.g. through the total
-mass of merging binaries.
-\jillianremark{The previous sentence is confusing - rephrase?
-I have trouble with ``the detected population can further favor low-Z environments'' because that makes no sense.}
+Gravitational wave detectors are also far more sensitive to  massive compact binaries, as are  preferentially  formed in low metallicity
+environments \citep{PSellipticals,popsyn-LowMetallicityImpact2c-StarTrackRevised-2014}.  As a result, low metallicity
+environments can be overwhelmingly efficient factories for detectable black hole binaries
+\citep{popsyn-LowMetallicityImpact2c-StarTrackRevised-2014,gwastro-EventPopsynPaper-2016}.  
+%
+For this reason, our estimates for compact binary coalescence rates must account for how often  different star-forming
+conditions occur;  how often compact binaries that can coalesce now can  derive from each environment; and how often LIGO will detect compact
+binaries with different masses, all other things being equal.
+
+\begin{widetext}
+% POINT:  Model
+To characterize how much more likely LIGO will detect coalescing binaries with different masses, we use a common and
+naive estimate for the volume to which advanced LIGO is sensitive \citep[see,e.g.,][]{PSellipticals}:\footnote{For
+  simplicity, in this calculation we neglect the effects of cosmology; strong field coalescence; and black hole spin;
+  see \cite{popsyn-LowMetallicityImpact2c-StarTrackRevised-2014}, \cite{AstroPaper}, or \cite{RatesPaper} for more details.}
+\begin{eqnarray}
+V(m_1,m_2) = \frac{4\pi}{3} [445 \unit{Mpc}]^3 \int p(m_1,m_2|Z) dm_1 d,m_2 [ (\mc/1.2 M_\odot)^{5/6}]^3
+\end{eqnarray}
+This expression depends explicitly on an assumed and metallicity-dependent mass distribution for compact object
+mergers, through the characteristic chirp mass $\mc_{C}\equiv [\int p(m_1,m_2|Z) dm_1 d,m_2 (\mc/1.2
+  M_\odot)^{15/6}]^{5/16}$ .  We calibrate our metallicity-dependent mass distributions to metallicity-dependent binary
+evolution calculations presented in \cite{popsyn-LowMetallicityImpact2-StarTrackRevised-2012} and
+\cite{popsyn-LowMetallicityImpact2c-StarTrackRevised-2014}; see, e.g., their Table 1 and Figures 5-7.
+For neutron stars, we adopt a fiducial neutron star mass of $1.4 M_\odot$ at all metallicities.
+For black
+hole-neutron star binaries, we 
+For the metallicity-dependent where $p(m_1,m_2|Z)$
+
+% POINT:  Model
+To characterize how often different star-forming conditions occur, we use our simulations, which provide a galaxy's star formation rate
+$\dot{M}_*$ and star formation metallicity distribution $p(\log Z|t)$.
+
+% POINT: 
+To characterize how often compact binaries form and coalesc
+
 % POINT: Simple model to encompass all
-To explore plausible binary detection scenarios, we adopt a parameterized formalism for binary evolution and event detection, motivated by
-the detailed studies of  \abbrvPSgrb{} and \abbrvPSellipticals.  Specifically, we encapsulate all information about
+  Specifically, we encapsulate all information about
  binary evolution into two  parameterized response functions.  The funciton ${\cal G}(t| Z) =
@@
 due to any individual galaxy via the following formula 
-\begin{widetext}
 \begin{subequations}
@@
 \end{subequations}
-\end{widetext}
 In this expression, the galactic star formation rate
-$\dot{M}_*$ and star formation metallicity distribution $p(\log Z|t)$ are galaxy-dependent and drawn from our
+are galaxy-dependent and drawn from our
 simulations.   \editremark{rewrite this to be average chirp mass at a given metallicity}
 
+\end{widetext}
 We parameterize the response function ${\cal G}(t|Z)$ with two factors: (a) an overall efficiency $\lambda$ for forming

### 2016-07-11 paper/paper.tex
spellcheck

@@
 Recent simulations of compact binary evolution suggest the compact object merger rate depends
-sensitively on the progentior's metallicity, to the extent that rare low-metallicity star formation during galaxy
+sensitively on the progenitor's metallicity, to the extent that rare low-metallicity star formation during galaxy
 assembly can produce more detected compact binaries than typical star formation.   
@@
 The host galaxies of distant short GRBs have already been extensively investigated, with the associations being used to
-draw preliminary conclusions about their progentitors  \cite{2014ARAA..52...43B}.   
+draw preliminary conclusions about their progenitors  \cite{2014ARAA..52...43B}.   
 %Of necessity, these analyses  on bulk correlations, often stacked to increase significance across multiple sources
@@
   evolution of h258 and h277 also differ at early times.  Figure
-  \ref{fig:TwoGalaxies} shows the history of the mean metallicty of
+  \ref{fig:TwoGalaxies} shows the history of the mean metallicity of
   recently formed stars vs time (thick solid lines), where we define
   recent as within the past 50 Myr.  The shaded regions correspond to
-  one standard devation of the mean, while the thick dashed lines
+  one standard deviation of the mean, while the thick dashed lines
   represent the top and bottom 90\%.  We see that the early evolution
@@
 \caption{\label{fig:TwoGalaxies}\textbf{Star formation and metallicity versus time}:  \emph{Left panel}: Star formation history $\dot{M}_{*}$
-  versus time.  Black corresponds to galaxy A (``boring'') and red to gaalxy B (``exciting'').  
+  versus time.  Black corresponds to galaxy A (``boring'') and red to galaxy B (``exciting'').  
 \emph{Right panel}: A plot of the  metallicity $Z$ of recently-formed stars versus time.  Solid red and black lines show
@@
 merger of  near the peak of their
-star-forming history, newly-born stars are created with significantlydifferent metallicity.  Additionally, prior to the
+star-forming history, newly-born stars are created with significantly different metallicity.  Additionally, prior to the
 second major merger of galaxy B at $\simeq 6\unit{Gyr}$, stars form in the ``exciting'' galaxy at a systematically lower
@@
 
-Binary evolution calculations suggest the binary compact object formation rate rate depends sensitively on the assumed metallicity, in conjuction
+Binary evolution calculations suggest the binary compact object formation rate rate depends sensitively on the assumed metallicity, in conjunction
 with other parameters \citep[see,\,e.g.][and references
@@
 % POINT: 
-To characterize how often compact binaries form and coalesc
+To characterize how often compact binaries form and coalesce
 
@@
   Specifically, we encapsulate all information about
- binary evolution into two  parameterized response functions.  The funciton ${\cal G}(t| Z) =
+ binary evolution into two  parameterized response functions.  The function ${\cal G}(t| Z) =
 dN/dt dM_*$ describes how many mergers per unit initial mass occur after a time $t$ since a starburst,

### 2016-07-11 python/ParseStars.m
Adding parsers

@@ -1,0 +1,166 @@
+ (* $Id: ParseStars.m,v 1.6 2014-07-29 20:08:25 oshaughn Exp $
+*   Compare to AlbertoCatalogManager
+ *)
+
+<<MyTools`TypedList`
+<< AppliedStatistics`Nonparametric`PointsToDensity`KernelEstimators`
+<< AppliedStatistics`Nonparametric`PointsToDensity`WeightedKernelEstimators`
+$dirStarData = $dirROSProjs<>"/PSnucleosynthesis/Branch-GalaxyAssemblyAndZDistribution/Communications/2011-08-03-Jillian-StarData/";
+
+$dirStarDataMore = $dirROSProjs<>"/PSnucleosynthesis/Branch-GalaxyAssemblyAndZDistribution/bhmetals/";
+
+mapfunc = ParallelMap;
+
+<<MyUnits`UnitManager`;
+
+timeScale = 1.223 *10^18 Convert[Second/(Giga Year), 1]
+
+
+jillianCatalogLoad["Small"] := Module[{tmax,dat},
+ SetDirectory[$dirStarData];
+ dat = {#[[1]], #[[2]], Random[] }&/@ Drop[Import["starmetals.dat", "Table"], 1];
+ tmax = Max[dat[[All,-1]]];
+ StarGasCatalog @@ {"Type"-> "Jillian", "ExtractionRedshift"->4, "ExtractionTime"->tmax,
+    "Data"->dat
+ }
+]
+
+jillianCatalogLoad["Large"] := Module[{tmax,dat},
+ SetDirectory[$dirStarData];
+ dat = {#[[1]], #[[2]], #[[3]] timeScale}&/@ Drop[Import["starmetals.20110819.dat", "Table"], 1];
+ tmax = Max[dat[[All,3]]];
+ StarGasCatalog @@ {"Type"-> "Jillian", "ExtractionRedshift"->4, "ExtractionTime"->tmax,
+    "Data"->dat }
+];
+
+jillianCatalogLoad["Large","Movie", z_]/;MemberQ[{2, 2.4, 2.6, 3, 3.4, 4,5,6,8},z] := Module[{tmax,dat},
+ SetDirectory[$dirStarDataMore];
+ dat = {#[[1]], #[[2]], #[[3]] timeScale}&/@ Drop[Import["h258.z" <>ToString[z]<>".starmetal.dat.gz", "Table"], 1];
[…]

### 2016-07-11 python/ParseStars.py

@@ -1,0 +1,54 @@
+
+import numpy as np
+#import astropy
+from astropy.cosmology import WMAP9 as cosmo   # http://astropy.readthedocs.org/en/latest/cosmology/
+
+rosDebug =True
+
+jbTimeScale = 38.7811  #  = = 1.223*10^18 Convert[Second/(Giga Year), 1]
+jbStarMass =  26676*0.3
+jbGasMass = 26676.0  # Msun?
+
+class StarCatalog:
+    """
+    Class containing all information loaded from star output files.
+    """
+    def __init__(self, fname, z):
+        if rosDebug:
+            print "Loading ", fname,
+        # Data format: 
+        self.dat = np.loadtxt(fname)
+        self.z = float(z)
+        self.mass = len(self.dat)*jbStarMass  # I suspect this is wrong because I don't remember how to distinguish between gas        
+        if rosDebug:
+            print " ....finished, saved as z= ", z, " with log M = ", np.log10(self.mass)
+        # links, so no cost
+        self.Zs = self.dat[:,0]  # Star particle birth 
+        self.Zg = self.dat[:,1]  # Mean metallicity of nearest 32 particles
+        self.tb  = self.dat[:,2]  # time in Gyr.  Beware cosmology
+        # if rosDebug:
+        #     print  "    cosmo time ", cosmo.age(self.z), " versus max t in file ", np.max(self.tb)    # check time conversion and cosmology
+        self.weights = np.ones(len(self.dat))*1.0/len(self.dat)  # treat all particles equally
+
+    def time(self):
+        return cosmo.age(self.z)
+
+    def integrate(self,fn):   # fn takes 3 arguments: Zs, Zg, and t in Gyr
+        return np.sum(fn(self.Zs,self.Zg, self.tb)*self.weights)   # integrate an arbitrary expression of these quantities. Use for adding in time and Z dependent formation
+
+
+def cumulative_P(vals):
+    vals_sorted = np.sort(np.copy(vals))
+    P = np.arange(len(vals))*1.0/len(vals)
+    return vals_sorted,P
+
+def cumulative_P_weighted(vals, wts):
+    idx_sorted_util  = np.lexsort((np.arange(len(vals)), vals))
+    vals_sorted  = np.array([vals[k] for k in idx_sorted_util])
+    wts  = np.array([wts[k] for k in idx_sorted_util])
+    cum_wts = np.cumsum(wts)
+    cum_wts = cum_wts/cum_wts[-1]
+
+    return vals_sorted, cum_wts
+    
+

### 2016-07-11 python/sfr_to_rate_nobins_BBH.py
BBH code

@@ -1,0 +1,63 @@
+#! /usr/bin/env python
+#  sfr_to_rate_nobins.py 
+#  GOAL
+#      Take SFR history and spit out an event rate, using different response functions
+#      --time-exponent 0   : use uniform in time, starting after 10 Myr and running to 
+#      --time-exponent 1   : use 1/t delay time, start (DEFAULT)
+#      --time-max    100    : time max in Gyr for response function (DEFAULT).  If time-exponent<1, time-max=10Gyr
+# 
+#      --starmetal-file
+#      --Z-exponent 0
+#
+#  USAGE
+#    python sfr_to_rate_nobins.py --starmetal-file ~/PersonalJBArchive/boring-galaxy/z0.016.starmetal.dat --Z-exponent 2
+#    python sfr_to_rate_nobins.py --starmetal-file ~/PersonalJBArchive/boring-galaxy/z0.016.starmetal.dat
+#
+# PLOTS
+#    Third plot is money plot: shows you where the mergers are coming from, for different exponent choices.
+
+import numpy as np
+
+import bisect
+from scipy.interpolate import griddata
+
+import ParseStars
+
+import argparse
+parser = argparse.ArgumentParser()
+parser.add_argument("--starmetal-file", default=None)
+parser.add_argument("--time-exponent",default=1,type=float)
+parser.add_argument("--Z-exponent",default=0,type=float)
+opts = parser.parse_args()
+if not opts.starmetal_file:
+    print "  Please specify an SFR file "
+
+
+# SFR files:
+#    - not guaranteed to have same # per Z bin ! 
+dat = np.loadtxt(opts.starmetal_file,skiprows=1)
+# format of this file: 3 columns, star metallicity, nearby gas metallicity, formation time of star
+lambda0 = 1e-3
+
+
+def BBH_function(arg):
+    # we will add something real here
+    return 1.0
+
+def metal_function(z_exp):
+    # number of merging compact binaries in a starburst depends on metallicity
+    return np.minimum(np.power((1e-8+dat[:,0])/0.02,-1.*z_exp), 1e3*np.ones(len(dat)))
+
+def time_function(time_exp):
+    # where does this come from?
+    return 1./np.power(0.01+dat[:,2], time_exp)
+
+if opts.Z_exponent:
+    # print a specific value
[…]

### 2016-07-11 paper/paper.tex
Updating paper text

@@
 \end{eqnarray}
+where $\mc\equiv (m_1 m_2)^{3/5}/(m_1+m_2)^{1/5}$.   
 This expression depends explicitly on an assumed and metallicity-dependent mass distribution for compact object
@@
 evolution calculations presented in \cite{popsyn-LowMetallicityImpact2-StarTrackRevised-2012} and
-\cite{popsyn-LowMetallicityImpact2c-StarTrackRevised-2014}; see, e.g., their Table 1 and Figures 5-7.
-For neutron stars, we adopt a fiducial neutron star mass of $1.4 M_\odot$ at all metallicities.
-For black
-hole-neutron star binaries, we 
-For the metallicity-dependent where $p(m_1,m_2|Z)$
+\cite{popsyn-LowMetallicityImpact2c-StarTrackRevised-2014}; see, e.g., their Table 1 and Figures 5-7.    For neutron
+stars, we adopt a fiducial neutron star mass of $1.4 M_\odot$ at all metallicities.  For BH-NS binaries, we adopt a
+highly simplified model: the black hole masses are uniformly \editremark{fixme?} drawn from $5 M_\odot$ to the maximum mass allowed by
+\emph{isolated} stellar evolution, as reported in prior work \citep[see,e.g.][and references
+  therein]{gwastro-EventPopsynPaper-2016}.
+In agreement with much more detailed prior work \cite{popsyn-LowMetallicityImpact2c-StarTrackRevised-2014}, this simplified model yields typical chirp masses for BH-NS binaries that
+vary slightly as $Z/Z_\odot$ decreases, from a lower limit of $3 M_\odot$ near solar metallicity to an upper limit of
+$4.3 M_\odot$ in low-metallicity environments.  Finally, for binary black holes, we assume only comparable-mass binaries
+form, with  component masses drawn from
 

### 2016-07-11 python/maxmass.py
find average chirp mass as a function of metallicity using max mass relation

@@ -1,0 +1,76 @@
+import numpy as np
+import matplotlib.pyplot as plt
+from scipy.interpolate import interp1d
+import scipy.interpolate as interpol
+
+
+metals,maxbh = np.loadtxt("mass_max_of_z.dat",unpack=True)
+
+print metals
+print maxbh
+
+metalgrid = np.linspace(min(metals),max(metals),1000)
+
+
+f = interpol.interp1d(metals,maxbh)
+maxmassgrid = f(metalgrid)
+
+"""
+plt.plot(metals,maxbh)
+plt.xlabel("metals")
+plt.ylabel("max BH mass")
+plt.show()
+### ok we are good with the interp. ###
+"""
+
+input_metal = 0.1
+sigma = 5.0
+"""thismetal = np.abs(metalgrid - input_metal).argmin()
+print thismetal
+place = thismetal #np.where(metalgrid == thismetal)
+print place
+maxmass = maxmassgrid[place]
+print maxmass"""
+
+
+def probability(input_metal,sigma):
+    place = np.abs(metalgrid - input_metal).argmin()
+    maxmass = maxmassgrid[place]
+    print place,maxmass
+    prob = np.exp(-np.power(maxmassgrid-maxmass,2.0) / (2*np.power(sigma,2.)))
+    return prob
+
+dist = probability(input_metal,sigma)
+
+"""plt.plot(maxmassgrid,dist)
+plt.xlabel("BH mass")
+plt.ylabel("probability")
+plt.title(" input metallicity of "+str(input_metal))
+plt.show()                
+"""
+
+def make_uniform_func(metal_now):
+    MmaxNow = f(metal_now)
+    print MmaxNow
+    nm = 1./(MmaxNow - 3)  # normalization
+    return lambda x, Nm = nm, A = MmaxNow: np.where( np.logical_and(x<A , x > 3), nm* np.ones(len(x)), np.zeros(len(x)))
+
+
+prob_function = make_uniform_func(0.1) # input is a metallicity
+newmassgrid = np.linspace(0,100,50)
+#print np.logical_and(newmassgrid < 80 , newmassgrid > 3)
+p = prob_function(newmassgrid)
+plt.plot(newmassgrid,p)
+#print p
+plt.show()
+
+
+import scipy
+def average_mass(input_probability_distribution):
+    masses = np.linspace(0,100,50)
+    prob = input_probability_distribution(masses)
[…]

### 2016-07-11 python/maxmass.py
cleaning up

@@ -6,8 +6,8 @@ import scipy.interpolate as interpol
 
 metals,maxbh = np.loadtxt("mass_max_of_z.dat",unpack=True)
 
-print metals
-print maxbh
+#print metals
+#print maxbh
 
 metalgrid = np.linspace(min(metals),max(metals),1000)
 
@@ -36,7 +36,7 @@ print maxmass"""
 def probability(input_metal,sigma):
     place = np.abs(metalgrid - input_metal).argmin()
     maxmass = maxmassgrid[place]
-    print place,maxmass
+    #print place,maxmass
     prob = np.exp(-np.power(maxmassgrid-maxmass,2.0) / (2*np.power(sigma,2.)))
     return prob
 
@@ -51,7 +51,7 @@ plt.show()
 
 def make_uniform_func(metal_now):
     MmaxNow = f(metal_now)
-    print MmaxNow
+    #print MmaxNow
     nm = 1./(MmaxNow - 3)  # normalization
     return lambda x, Nm = nm, A = MmaxNow: np.where( np.logical_and(x<A , x > 3), nm* np.ones(len(x)), np.zeros(len(x)))
 
@@ -72,5 +72,5 @@ def average_mass(input_probability_distribution):
     result = scipy.integrate.simps(prob*np.power(masses, 15./6), masses)
     return np.power(result, 6/15.)
 
-thing = average_mass(prob_function)
-print thing
+the_answer = average_mass(prob_function)
+print "the mean mass for the metallicity",input_metal, " is" ,the_answer

### 2016-07-11 python/maxmass.py
cleaning up

@@ -56,7 +56,7 @@ def make_uniform_func(metal_now):
     return lambda x, Nm = nm, A = MmaxNow: np.where( np.logical_and(x<A , x > 3), nm* np.ones(len(x)), np.zeros(len(x)))
 
 
-prob_function = make_uniform_func(0.1) # input is a metallicity
+prob_function = make_uniform_func(input_metal) # input is a metallicity
 newmassgrid = np.linspace(0,100,50)
 #print np.logical_and(newmassgrid < 80 , newmassgrid > 3)
 p = prob_function(newmassgrid)

### 2016-07-11 python/maxmass.py
comments

@@ -1,8 +1,12 @@
+##  this code does the following:
+##  read in table of max BH mass vs metals
+##  interpolate this data
+##  makes a uniform probability function of mass for a given metallicity
+##  calculates the average chirp mass for this metallicity
+
 import numpy as np
 import matplotlib.pyplot as plt
 from scipy.interpolate import interp1d
-import scipy.interpolate as interpol
-
 
 metals,maxbh = np.loadtxt("mass_max_of_z.dat",unpack=True)
 
@@ -24,7 +28,7 @@ plt.show()
 """
 
 input_metal = 0.1
-sigma = 5.0
+#sigma = 5.0
 """thismetal = np.abs(metalgrid - input_metal).argmin()
 print thismetal
 place = thismetal #np.where(metalgrid == thismetal)
@@ -32,7 +36,7 @@ print place
 maxmass = maxmassgrid[place]
 print maxmass"""
 
-
+"""
 def probability(input_metal,sigma):
     place = np.abs(metalgrid - input_metal).argmin()
     maxmass = maxmassgrid[place]
@@ -42,7 +46,7 @@ def probability(input_metal,sigma):
 
 dist = probability(input_metal,sigma)
 
-"""plt.plot(maxmassgrid,dist)
+plt.plot(maxmassgrid,dist)
 plt.xlabel("BH mass")
 plt.ylabel("probability")
 plt.title(" input metallicity of "+str(input_metal))

### 2016-07-11 paper/paper.tex
Updating

@@
 \begin{eqnarray}
-V(m_1,m_2) = \frac{4\pi}{3} [445 \unit{Mpc}]^3 \int p(m_1,m_2|Z) dm_1 d,m_2 [ (\mc/1.2 M_\odot)^{5/6}]^3
+V = \frac{4\pi}{3} [445 \unit{Mpc}]^3 \int p(m_1,m_2|Z) dm_1 dm_2 [ (\mc/1.2 M_\odot)^{5/6}]^3
 \end{eqnarray}
@@
 This expression depends explicitly on an assumed and metallicity-dependent mass distribution for compact object
-mergers, through the characteristic chirp mass $\mc_{C}\equiv [\int p(m_1,m_2|Z) dm_1 d,m_2 (\mc/1.2
+mergers, through the characteristic chirp mass $\mc_{*}(Z)\equiv [\int p(m_1,m_2|Z) dm_1 d,m_2 (\mc/1.2
   M_\odot)^{15/6}]^{5/16}$ .  We calibrate our metallicity-dependent mass distributions to metallicity-dependent binary
@@
 stars, we adopt a fiducial neutron star mass of $1.4 M_\odot$ at all metallicities.  For BH-NS binaries, we adopt a
-highly simplified model: the black hole masses are uniformly \editremark{fixme?} drawn from $5 M_\odot$ to the maximum mass allowed by
+highly simplified model: the black hole masses are uniformly \editremark{fixme?} drawn from $5 M_\odot$ to the maximum
+black hole mass $M_{max}(Z)$ allowed by
 \emph{isolated} stellar evolution, as reported in prior work \citep[see,e.g.][and references
@@
 vary slightly as $Z/Z_\odot$ decreases, from a lower limit of $3 M_\odot$ near solar metallicity to an upper limit of
-$4.3 M_\odot$ in low-metallicity environments.  Finally, for binary black holes, we assume only comparable-mass binaries
-form, with  component masses drawn from
+$4.3 M_\odot$ in low-metallicity environments.  Finally, for binary black holes, we assume  comparable-mass binaries
+form ($m_1=m_2$), with the distribution of component masses chosen to be $\propto m_1^{-p}$ 
+ with $p=2$ between $3 M_\odot$ and $M_{max}(Z)$ and zero otherwise; see, e.g.,
+\cite{popsyn-LowMetallicityImpact2b-StarTrackRevised-2013}.    For binary black holes, this means  the
+detection-weighted mass distribution [$\propto p(m_1,m_2)
+\mc^{15/6}$] depends weakly on mass [$ p(m_1,m_2)
+\mc^{15/6} \propto m_1^{-0.5} \delta(m_1-m_2)$.  In our simple model, the total  and chirp mass
+distributions   are qualitatively consistent with detailed  binary evolution calculations \citep{popsyn-LowMetallicityImpact2b-StarTrackRevised-2013}.
+
+\end{widetext}
 
@@
 % POINT: 
-To characterize how often compact binaries form and coalesce
-
-% POINT: Simple model to encompass all
-  Specifically, we encapsulate all information about
- binary evolution into two  parameterized response functions.  The function ${\cal G}(t| Z) =
-dN/dt dM_*$ describes how many mergers per unit initial mass occur after a time $t$ since a starburst,
-given ambient metallicity $Z$.  The function $p(m_1,m_2|Z)$ is a metallicity-dependent mass distribution for binaries
-formed in a metallicity $Z$.
-%
-Finally, we account for the substantially increased sensitivity of gravitational wave detectors to binaries of larger
-chirp mass $\mc=(m_1 m_2)^{3/5}/(m_1+m_2)^{1/5}$; see \abbrvPSellipticals.
-%
-In terms of this response function, we can therefore calculate the relative contribution to the LIGO  event rate $r_D$
-due to any individual galaxy via the following formula 
-\begin{subequations}
-\label{eq:RatePerGalaxy}
-\begin{eqnarray}
-r_D  &\equiv& \int^{0}_{-T_{univ}} dt' d\log Z  \, [\dot{M}_*(t') p(\log Z|t) ] \times \; {\cal G}(0-t' | Z)  
- [\int d\mc p(\mc|Z) (\mc/1.2 M_\odot)^{15/6}]
-%\\
-%% {\cal R}(z)&\equiv &  \int dx {\cal R} p(z)
-\end{eqnarray}
-\end{subequations}
-In this expression, the galactic star formation rate
-are galaxy-dependent and drawn from our
-simulations.   \editremark{rewrite this to be average chirp mass at a given metallicity}
-
-\end{widetext}
-We parameterize the response function ${\cal G}(t|Z)$ with two factors: (a) an overall efficiency $\lambda$ for forming
-binaries;  and (b) a
-cumulative delay time distribution $P_t(<t|Z)$, describing the fraction of binaries born at $t=0$ that merge in less
-than time $t$ from a population of binaries $Z$:\footnote{For simplicity, we assume the mass and delay time
+To characterize how often compact binaries form and coalesce, we use the ansatz adopted in \abbrvPSellipticals{} and
+\abbrvPSgrb{}: for a star-forming parcel of mass $\Delta M$ the number of binaries born at time $0$ which
+are coalescing now is $\lambda \Delta M dP/dt$, where $\lambda$ is an overall efficiency per unit mass and $P(<t|Z)$ is
+a metallicity-dependent delay time distribution.\footnote{For simplicity, we assume the mass and delay time
   distributions are uncorrelated.  Figure A9 in \abbrvPSgrb{} shows this approximation, while not strictly true, is an
   excellent approximation for merging BH-BH binaries at solar metallicity.  }
-\begin{eqnarray}
-G(t,x|Z) &=& \lambda(Z) p_x(x|Z) \frac{dP_t}{dt}(t) 
-\end{eqnarray}
-Previous studies suggest the number of merging compact binaries $\lambda \delta M_*$ produced by a starburst depends
-as a power law on metallicity:
+    In this paper we only investigate the relative contribution of
+different star-forming environments, not the overall normalization, so the overall scale of $\lambda$ is irrelevant.  
+However, to account for the strong tendency of low-metallicity star-forming regions to produce many binary compact
+objects, we adopt a power law
 \begin{eqnarray}
@@
 %$\lambda_o F_{max} < 3\times 10^{-4}/M_\odot$
- (see, e.g.\cite{popsyn-LIGO-SFR-2008}, \abbrvKBLowZa).
-In this paper we only investigate the dependence of rates with metallicity; we therefore  adopt 
-\[
-\lambda_0 = 10^{-3}/M_\odot
-\]
-as a typical value for neutron star compact binaries (see \abbrvPSgrb{}, \abbrvPSellipticals, and \abbrvKBLowZa).
+ (see, e.g.\cite{popsyn-LIGO-SFR-2008}, \abbrvKBLowZa).  For the purposes of illustration, we adop a  concrete scale
+factor  $
+\lambda_0 = 10^{-3}/M_\odot $,  a typical value suitable for neutron star compact binaries (see \abbrvPSgrb{}, \abbrvPSellipticals, and \abbrvKBLowZa).
 %
-
-For binaries containing neutron stars, for simplicity we adopt the universal delay time distribution
+For binaries containing neutron stars, for simplicity and without loss of generality we adopt the universal delay time distribution
 %% Finally, we parameterize the delay time distribution by  either
@@
 For binary black holes formed near solar metallicity, the delay time distribution can favor long delays between birth
-and merger, as demonstrated in \abbrvPSellipticals{}.
-
-Figure 2 of  \cite{2016arXiv160508783L} is an extreme example of this well-known trend
-
-\editremark{Note}:
+and merger, as demonstrated in Figures 9 and 10 of \abbrvPSellipticals{}.  [Figure 2 of  \cite{2016arXiv160508783L} is
+  an extreme example of this well-known trend.]  In practice, however, binary black holes produced near solar
+metallicity correspond to a relatively small proportion of the overall population; we therefore neglect this
+effect \footnote{may want to change}.
 

### 2016-07-11 paper/paper.tex
Adding sentence
Section 5 sucks less

@@
 
+% POINT: Net effect
+Therefore, up to an irrelevant overall scale factor, the  present-day detection-weighted coalescence rate $r_D$  of binary compact objects formed by within two similar
+galaxies  can be calculated via
+\begin{eqnarray}
+ r_D \propto  \int d\log Z  \int _{13 \unit{Gyr}}^0dt  V(Z) \lambda(Z) \frac{dP}{dt}(t) \dot{M} p(\log Z|t)
+\end{eqnarray}
+
 \section{Formation rate for binary black holes}
@@
 
-% POINT: Observations provide sample of extragalactic  binaries at merger, and  host galaxies.  Possible to mine large archive of events
-% to deduce correlations
-
-On the one hand,  relatively few formation scenarios will correctly reproduce the observed mass and spin distributions
-\citep{2004MNRAS.352.1372B,2003ApJ...589L..37B,gwastro-Ilya-ConfProc-NRDA-2010}.  
-% POINT: Value of associations
-%% Green's function connecting the merger
-%% rate $dN/dt$ to the star formation rate host galaxy star formation history and metallicity,
-%% both the delay time distribution and correlation any preference for different metallicities can be determined
-On the other hand, each host galaxy associates a merger to a unique star formation history and metallicity distribution.
-With many events, these associations can potentially determine the ``response function'' for compact binaries: how often star forming gas of a given metallicity evolves into
-merging compact binaries;  see, e.g., studies of
-
+Our calculations suggest that because of the often-long delays between formation and merger, combined with the
+propensity of low-metallicity gas to play an exceptionally significant role, unusually detailed information about each host galaxy could be required to realize the full
+potential of  associations between gravitational wave sources and their candidate host galaxies.
 %
-Highly atypical formation scenarios seemingly should produce events in or near atypical hosts.  
-% POINT: Introduce *idea* of comparison: refs for mass-metallicity relation
-For example, in the local universe galaxies lie along mass-metallicity  (\cite{2004ApJ...613..898T}; see also
-\cite{sfr-ZEvolution-ByGalaxy-Panter2008})
-or mass-metallicity-star formation rate  correlations (e.g., \cite{2010MNRAS.408.2115M}).
-% POINT: Evolution tricky
-[The change in these correlations with redshift is still being investigated; see, e.g., \editremark{citation: Panter;
-    Mannucci; }, \cite{2011ApJ...739....1L} and references therein.]
-% POINT: previous studies
-Based on these correlations, both short  and long GRBs seem to arise from
-relatively typical hosts at their redshift; see, e.g., \cite{grb-short-Hosts-Berger2008} and \cite{grb-long-HostMetallicityVsTrend-Mannucci2010}.
-
-%  - Host associations: lots of information
-Host galaxy associations provide rich information about a transient's present and past environment.
-%
-For example, in several cases the metallicity of gas neighboring a long GRB (\citet{ 2008AJ....135.1136M}; \citet{2010AJ....140.1557L}
-\editremark{links}), short GRB (\editremark{XXX}), or SN has been directly measured.
-%
-The precise host offset can be compared to the distribution of light and star formation  \citep{2010ApJ...708....9F}.
-%
-Finally,  on a host-by-host basis, the delay time between birth and merger has been constrained for long GRBs (\editremark{XXX}), short GRBs \citep{2010ApJ...725.1202L}, and
-  SN Ia \citep{2011MNRAS.412.1508M}.
-%
-
-Biases towards low-metallicity star formation have been extensively studied in the context of long GRBs and their host galaxies.
-%
-For example, \cite{2009ApJ...702..377K} demonstrated that a sufficiently strong bias towards low-metallicity star formation would predict
-most  events in the local universe occur low-mass and dwarf galaxies.
-%<
-For less extreme metallicity biases, subsequent calculations by  \citet{2011MNRAS.417..567N} demonstrated that the
-metallicity distribution within galaxies will usually lead to events in a wide range of host galaxies in the local universe.
-
-\subsection{Local metallicity measurements?}
-To this point, we have emphasized \emph{global} measurements of the galactic star formation history.  With the advent of
+Fortunately,  with the advent of
 IFUs and position-resolved spectroscopy, observers can now probe the star formation history and metallicity of
@@
 These highly-detailed probes will be essential tools to develop a comprehensive model of the galaxy's merger and
-chemical evolution history.  That said, the metallicity of stars and gas adjacent to a specific merger event provides
+chemical evolution history.
+
+Even when electromagnetic counterparts are available, the long delay times between coalescence and merger  limit
+the prospects of detailed electromagnetic followup of individual event. 
+The metallicity of stars and gas adjacent to a specific merger event provides
 few direct, unambiguous clues to a compact binary merger's progenitors.  
@@
 %
+
+% POINT: 
+Despite the challenges involved in obtaining sufficient statistics, possibly requiring third-generation instruments to
+obtain sufficiently many associations, past experience suggests  host galaxy associations
+will provide unique clues into the formation mechanism of compact binaries.
+% 
+Each host galaxy associates a merger to a unique star formation history and metallicity distribution.
+With many events, these associations can potentially determine the ``response function'' for compact binaries: how often star forming gas of a given metallicity evolves into
+merging compact binaries.    
+%
+For example, in several cases the metallicity of gas neighboring a long GRB (\citet{ 2008AJ....135.1136M}; \citet{2010AJ....140.1557L}
+\editremark{links}), short GRB (\editremark{XXX}), or SN has been directly measured.
+%
+The precise host offset can be compared to the distribution of light and star formation  \citep{2010ApJ...708....9F}.
+%
+Finally,  on a host-by-host basis, the delay time between birth and merger has been constrained for long GRBs (\editremark{XXX}), short GRBs \citep{2010ApJ...725.1202L}, and
+  SN Ia \citep{2011MNRAS.412.1508M}.  
+%
+The future of gravitational wave host galaxy associations is bright.
+
+% POINT: Observations provide sample of extragalactic  binaries at merger, and  host galaxies.  Possible to mine large archive of events
+% to deduce correlations
+
+%% %
+%% Highly atypical formation scenarios seemingly should produce events in or near atypical hosts.  
+%% % POINT: Introduce *idea* of comparison: refs for mass-metallicity relation
+%% For example, in the local universe galaxies lie along mass-metallicity  (\cite{2004ApJ...613..898T}; see also
+%% \cite{sfr-ZEvolution-ByGalaxy-Panter2008})
+%% or mass-metallicity-star formation rate  correlations (e.g., \cite{2010MNRAS.408.2115M}).
+%% % POINT: Evolution tricky
+%% [The change in these correlations with redshift is still being investigated; see, e.g., \editremark{citation: Panter;
+%%     Mannucci; }, \cite{2011ApJ...739....1L} and references therein.]
+%% % POINT: previous studies
+%% Based on these correlations, both short  and long GRBs seem to arise from
+%% relatively typical hosts at their redshift; see, e.g., \cite{grb-short-Hosts-Berger2008} and \cite{grb-long-HostMetallicityVsTrend-Mannucci2010}.
 
@@
 
+Biases towards low-metallicity star formation have been extensively studied in the context of long GRBs and their host galaxies.
+%
+For example, \cite{2009ApJ...702..377K} demonstrated that a sufficiently strong bias towards low-metallicity star formation would predict
+most  events in the local universe occur low-mass and dwarf galaxies.
+%<
+For less extreme metallicity biases, subsequent calculations by  \citet{2011MNRAS.417..567N} demonstrated that the
+
 % POINT: Future directions

### 2016-07-11 python/sfr_to_rate_nobins_BBH.py
changes

@@ -52,6 +52,7 @@ def time_function(time_exp):
     # where does this come from?
     return 1./np.power(0.01+dat[:,2], time_exp)
 
+
 if opts.Z_exponent:
     # print a specific value
     weights = metal_function(opts.Z_exponent) * time_function(opts.time_exponent)*BBH_function(1.0)

### 2016-07-11 paper/paper.tex
section 3 comments jillian

@@
 \usepackage{ifpdf}
+\usepackage[normalem]{ulem}
 %\usepackage{eps2pdf}
@@
 %
-The host galaxies of gravitational wave sources will identified, either directly or statistically.  
+The host galaxies of gravitational wave sources will be identified, either directly or statistically.  
 On the one hand, addition to the strong gravitational wave signal, mergers of neutron stars are expected to  frequently be accompanied by detectable
@@
 (SPH) $N$-body simulations of Milky Way-like galaxies with GASOLINE
-\citep{2001PhDT........21S,2004NewA....9..137W}.  These simulations allow us to analyze both
+\citep{Stadel01,Wadsley04}.  These simulations allow us to analyze both
 spatially and temporally resolved star formation, and determine not
@@
 simulation has been previously discussed by
-\citet{2009MNRAS.398..312G,2010ApJ...721L.148B,2011ApJ...742...13B,2011ApJ...728...51B}; however we have
+\citet{Governato09,Bellovary10,Bellovary11,Brooks11}; however we have
 re-run the simulation at a factor of two higher in spatial resolution
 and additionally included new physics including a prescription for
-cooling by molecular hydrogen \citet{2012MNRAS.425.3058C}.
+cooling by molecular hydrogen \citet{Christensen12}.
 
@@
 uniform resolution, and resampled the region at very high
-resolution using the volume renormalization technique \citep{1993ApJ...412..455K}.
+resolution using the volume renormalization technique \citep{Katz93}.
 This technique allows us to follow the detailed physical processes
@@
 WMAP3 cosmology \citep{WMAP} and model the ionizing UV background
-with the prescription from \citet{1996ApJ...461...20H}.  Stars form
+with the prescription from \citet{Haardt96}.  Stars form
 probabilistically from gas particles which meet density ($n_{min} =
@@
 particle (representing a simple stellar population with a Kroupa IMF
-\citep{2001MNRAS.322..231K}) which is given by
+\citep{Kroupa01}) which is given by
 
@@
 blastwave formalism described in \citet{1977ApJ...218..148M} and implemented in
-our simulations as in \citet{2006MNRAS.373.1074S}.  Each supernova releases
+our simulations as in \citet{Stinson06}.  Each supernova releases
 $E_{SN} = 10^{51}$ erg into the surrounding gas with a radius
@@
 number of observed relations such as the mass-metallicity relation
-\citep{2007ApJ...655L..17B}, the Tully-Fisher relation \citep{2009MNRAS.398..312G}, and
-the size-luminosity relation \citep{2011ApJ...728...51B}, as well as reproduce
+\citep{Brooks07}, the Tully-Fisher relation \citep{Governato09}, and
+the size-luminosity relation \citep{Brooks11}, as well as reproduce
 the detailed characteristics of bulgeless dwarf galaxies
-\citep{2010Natur.463..203G} and the Milky Way \citep{2011ApJ...742...76G}.
+\citep{Governato10} and the Milky Way \citep{2011ApJ...742...76G}.
 
 Also included in our simulations is a scheme for turbulent metal
-diffusion \citep{2010MNRAS.407.1581S}.  Metals are created in supernova explosions
+diffusion \citep{Shen10}.  Metals are created in supernova explosions
 and deposited directly to the gas within the blast radius.  Stellar
@@
 supernova.  We follow metal enrichment from both Type II and Type 1a
-supernova, with metal yields derived from \citet{1993PhR...227...65W} and
-\citet{1986A&A...158...17T} respectively.  From this point onwards metals
+supernova, with metal yields derived from \citet{Weaver93} and
+\citet{Thielemann86} respectively.  From this point onwards metals
 diffuse through the surrounding gas, according to 
@@
 %
-where the diffusion paremeter $D$ is given by
+where the diffusion parameter $D$ is given by
 %
@@
 We identify individual galaxies using the halo finder $AHF$
-\citep{2004MNRAS.351..399G,2009ApJS..182..608K}, which identifies halos based on an
-overdensity criterion for a flat universe \citep{1997PhDT........14G}.  For this
+\citep{Gill04,Knollman09}, which identifies halos based on an
+overdensity criterion for a flat universe \citep{Gross97}.  For this
 work, we are focusing on the primary (i.e. most massive) galaxy at any
@@
 properties, including stellar dynamics
-\citep{2012ApJ...758L..23L,2014ApJ...794..151L,2014ApJ...790...89K}, baryon fraction
-\citep{2013ApJ...766...56M}, halo properties \citep{2009ApJ...702.1058Z,2010ApJ...721..738Z}, and
-disk properties \citep{2011ApJ...728...51B}.  It has a virial mass of $M_{vir} =
+\citep{Loebman12,Loebman14,2014ApJ...790...89K}, baryon fraction
+\citep{Munshi13}, halo properties \citep{Zolotov09,Zolotov10}, and
+disk properties \citep{Brooks11}.  It has a virial mass of $M_{vir} =
 6.79 \times 10^{11} \msun$, stellar mass $M_* = 4.24 \times 10^{10}
@@
   a gas disk rapidly reforms following the collision (see
-  \citet{2009MNRAS.398..312G}), resulting in a massive disk galaxy at $z = 0$
+  \citet{Governato09}), resulting in a massive disk galaxy at $z = 0$
   which looks remarkably similar to the Milky Way and to the other
@@
 \includegraphics[width=\columnwidth]{Figures/exciting}
-\caption{\textbf{Two fiducial galaxies}
+\caption{Synthetic SDSS $gri$ images of our two Milky Way-type galaxies, h277 (left) and h258 (right), created with \textsc{SUNRISE} \citep{Jonsson06}.
+\label{fig:images}
 }
@@
 detection in an individual galaxy, motivated by
-the detailed studies of  \abbrvPSgrb{} and \abbrvPSellipticals; similar approaches have been used by
+the detailed studies of  \abbrvPSgrb{} and \abbrvPSellipticals; \jillianremark{this is first mention of PSG and PSE, define} similar approaches have been used by
 \cite{2016arXiv160508783L} and others.
@@
 %   - of course
-Gravitational wave detectors are also far more sensitive to  massive compact binaries, as are  preferentially  formed in low metallicity
+Gravitational wave detectors are also far more sensitive to  massive compact binaries, \sout{as}  \jillianremark{ which?} are  preferentially  formed in low metallicity
 environments \citep{PSellipticals,popsyn-LowMetallicityImpact2c-StarTrackRevised-2014}.  As a result, low metallicity
@@
 For this reason, our estimates for compact binary coalescence rates must account for how often  different star-forming
-conditions occur;  how often compact binaries that can coalesce now can  derive from each environment; and how often LIGO will detect compact
+conditions occur;  how often compact binaries that can coalesce now \jillianremark{\sout{can}}  derive from each environment; and how often LIGO will detect compact
 binaries with different masses, all other things being equal.
@@
 where $\mc\equiv (m_1 m_2)^{3/5}/(m_1+m_2)^{1/5}$.   
-This expression depends explicitly on an assumed and metallicity-dependent mass distribution for compact object
+This expression depends explicitly on an assumed \jillianremark{\sout{and}} metallicity-dependent mass distribution for compact object
 mergers, through the characteristic chirp mass $\mc_{*}(Z)\equiv [\int p(m_1,m_2|Z) dm_1 d,m_2 (\mc/1.2
@@
 form ($m_1=m_2$), with the distribution of component masses chosen to be $\propto m_1^{-p}$ 
- with $p=2$ between $3 M_\odot$ and $M_{max}(Z)$ and zero otherwise; see, e.g.,
+ with $p=2$ between $3 M_\odot$ and $M_{max}(Z)$ and zero otherwise \jillianremark{(hold on, p=0 otherwise or masses $ \propto 0$ otherwise?)}; see, e.g.,
 \cite{popsyn-LowMetallicityImpact2b-StarTrackRevised-2013}.    For binary black holes, this means  the
@@
 % POINT:  Model
-To characterize how often different star-forming conditions occur, we use our simulations, which provide a galaxy's star formation rate
-$\dot{M}_*$ and star formation metallicity distribution $p(\log Z|t)$.
+To characterize the frequency of different star-forming conditions, we use our cosmological simulations of Milky Way-like galaxies, which provide each galaxy's star formation rate
+$\dot{M}_*$ and star formation metallicity distribution $p(\log Z|t)$ over time.
 
@@
     In this paper we only investigate the relative contribution of
-different star-forming environments, not the overall normalization, so the overall scale of $\lambda$ is irrelevant.  
+different star-forming environments, not the overall normalization \jillianremark{(why doesn't the absolute value matter?)}, so the overall scale of $\lambda$ is irrelevant.  
 However, to account for the strong tendency of low-metallicity star-forming regions to produce many binary compact
@@
 \label{eq:LambdaVersusZModel}
-\lambda(Z) &=& \lambda_o \text{max}[(Z/Z_\odot)^{-a}, F_{max}] 
+\lambda(Z) &=& \lambda_o \text{min}[(Z/Z_\odot)^{-a}, F_{max}] 
 \end{eqnarray}
@@
 %$\lambda_o F_{max} < 3\times 10^{-4}/M_\odot$
- (see, e.g.\cite{popsyn-LIGO-SFR-2008}, \abbrvKBLowZa).  For the purposes of illustration, we adop a  concrete scale
+ (see, e.g.\cite{popsyn-LIGO-SFR-2008}, \abbrvKBLowZa).  For the purposes of illustration, we adopt a  concrete scale
 factor  $
@@
 metallicity correspond to a relatively small proportion of the overall population; we therefore neglect this
-effect \footnote{may want to change}.
+effect\footnote{may want to change}.
 
@@
 
-Even when electromagnetic counterparts are available, the long delay times between coalescence and merger  limit
+Even when electromagnetic counterparts are available, the long delay times between coalescence and merger \jillianremark{(hold on are coalescence and mergers not the same thing?
+does coalescence represent the beginning of the inspiral?
+hmmm)} limit
 the prospects of detailed electromagnetic followup of individual event. 

### 2016-07-11 python/maxmass.py
fix bug

@@ -7,6 +7,7 @@
 import numpy as np
 import matplotlib.pyplot as plt
 from scipy.interpolate import interp1d
+import scipy.interpolate as interpol
 
 metals,maxbh = np.loadtxt("mass_max_of_z.dat",unpack=True)
 
@@ -18,6 +19,8 @@ metalgrid = np.linspace(min(metals),max(metals),1000)
 
 f = interpol.interp1d(metals,maxbh)
 maxmassgrid = f(metalgrid)
+#print f(0.1)
+#print "******"
 
 """
 plt.plot(metals,maxbh)

### 2016-07-11 python/sfr_to_rate_nobins_BBH.py
Modifying

@@ -16,9 +16,13 @@
 # PLOTS
 #    Third plot is money plot: shows you where the mergers are coming from, for different exponent choices.
 
+import matplotlib.pyplot as plt
+import sys
 import numpy as np
+from scipy.integrate import simps
 
 import bisect
+from scipy.interpolate import interp1d
 from scipy.interpolate import griddata
 
 import ParseStars
@@ -26,12 +30,78 @@ import ParseStars
 import argparse
 parser = argparse.ArgumentParser()
 parser.add_argument("--starmetal-file", default=None)
+parser.add_argument("--type-bbh",action='store_true',help="Volume function selection bias (and Z exponent?) appropriate to BBH")
+parser.add_argument("--type-bhns",action='store_true',help="Volume function selection bias (and Z exponent?) appropriate to BH-NS")
 parser.add_argument("--time-exponent",default=1,type=float)
 parser.add_argument("--Z-exponent",default=0,type=float)
 opts = parser.parse_args()
 if not opts.starmetal_file:
     print "  Please specify an SFR file "
 
+
+# Maximum mass information (single BH)
+
+metals,maxbh = np.loadtxt("mass_max_of_z.dat",unpack=True)
+metals = metals[::-1]  # write in order
+maxbh = maxbh[::-1]
+metals = np.concatenate( (np.array([1e-5]), metals,[100]))
+maxbh = np.concatenate( ([maxbh[0]],maxbh,[maxbh[-1]] ))
+
+#plt.plot(metals, maxbh);plt.legend(); plt.xlabel("metals") ; plt.ylabel("max BH mass")
+#plt.savefig('inputs.png'); plt.clf
+#plt.plot(np.log10(metals), maxbh);plt.legend(); plt.xlabel("metals") ; plt.ylabel("max BH mass")
+#plt.savefig('inputs-scaled.png')
+
+#maxbh_of_logZ = interp1d(np.log10(metals),maxbh,bounds_error=True,fill_value = np.max(maxbh),kind='linear')
+#maxbh_of_Z = lambda x: maxbh_of_logZ(np.log10(x))
+maxbh_of_Z = interp1d(metals,maxbh,bounds_error=False)#,bounds_error=True,fill_value =np.max(maxbh),kind='linear',copy=True)
+
[…]

### 2016-07-11 paper/paper.tex
Fixing segue

@@
 
+Our goal in this work is to estimate the \emph{ratio} of compact binaries that should be merging, at present, in the two
+simulated galaxies described above.
+
 To explore plausible binary detection scenarios, we adopt a parameterized formalism for binary evolution and event
@@
 form ($m_1=m_2$), with the distribution of component masses chosen to be $\propto m_1^{-p}$ 
- with $p=2$ between $3 M_\odot$ and $M_{max}(Z)$ and zero otherwise \jillianremark{(hold on, p=0 otherwise or masses $ \propto 0$ otherwise?)}; see, e.g.,
+ between $3 M_\odot$ and $M_{max}(Z)$ and zero otherwise, adopting a fiducial exponent $p=2$; see, e.g.,
 \cite{popsyn-LowMetallicityImpact2b-StarTrackRevised-2013}.    For binary black holes, this means  the

### 2016-07-11 python/sfr_to_rate_nobins_BBH.py
Push

@@ -24,6 +24,7 @@ from scipy.integrate import simps
 import bisect
 from scipy.interpolate import interp1d
 from scipy.interpolate import griddata
+from scipy.integrate import quad
 
 import ParseStars
 
@@ -72,10 +73,10 @@ maxbh_of_Z = interp1d(metals,maxbh,bounds_error=False)#,bounds_error=True,fill_v
 # sys.exit(0)
 
 def mc(m1,m2):
-    return np.power(m1**m2,3./5.)/np.power(m1+m2, 1./5.)
+    return np.power(m1*m2,3./5.)/np.power(m1+m2, 1./5.)
 
 def average_func(func,input_probability_distribution):
-    masses = np.linspace(0,100,50)
+    masses = np.linspace(0.1,100,500)  # zero total mass causes problems with mchirp definition
     prob = input_probability_distribution(masses)
     result = simps(prob*func(masses), masses)
     return result
@@ -87,19 +88,46 @@ def make_uniform_func(metal_now):
     return lambda x, Nm = nm, A = MmaxNow: np.where( np.logical_and(x<A , x > 3), nm* np.ones(len(x)), np.zeros(len(x)))
 
 
+def make_power_func(metal_now,mass_exponent=2):
+    MmaxNow = maxbh_of_Z(metal_now)
+    ret, err = quad( lambda x: np.power(x,-1*mass_exponent),3,MmaxNow)
+    nm  =ret
+#    print metal_now, MmaxNow, nm
+    return lambda x, Nm = nm, A = MmaxNow,p=mass_exponent: np.where( np.logical_and(x<A , x > 3), nm* np.power(x,-1.*p), np.zeros(len(x)))
+
 def Vaveraged_bns(Z):
     mc_av =mc(1.4, 1.4)
     return np.power(mc_av, 15./6.)
 
 def Vaveraged_bhns(Z):
     prob_Mbh = make_uniform_func(Z)
-    mc_av = average_func(lambda x: mc(1.4,x), prob_Mbh)
-#    print " internal ", Z, mc_av
-    return np.power(mc_av, 15./6.)
+    mc_av = np.power(average_func(lambda x: np.power(mc(1.4,x),15./6), prob_Mbh),5./16.)
+    nm_check = average_func(lambda x: 1, prob_Mbh)
+#    print " internal ", Z, mc_av, nm_check
+    return np.power(mc_av, 15./6.)/nm_check
 
[…]

### 2016-07-11 paper/paper.tex

@@
 
-Add me: \cite{2013ApJ...779..102K}
-Add me but note conflict \cite{2015MNRAS.453.4337S}, etc
+Add me: \cite{Kirby13}
+Add me but note conflict \cite{Somerville15}, etc
 
-Add me: \citet{2014ARAA..52..415M}
+Add me: \citet{Madau14}
 
@@
 including large-scale torques from cosmic structure.  We use
-WMAP3 cosmology \citep{WMAP} and model the ionizing UV background
+WMAP3 cosmology \citep{WMAP3} and model the ionizing UV background
 with the prescription from \citet{Haardt96}.  Stars form
@@
 particle (representing a simple stellar population with a Kroupa IMF
-\citep{Kroupa01}) which is given by
+\citep{Kroupa}) which is given by
 
@@
 that our galaxies match the observed Kennicutt-Schmidt law
-\citep{1989ApJ...344..685K};  X$_{\rm H_2}$ is the molecular hydrogen fraction of the gas particle; $m_{star}$ and $m_{gas}$ are the star and gas
+\citep{Kennicutt89};  X$_{\rm H_2}$ is the molecular hydrogen fraction of the gas particle; $m_{star}$ and $m_{gas}$ are the star and gas
 particle masses;\footnote{In our high-resolution simulations \textbf{ROS-check!}\jillianremark{this number is correct, is that what you want to check? - JMB}, each gas particle starts with a mass
   $m_{gas,0}=26,676 M_\odot$, gaining mass from feedback and losing it to star formation.  Each star particle, when
-  formed, has $1/3$ of the progenitor mass of the forming gas particle.  See \cite{2010ApJ...717..121C} for a discussion
+  formed, has $1/3$ of the progenitor mass of the forming gas particle.  See \cite{Christensen10} for a discussion
 of resolution issues in these SPH simulations.} $t_{form}$ is the dynamical time for the gas
@@
 which we set to 1 Myr.  We model supernova feedback using the
-blastwave formalism described in \citet{1977ApJ...218..148M} and implemented in
+blastwave formalism described in \citet{McKee77} and implemented in
 our simulations as in \citet{Stinson06}.  Each supernova releases
@@
 the detailed characteristics of bulgeless dwarf galaxies
-\citep{Governato10} and the Milky Way \citep{2011ApJ...742...76G}.
+\citep{Governato10} and the Milky Way \citep{Guedes11}.
 
@@
 and deposited directly to the gas within the blast radius.  Stellar
-masses are converted to ages as described by \citet{1996A&A...315..105R}, and
+masses are converted to ages as described by \citet{Raiteri96}, and
 stars more massive than 8 M$_\odot$ are able to undergo a Type II
@@
 We identify individual galaxies using the halo finder $AHF$
-\citep{Gill04,Knollman09}, which identifies halos based on an
+\citep{Gill04,Knollmann09}, which identifies halos based on an
 overdensity criterion for a flat universe \citep{Gross97}.  For this
@@
 properties, including stellar dynamics
-\citep{Loebman12,Loebman14,2014ApJ...790...89K}, baryon fraction
+\citep{Loebman12,Loebman14,Kassin14}, baryon fraction
 \citep{Munshi13}, halo properties \citep{Zolotov09,Zolotov10}, and
@@
 %   - of course
-Gravitational wave detectors are also far more sensitive to  massive compact binaries, \sout{as}  \jillianremark{ which?} are  preferentially  formed in low metallicity
+Gravitational wave detectors are also far more sensitive to  massive compact binaries, which are  preferentially  formed in low metallicity
 environments \citep{PSellipticals,popsyn-LowMetallicityImpact2c-StarTrackRevised-2014}.  As a result, low metallicity
@@
 For this reason, our estimates for compact binary coalescence rates must account for how often  different star-forming
-conditions occur;  how often compact binaries that can coalesce now \jillianremark{\sout{can}}  derive from each environment; and how often LIGO will detect compact
+conditions occur;  how often compact binaries that can coalesce now can derive from each environment; and how often LIGO will detect compact
 binaries with different masses, all other things being equal.
@@
 where $\mc\equiv (m_1 m_2)^{3/5}/(m_1+m_2)^{1/5}$.   
-This expression depends explicitly on an assumed \jillianremark{\sout{and}} metallicity-dependent mass distribution for compact object
+This expression depends explicitly on an assumed and metallicity-dependent mass distribution for compact object
 mergers, through the characteristic chirp mass $\mc_{*}(Z)\equiv [\int p(m_1,m_2|Z) dm_1 d,m_2 (\mc/1.2
@@
   excellent approximation for merging BH-BH binaries at solar metallicity.  }
-    In this paper we only investigate the relative contribution of
-different star-forming environments, not the overall normalization \jillianremark{(why doesn't the absolute value matter?)}, so the overall scale of $\lambda$ is irrelevant.  
+    In this paper we are investigating the relative contribution of
+different star-forming environments and galaxy evolutionary histories, not the overall normalization, so the overall scale of $\lambda$ is irrelevant.  
 However, to account for the strong tendency of low-metallicity star-forming regions to produce many binary compact

### 2016-07-12 python/analyze_me.sh
Analysis basics.  Still trouble with BBH case not changing enough .. we are saturating the lambda(Z) dependence

@@ -1,0 +1,53 @@
+
+HERE=`pwd`
+
+# BHBH
+mkdir bh_bh; cd bh_bh
+for my_type  in exciting boring
+do
+  mkdir ${my_type}; cd ${my_type}
+  ln -sf ${HERE}/mass_max_of_z.dat .
+  python ${HERE}/sfr_to_rate_nobins_BBH.py --starmetal-file ~/PersonalJBArchive/${my_type}-galaxy/z0.016.starmetal.dat --type-bbh > my.log
+  cd ..
+done
+mkdir dwarf1; cd dwarf1
+    ln -sf ${HERE}/mass_max_of_z.dat .
+  python ${HERE}/sfr_to_rate_nobins_BBH.py --starmetal-file ~/PersonalJBArchive/Dwarf1/dwarf1.z0.starmetal.dat --type-bbh > my.log
+   cd ..
+mkdir dwarf2; cd dwarf2
+    ln -sf ${HERE}/mass_max_of_z.dat .
+  python ${HERE}/sfr_to_rate_nobins_BBH.py --starmetal-file ~/PersonalJBArchive/Dwarf2/dwarf2.z0.1.starmetal.dat --type-bbh > my.log
+   cd ..
+cd ..
+
+# BHNS
+mkdir bh_ns; cd bh_ns
+for my_type  in exciting boring
+do
+  mkdir ${my_type}; cd ${my_type}
+  ln -sf ${HERE}/mass_max_of_z.dat .
+  python ${HERE}/sfr_to_rate_nobins_BBH.py --starmetal-file ~/PersonalJBArchive/${my_type}-galaxy/z0.016.starmetal.dat --type-bhns > my.log
+  cd ..
+done
+mkdir dwarf1; cd dwarf1
+    ln -sf ${HERE}/mass_max_of_z.dat .
+  python ${HERE}/sfr_to_rate_nobins_BBH.py --starmetal-file ~/PersonalJBArchive/Dwarf1/dwarf1.z0.starmetal.dat --type-bhns > my.log
+   cd ..
+mkdir dwarf2; cd dwarf2
+    ln -sf ${HERE}/mass_max_of_z.dat .
+  python ${HERE}/sfr_to_rate_nobins_BBH.py --starmetal-file ~/PersonalJBArchive/Dwarf2/dwarf2.z0.1.starmetal.dat --type-bhns > my.log
+   cd ..
+
+cd ..
+
+
+# BHNS
[…]

### 2016-07-12 python/sfr_to_rate_nobins_BBH.py

@@ -34,7 +34,8 @@ parser.add_argument("--starmetal-file", default=None)
 parser.add_argument("--type-bbh",action='store_true',help="Volume function selection bias (and Z exponent?) appropriate to BBH")
 parser.add_argument("--type-bhns",action='store_true',help="Volume function selection bias (and Z exponent?) appropriate to BH-NS")
 parser.add_argument("--time-exponent",default=1,type=float)
-parser.add_argument("--Z-exponent",default=0,type=float)
+parser.add_argument("--Z-exponent",default=None,type=float)
+parser.add_argument("--verbose", action='store_true')
 opts = parser.parse_args()
 if not opts.starmetal_file:
     print "  Please specify an SFR file "
@@ -45,7 +46,7 @@ if not opts.starmetal_file:
 metals,maxbh = np.loadtxt("mass_max_of_z.dat",unpack=True)
 metals = metals[::-1]  # write in order
 maxbh = maxbh[::-1]
-metals = np.concatenate( (np.array([1e-5]), metals,[100]))
+metals = np.concatenate( (np.array([1e-9]), metals,[1e5]))
 maxbh = np.concatenate( ([maxbh[0]],maxbh,[maxbh[-1]] ))
 
 #plt.plot(metals, maxbh);plt.legend(); plt.xlabel("metals") ; plt.ylabel("max BH mass")
@@ -126,48 +127,94 @@ def Vaveraged_bhbh(Z):
 #print 1, maxbh_of_Z(1), mc_av
 #sys.exit(0)
 
-for lZ in np.linspace(-3,0, 30):
-    print lZ, Vaveraged_bns(np.power(10,lZ)), Vaveraged_bhns(np.power(10,lZ)) , Vaveraged_bhbh(np.power(10,lZ))
+# Get data for three key functions, and interpolate it
+if opts.verbose:
+    print " Building 'V' factor used later...here is the specific table "
+    print "  log10 Z/Zsun     V_bns  V_bhns  V_bhbh "
+dat_logZoverZsun = np.linspace(-7,4,400)
+dat_nsns = np.zeros(len(dat_logZoverZsun))
+dat_bhns=np.zeros(len(dat_logZoverZsun))
+dat_bhbh=np.zeros(len(dat_logZoverZsun))
+for indx in np.arange(len(dat_nsns)):
+    lZ =dat_logZoverZsun[indx]
+    v1=dat_nsns[indx] = Vaveraged_bns(np.power(10,lZ))
[…]

### 2016-07-12 paper/paper.tex
Prepping organization

@@
 
+\editremark{recheck numbers: we are tweaking things, and Zsun is seemingly inconsistent in the two approaches }
+ Our two galaxies have extremely similar star formation histories and metallicity evolution, particularly at late
+ times.  
+However, at early times, the exciting galaxy forms stars for $\simeq 2\unit{Gyr}$ at a lower characteristic metallicity
+($Z\simeq 0.8 10^{-3}$) compared
+to the borinng galaxy ($Z\simeq 2\times 10^{-3}$).  In this reigme, the formation efficiency $\lambda$ and sensitive volume $V$
+can depend sensitively on mass; for example, for binary black holes, the ratio of  $(\lambda V)_{boring}/(\lambda
+V)_{exciting} \simeq 7$.
+% 1e-3:  V = 276, lambda= 400   
+% 2e-3:  V= 152.657625157, lambda = 100
+% so the ratio should be a factor of about 7x higher due to this region.
+Therefore, though only a fraction \textbf{XXX} of all star formation occurs in this epoch, by this order of magnitude
+argument, the overall number of
+present-day coalescing binary black holes in our two galaxies is expected to differ by as much as a factor of \textbf{YYY (=2?)}.  
+%
+Using the concrete phenomenological calculations described above, we in fact find
+$r_{D,boring}/r_{D,exciting}=\textbf{ZZZ}$.
+
+The origin of the differenc
+
 \section{Implications for transient multimessenger astronomy}
@@
 
-\appendix
-
 \bibliography{bhmetals}

### 2016-07-12 python/sfr_to_rate_nobins_BBH.py

@@ -46,7 +46,7 @@ if not opts.starmetal_file:
 metals,maxbh = np.loadtxt("mass_max_of_z.dat",unpack=True)
 metals = metals[::-1]  # write in order
 maxbh = maxbh[::-1]
-metals = np.concatenate( (np.array([1e-9]), metals,[1e5]))
+metals = np.concatenate( (np.array([1e-18]), metals,[1e9]))
 maxbh = np.concatenate( ([maxbh[0]],maxbh,[maxbh[-1]] ))
 
 #plt.plot(metals, maxbh);plt.legend(); plt.xlabel("metals") ; plt.ylabel("max BH mass")
@@ -131,7 +131,7 @@ def Vaveraged_bhbh(Z):
 if opts.verbose:
     print " Building 'V' factor used later...here is the specific table "
     print "  log10 Z/Zsun     V_bns  V_bhns  V_bhbh "
-dat_logZoverZsun = np.linspace(-7,4,400)
+dat_logZoverZsun = np.linspace(-9,7,400)
 dat_nsns = np.zeros(len(dat_logZoverZsun))
 dat_bhns=np.zeros(len(dat_logZoverZsun))
 dat_bhbh=np.zeros(len(dat_logZoverZsun))
@@ -158,7 +158,8 @@ if opts.verbose:
 # format of this file: 3 columns, star metallicity, nearby gas metallicity, formation time of star
 lambda0 = 1e-3
 
-Zsun_val = 0.02
+Zsun_val_stellar = 0.02    # Problem: galaxy plot has zsun = 0.01, but KB has Zsun=0.02
+Zsun_val_JB =0.01
 
 def volume_function():
     """
@@ -167,17 +168,17 @@ def volume_function():
     # we will add something real here
     if not opts.type_bbh and not opts.type_bhns:
         print " Volume function: using NSNS"
-        return fn_nsns(dat[:,0]/Zsun_val)
+        return fn_nsns(dat[:,0]/Zsun_val_stellar)
     elif opts.type_bhns:
         print " Volume function: using BHNS"
-        return fn_bhns(dat[:,0]/Zsun_val)
+        return fn_bhns(dat[:,0]/Zsun_val_stellar)
     else:
         print " Volume function: using BHBH"
-        return fn_bhbh(dat[:,0]/Zsun_val)
+        return fn_bhbh(dat[:,0]/Zsun_val_stellar)
 
 def metal_function(z_exp):
[…]

### 2016-07-12 paper/paper.tex
Draft

--- 2016-07-11 paper/paper.tex
@@
 Using detailed simulations of galaxy and chemical evolution, we demonstrate by example that galaxies with similar present-day appearance can host distinctly different
-compact binary populations.
-We discuss the implications for transient multimessenger astronomy with compact binary sources. \jillianremark{Add quantifiable stuff when we have it.}
+compact binary populations.  As an example, we demonstrate how the coalescing binary black hole population can differ by
+factors of order  unity, and even binary neutron star populations differ by tens of percent.  
+We discuss the implications for transient multimessenger astronomy with compact binary sources. 
+%\jillianremark{Add quantifiable stuff when we have it.}
 %% Present and future observations of  merging compact binaries can provide valuable constraints on their birthrate
@@
 
-Add me: Hopkins et al  \cite{2016arXiv160508783L} (in context of similar model, building off my prior work)
+%Add me: Hopkins et al  \cite{2016arXiv160508783L} (in context of similar model, building off my prior work)
 
@@
 
-\section{Formation rate for binary black holes}
+\section{Compact object binary formation rate}
 \label{sec:results:BBH}
+
+%\editremark{recheck numbers: we are tweaking things, and Zsun is seemingly inconsistent in the two approaches }
+ Our two galaxies have extremely similar star formation histories and metallicity evolution, particularly at late
+ times.  
+However, at early times, the exciting galaxy forms stars for $\simeq 2\unit{Gyr}$ at a lower characteristic metallicity
+($Z\simeq 0.8 \times10^{-3}$) compared
+to the boring galaxy ($Z\simeq 2\times 10^{-3}$).  In this reigme, the formation efficiency $\lambda$ and sensitive volume $V$
+can depend sensitively on mass; for example, for binary black holes, the ratio of  $(\lambda V)_{boring}/(\lambda
+V)_{exciting} \simeq 7$.    However, in this same epoch, the star formation rate in the exciting (low-metallicity)
+galaxy is smaller, by a factor of roughly 2.
+% 1e-3:  V = 276, lambda= 400   
+% 2e-3:  V= 152.657625157, lambda = 100
+% so the ratio should be a factor of about 7x higher due to this region.
+Therefore, though only a fraction \textbf{XXX} of all star formation occurs in this epoch, by this order of magnitude
+argument, the overall number of
+present-day coalescing binary black holes in our two galaxies is expected to differ by as much as a factor of order \textbf{only
+a few percent.}  
+%
+Using the concrete phenomenological calculations described above, we in fact find
+$r_{D,boring}/r_{D,exciting}=\textbf{ZZZ}$.
+
+The close agreement between the two galaxies' binary black hole populations  is entirely a
+a numerical coincdence between the specific star formation rate and metallicities in these two galaxies.  The effects described here
+  are well within the scatter around the mass-metallicity relation.  Marginally different realizations of these
+  histories can easily produce factors of order unity difference in galaxies with otherwise indistinguishable
+  present-day properties.\editremark{do we have another example}
+
+More broadly, Table \ref{tab:Results} shows the results of our calculations for the three types of compact binaries
+described above.   These calculations show just how dramatically different the compact binary populations of galaxies
+with similar present-day mass but different star formation histories could be.   In particular, dwarf galaxies have an
+exceptionally large fraction of low-metallicity star formation in their history.  The precise details of their chemical
+evolution can modify their present-day binary black hole binary populations by factors of order a few, despite  adopting
+the conservative choices described above for the dependence of rate on metallicity.
+
+To highlight how sensitively compact binaries depend on detailed evolutionary trajectories, Table \ref{tab:Results}
+shows results for binary neutron stars.  By our construction, no metallicity dependence is included in the present-day
+event rate for neutron stars.  Thus, the differences in
+present-day state between these two galaxy population models arise solely and exclusively on the time distribution history of past star formation.
+In general, the present-day population depends often significantly (i.e., tens of
+percent) on the assembly history alone, even aside from any composition-dependent effects.
+
+\begin{table}
+\begin{centering}
+\begin{tabular}{|ll|l|}\hline
+ \text{Boring} & \text{BHBH} & 1.05 \\
+ \text{Exciting} & \text{BHBH} & 1.11 \\
+ \text{Dwarf1} & \text{BHBH} & 3.14 \\
+ \text{Dwarf2} & \text{BHBH} & 10.3 \\ \hline
+ \text{Boring} & \text{NSNS} & 0.000425 \\
+ \text{Exciting} & \text{NSNS} & 0.000513 \\ \hline
+ \text{Boring} & \text{BHNS} & 0.00162 \\
+ \text{Exciting} & \text{BHNS} & 0.00195 \\
+ \text{Dwarf1} & \text{BHNS} & 0.00217 \\
+ \text{Dwarf2} & \text{BHNS} & 0.00182\\  \hline
+\end{tabular}
+\end{centering}
+\caption{\label{tab:Results}\textbf{Event rates per unit mass $r_D/M$, arbitrary units}, for the three different types of binaries
+  discussed.  
+}
+\end{table}
 
@@
 
-Even when electromagnetic counterparts are available, the long delay times between coalescence and merger \jillianremark{(hold on are coalescence and mergers not the same thing?
-does coalescence represent the beginning of the inspiral?
-hmmm)} limit
+Even when electromagnetic counterparts are available, the long delay times between binary formation and merger limit
 the prospects of detailed electromagnetic followup of individual event. 
@@
 %
-The future of gravitational wave host galaxy associations is bright.
+%The future of gravitational wave host galaxy associations is bright.
 
@@
 
-We present a model for binary black hole \jillianremark {and other binary compact object formation?} based on models of binary formation and properties over cosmic time.
-We fold these models with star formation histories and metallicity distributions taken from state of the art cosmological simulations of Milky Way-like galaxies.
-We demonstrate that galaxies which appear similar at $z = 0$ but have differing merger histories will have different rates of BBH mergers detectable by LIGO.
-\jillianremark{sentence detailing the specifics of this prediction, once we know what it is.}
+We examine the present-day populations of coalescing compact binaries in galaxies with different assembly histories.  We
+combine  detailed and state-of-the-art cosmological simulations of galaxies with a simple but robust phenomenological
+model for how compact binaries form from different environments.   
+%% We model for compact binary black hole \jillianremark {and other binary compact object formation?} based on models of
+%% binary formation and properties over cosmic time.  We fold these models with star formation histories and metallicity
+%% distributions taken from state of the art cosmological simulations of Milky Way-like galaxies. 
+ We demonstrate that
+galaxies which appear similar at $z = 0$ but have differing merger histories will have substantially different
+detection-weighted compact binary
+coalescence rates rates.
 
-One result of our conclusions is that we can learn about the past assembly history of a galaxy from its LIGO event rate, \jillianremark{ that's really cool.
-}  Also we can use resolved star formation histories of nearby galaxies {\bf (citations)} to predict likelihoods for LIGO events.
-\jillianremark { what else}\\
+For binary black hole mergers in particular, we show that the present-day binary black hole coalescence rate can vary by factors of several in otherwise
+similar present-day environments.   Our calculations supports and extends prior investigations which demonstrated both
+that black hole merger rates depend sensitively on low-metallicitiy environments
+\cite{PSellipticals,popsyn-LowMetallicityImpact2b-StarTrackRevised-2013,gwastro-EventPopsynPaper-2016}.   More broadly,
+because compact binaries can merge long after they form, their host galaxy can evolve substantially in composition
+between birth and merger.
+%% and that the delay between compact
+%% binary formation and coalesence ccn be
+%% the sensitive dependence of binary evolution on
+%% metallicity implies that
+%% * BBH properties far from apparent.  No surprise: delays can be long , particularly because formation in low Z favored,
+%% so system changes significantly from assembly conditions
 
-* BBH properties far from apparent.
-No surprise: delays can be long \cite{PSellipticals,popsyn-LowMetallicityImpact2b-StarTrackRevised-2013,gwastro-EventPopsynPaper-2016}, particularly because formation in low Z favored,
-so system changes significantly from assembly conditions
-
-* EM counterpart properties: delay times are shorter, so more of a surprise that formation scenario matters.  However,
-BH properties depend on $Z$, which can influence the mass and spin of BHs that produce EM counterparts.
-
-* Detailed analysis of one host galaxy presented in this work is complementary to the population-based approach used in
-\cite{2016arXiv160508783L}, which favored formation in a wide range of galaxies and event times.   % that analysis also
-                                % used a poor input from BSE, about the coalescence delay
-
-Biases towards low-metallicity star formation have been extensively studied in the context of long GRBs and their host galaxies.
-%
+The detailed analysis of the compact binary populations formed through the assembly history of individual galaxies is
+complementary to the  population-based approach reported in
+\cite{2016arXiv160508783L}.     More broadly, our analysis reflect  similar theoretical studies performed in the interpretation of, for
+example, long GRBs and their host galaxies. 
 For example, \cite{2009ApJ...702..377K} demonstrated that a sufficiently strong bias towards low-metallicity star formation would predict
@@
 For less extreme metallicity biases, subsequent calculations by  \citet{2011MNRAS.417..567N} demonstrated that the
+metallicity distribution within galaxies will usually lead to events in a wide range of host galaxies in the local universe.
+% which favored formation in a wide range of galaxies and event times.   % that analysis also
+                                % used a poor input from BSE, about the coalescence delay
+
+In short, in this work we have demonstrated that  the confounding effects of host galaxy assembly history can in the
+near term complicate the interpretation of associations between GW sources and candidate host galaxies.   However, given sufficient
+statistics, as will inevitably become available with next-generation GW instruments, combined with large-scale
+multiband followup, these confounding challenges can  both be overcome and converged into opportunity.   In the far future,  with hundreds of thousands of thousands to millions of events per year in
+networks like Cosmic Voyager, Einstein Telescope, and DECIGO, GW measurements could even  provide complementary statistical probes of the past history of
+galaxy assembly and evolution.  
+%% , given The challenge of host-galaxy inhomogeneity is an irritating but demonstrably surmountable obstacle for the analysis and
+%% interpretation of GW host galaxies.  
+%
+
+%% One result of our conclusions is that we can learn about the past assembly history of a galaxy from its LIGO event rate, \jillianremark{ that's really cool.
+}  Also we can use resolved star formation histories of nearby galaxies {\bf (citations)} to predict likelihoods for LIGO events.
+\jillianremark { what else}\\
+
+%* EM counterpart properties: delay times are shorter, so more of a surprise that formation scenario matters.
+However, BH properties depend on $Z$, which can influence the mass and spin of BHs that produce EM counterparts.
 

### 2016-07-12 python/sfr_to_rate_nobins_BBH.py

@@ -161,6 +161,8 @@ lambda0 = 1e-3
 Zsun_val_stellar = 0.02    # Problem: galaxy plot has zsun = 0.01, but KB has Zsun=0.02
 Zsun_val_JB =0.01
 
+fac_convert = Zsun_val_stellar/Zsun_val_JB
+
 def volume_function():
     """
     volume_function: compute the metallicity-dependent factor proportional to V \propto \mc^(15/6)
@@ -168,24 +170,31 @@ def volume_function():
     # we will add something real here
     if not opts.type_bbh and not opts.type_bhns:
         print " Volume function: using NSNS"
-        return fn_nsns(dat[:,0]/Zsun_val_stellar)
+        return fn_nsns(fac_convert*dat[:,0]/Zsun_val_stellar)
     elif opts.type_bhns:
         print " Volume function: using BHNS"
-        return fn_bhns(dat[:,0]/Zsun_val_stellar)
+        return fn_bhns(fac_convert*dat[:,0]/Zsun_val_stellar)
     else:
         print " Volume function: using BHBH"
-        return fn_bhbh(dat[:,0]/Zsun_val_stellar)
+        return fn_bhbh(fac_convert*dat[:,0]/Zsun_val_stellar)
 
 def metal_function(z_exp):
     # number of merging compact binaries in a starburst depends on metallicity
-    return np.minimum(np.power((1e-8+dat[:,0])/Zsun_val_stellar,-1.*z_exp), 1e3*np.ones(len(dat)))
+    return np.minimum(np.power((1e-8+fac_convert*dat[:,0])/Zsun_val_stellar,-1.*z_exp), 1e3*np.ones(len(dat)))
 
 def time_function(time_exp):
     """
     time_function: dP/dt \propto 1/t for t > 0.01 Gyr
+    EXCEPT for BH-BH, suppress formation at early times
     """
     # where does this come from?
-    return np.where(dat[:,2]>0.01,1./np.power(dat[:,2]+1e-4, time_exp),np.zeros(len(dat)))
+    standard_delay =  np.where(dat[:,2]>0.01,1./np.power(dat[:,2]+1e-4, time_exp),np.zeros(len(dat)))
+    if opts.type_bbh:
+        standard_delay =  np.where(dat[:,2]>0.01,1./np.power(dat[:,2]+1e-4, 1),np.zeros(len(dat)))   # start with 1/t, to avodi confusion
[…]

### 2016-07-12 paper/paper.tex
resolve SF citations

@@
 can be explored at great depth and detail via  position-resolved spectroscopy, enabling detailed position-resolved star-formation
-and chemical evolution histories \editremark{citation: need better ones} \citep[see,e.g.][]{2009MNRAS.396..462K,2014MNRAS.444..336C}.
+and chemical evolution histories \editremark{citation: need better ones} \citep[see,e.g.][]{2009MNRAS.396..462K,2014MNRAS.444..336C, Dalcanton09,Williams11,CALIFA}.
 \jillianremark{Do you want citations of GRB host observations or just general galaxy stuff?}
@@
 %maybe move the below section to later and/or consolidate
-One simulation we report here, $h258$,
+One simulation we report here, h258,
 involves the formation of a Milky Way-like disk galaxy whose

### 2016-07-12 paper/paper.tex
Adding dwarfs

@@
 \newcommand\cqg{CQG}
+\newcommand\ExcitingGalaxy{h258}
+\newcommand\BoringGalaxy{h277}
+\newcommand\DwarfOne{h603}
+\newcommand\DwarfTwo{h516}
+\newcommand\DwarfThree{??}
+\newcommand\DwarfFour{XX}
+\newcommand\MysteryGalaxy{YY}
+\newcommand\ControlGalaxy{ZZ}
 \newcommand\E[1]{\left<#1\right>}
@@
 \title{Details matter: Similar host galaxies can harbor different merging compact binary populations} 
+\author{ J. Bellovary}
+\affiliation{Department of Physics, Queensborough Community College, Bayside, NY 11364}
+\email{jbellovary@qcc.cuny.edu}
 \author{R.\ O'Shaughnessy}
@@
 \email{oshaughn@mail.rit.edu}
-\author{ J. Bellovary}
-\affiliation{Department of Physics, Queensborough Community College, Bayside, NY 11364}
-\email{jbellovary@qcc.cuny.edu}
 \begin{abstract}
@@
 
-\editremark{We will be very careful to specify how SFR and metallicity are measured, backtracking}
+%\editremark{We will be very careful to specify how SFR and metallicity are measured, backtracking}
 
-Add me: \cite{Kirby13}
-Add me but note conflict \cite{Somerville15}, etc
+%Add me: \cite{Kirby13}
+\editremark{Jillian}: Add me but note conflict \cite{Somerville15}, etc or \cite{2015ARAA..53...51S}
 
-Add me: \citet{Madau14}
+%Add me: \citet{Madau14}  % not necessary, we are not doing a synthetic universe
 
@@
 %
-On the other hand, gravitational wave detectors can perform high-precision sky and volumetric localization \cite{2016LRR....19....1A,2016arXiv160307333S}.  As GW detector
+On the other hand, gravitational wave detectors can perform high-precision sky and volumetric localization \citep{2016LRR....19....1A,2016arXiv160307333S}.  As GW detector
 networks increase in sensitivity, these localizations will allow statistical and, eventually, unique identification of
@@
 The host galaxies of distant short GRBs have already been extensively investigated, with the associations being used to
-draw preliminary conclusions about their progenitors  \cite{2014ARAA..52...43B}.   
+draw preliminary conclusions about their progenitors  \citep{2014ARAA..52...43B}.   
 %Of necessity, these analyses  on bulk correlations, often stacked to increase significance across multiple sources
@@
 can be explored at great depth and detail via  position-resolved spectroscopy, enabling detailed position-resolved star-formation
-and chemical evolution histories \editremark{citation: need better ones} \citep[see,e.g.][]{2009MNRAS.396..462K,2014MNRAS.444..336C, Dalcanton09,Williams11,CALIFA}.
-\jillianremark{Do you want citations of GRB host observations or just general galaxy stuff?}
+and chemical evolution histories  \citep[see,e.g.][]{2009MNRAS.396..462K,2014MNRAS.444..336C,
+  Dalcanton09,Williams11,CALIFA}.  
 % POINT: But is it useful?
@@
 metallicity-dependent  phenomenological model to calculate the present-day rate and mass distribution of compact binary
-mergers from  a galaxy's known history.   In \S \ref{sec:results:BBH}, we use this model to demonstrate the binary black hole coalescence rate
-depends sensitively on the galaxy's assembly history, in a manner which is far from apparent from its present-day
-properties.  
-In \S \ref{sec:results} we show that while these two galaxy formation models should produce comparable detectable binary neutron star
-populations, these two scenarios could produce dramatically different populations of electromagnetically detectable
-merging black hole-neutron star binaries. 
+mergers from  a galaxy's known history.   In \S \ref{sec:results:BBH}, we use this model to demonstrate the binary black
+hole (BH-BH) coalescence rate
+can depend sensitively on the galaxy's assembly history, in a manner which is far from apparent from its present-day
+properties.    We also demonstrate that even the coalescence rates of binary neutron stars (NSNS) and black hole-neutron
+star (BH-NS) binaries also depend surprisingly sensitively on the assembly history of each galaxy. 
+In \S~\ref{sec:Discussion} we discuss the implications of our study for the interpretation of host galaxy associations
+identified via transient multmiessenger astronomy, in the short and long term.  We summarize our results in \S~ \ref{sec:conclude}.
+%% In \S \ref{sec:results} we show that while these two galaxy formation models should produce comparable detectable binary neutron star
+%% populations, these two scenarios could produce dramatically different populations of electromagnetically detectable
+%% merging black hole-neutron star binaries. 
 %
@@
 \citep{Kennicutt89};  X$_{\rm H_2}$ is the molecular hydrogen fraction of the gas particle; $m_{star}$ and $m_{gas}$ are the star and gas
-particle masses;\footnote{In our high-resolution simulations \textbf{ROS-check!}\jillianremark{this number is correct, is that what you want to check? - JMB}, each gas particle starts with a mass
+particle masses;\footnote{In our high-resolution simulations, each gas particle starts with a mass
   $m_{gas,0}=26,676 M_\odot$, gaining mass from feedback and losing it to star formation.  Each star particle, when
@@
 number of observed relations such as the mass-metallicity relation
-\citep{Brooks07}, the Tully-Fisher relation \citep{Governato09}, and
+\citep{Brooks07,Kirby13}, the Tully-Fisher relation \citep{Governato09}, and
 the size-luminosity relation \citep{Brooks11}, as well as reproduce
@@
 
-{\bf Richard go ahead and edit this however is needed.}  The evolution
+%{\bf Richard go ahead and edit this however is needed.}  
+The evolution
 of a galaxy, in terms of its stellar mass and metallicity evolution,
@@
 rate, we have chosen two simulations which are extremely similar at $z
-= 0$ but differ strongly in their merger histories.
+= 0$ but differ strongly in their merger histories; see Figure \ref{fig:GalaxyImages}.
 
-The simulation h277 (Boring Galaxy) is a Milky Way analog with a
+The simulation h277  is a Milky Way analog with a
 quiescent merger history.  It experiences its last major merger at $z
@@
   \times 10^{11} \msun$, stellar mass $M_* = 4.46 \times 10^{10}
-  \msun$, and maximum circular velocity $v_{circ} = 242$ km s$^{-1}$.  \editremark{Might we want to show the images of these galaxies?}
+  \msun$, and maximum circular velocity $v_{circ} = 242$ km s$^{-1}$.  %\editremark{Might we want to show the images of these galaxies?}
 
@@
 \includegraphics[width=\columnwidth]{Figures/exciting}
-\caption{Synthetic SDSS $gri$ images of our two Milky Way-type galaxies, h277 (left) and h258 (right), created with \textsc{SUNRISE} \citep{Jonsson06}.
+\caption{\label{fig:GalaxyImages}Synthetic SDSS $gri$ images of our two Milky Way-type galaxies, h277 (left) and h258 (right), created with \textsc{SUNRISE} \citep{Jonsson06}.
 \label{fig:images}
@@
 \caption{\label{fig:TwoGalaxies}\textbf{Star formation and metallicity versus time}:  \emph{Left panel}: Star formation history $\dot{M}_{*}$
-  versus time.  Black corresponds to galaxy A (``boring'') and red to galaxy B (``exciting'').  
+  versus time.  Black corresponds to \BoringGalaxy{} and red to \ExcitingGalaxy.  
 \emph{Right panel}: A plot of the  metallicity $Z$ of recently-formed stars versus time.  Solid red and black lines show
@@
 star-forming history, newly-born stars are created with significantly different metallicity.  Additionally, prior to the
-second major merger of galaxy B at $\simeq 6\unit{Gyr}$, stars form in the ``exciting'' galaxy at a systematically lower
-metallicity than in the ``boring'' counterpart.
+second major merger of galaxy B at $\simeq 6\unit{Gyr}$, stars form in the \ExcitingGalaxy{} galaxy at a systematically lower
+metallicity than in the \BoringGalaxy{} counterpart.
 }
 \end{figure*}
+
+\subsection{Dwarf galaxies}
+
+We have also employed the results of detailed simulations for several dwarf galaxies: \DwarfOne{}, \DwarfTwo{}, and others.
+
+%% h516 = dwarf2
+%% h603 = dwarf1
+%% dwarf3 = h799
+%% mystery = ? 
+%% control =?
 
@@
  times.  
-However, at early times, the exciting galaxy forms stars for $\simeq 2\unit{Gyr}$ at a lower characteristic metallicity
+However, at early times, the \ExcitingGalaxy{} galaxy forms stars for $\simeq 2\unit{Gyr}$ at a lower characteristic metallicity
 ($Z\simeq 0.8 \times10^{-3}$) compared
-to the boring galaxy ($Z\simeq 2\times 10^{-3}$).  In this reigme, the formation efficiency $\lambda$ and sensitive volume $V$
-can depend sensitively on mass; for example, for binary black holes, the ratio of  $(\lambda V)_{boring}/(\lambda
-V)_{exciting} \simeq 7$.    However, in this same epoch, the star formation rate in the exciting (low-metallicity)
+to the \BoringGalaxy{} galaxy ($Z\simeq 2\times 10^{-3}$).  In this reigme, the formation efficiency $\lambda$ and sensitive volume $V$
+can depend sensitively on mass; for example, for binary black holes, the ratio of  $(\lambda V)_{\BoringGalaxy{}}/(\lambda
+V)_{\ExcitingGalaxy{}} \simeq 7$.    However, in this same epoch, the star formation rate in the \ExcitingGalaxy{} (low-metallicity)
 galaxy is smaller, by a factor of roughly 2.
@@
 Using the concrete phenomenological calculations described above, we in fact find
-$r_{D,boring}/r_{D,exciting}=\textbf{ZZZ}$.
+$r_{D,\BoringGalaxy{}}/r_{D,\ExcitingGalaxy{}}=\textbf{ZZZ}$.
 
@@
 with similar present-day mass but different star formation histories could be.   In particular, dwarf galaxies have an
-exceptionally large fraction of low-metallicity star formation in their history.  The precise details of their chemical
+exceptionally large fraction of low-metallicity star formation in their history \cite{Kirby13}.  The precise details of their chemical
 evolution can modify their present-day binary black hole binary populations by factors of order a few, despite  adopting
@@
 \begin{tabular}{|ll|l|}\hline
- \text{Boring} & \text{BHBH} & 1.05 \\
- \text{Exciting} & \text{BHBH} & 1.11 \\
- \text{Dwarf1} & \text{BHBH} & 3.14 \\
- \text{Dwarf2} & \text{BHBH} & 10.3 \\ \hline
- \text{Boring} & \text{NSNS} & 0.000425 \\
- \text{Exciting} & \text{NSNS} & 0.000513 \\ \hline
- \text{Boring} & \text{BHNS} & 0.00162 \\
- \text{Exciting} & \text{BHNS} & 0.00195 \\
- \text{Dwarf1} & \text{BHNS} & 0.00217 \\
- \text{Dwarf2} & \text{BHNS} & 0.00182\\  \hline
+ \text{\BoringGalaxy{}} & \text{BHBH} & 1.05 \\
+ \text{\ExcitingGalaxy{}} & \text{BHBH} & 1.11 \\
+ \text{\DwarfOne} & \text{BHBH} & 3.14 \\
+ \text{\DwarfTwo} & \text{BHBH} & 10.3 \\ \hline
+ \text{\BoringGalaxy{}} & \text{NSNS} & 0.000425 \\
+ \text{\ExcitingGalaxy{}} & \text{NSNS} & 0.000513 \\ \hline
+ \text{\BoringGalaxy{}} & \text{BHNS} & 0.00162 \\
+ \text{\ExcitingGalaxy{}} & \text{BHNS} & 0.00195 \\
+ \text{\DwarfOne} & \text{BHNS} & 0.00217 \\
+ \text{\DwarfTwo} & \text{BHNS} & 0.00182\\  \hline
 \end{tabular}
@@
 \section{Implications for transient multimessenger astronomy}
+\label{sec:Discussion}
 
@@
 \section{Conclusions}
+\label{sec:conclude}
 
@@
 For binary black hole mergers in particular, we show that the present-day binary black hole coalescence rate can vary by factors of several in otherwise
-similar present-day environments.   Our calculations supports and extends prior investigations which demonstrated both
+similar present-day environments.   Our calculations support and extend prior investigations which demonstrated both
 that black hole merger rates depend sensitively on low-metallicitiy environments
-\cite{PSellipticals,popsyn-LowMetallicityImpact2b-StarTrackRevised-2013,gwastro-EventPopsynPaper-2016}.   More broadly,
+\citep[see,e.g.][]{PSellipticals,popsyn-LowMetallicityImpact2b-StarTrackRevised-2013,gwastro-EventPopsynPaper-2016}.   More broadly,
 because compact binaries can merge long after they form, their host galaxy can evolve substantially in composition
@@
 complementary to the  population-based approach reported in
-\cite{2016arXiv160508783L}.     More broadly, our analysis reflect  similar theoretical studies performed in the interpretation of, for
+\cite{2016arXiv160508783L}.     More broadly, our analysis reflects  similar theoretical studies performed in the interpretation of, for
 example, long GRBs and their host galaxies. 

### 2016-07-12 paper/paper.tex
section 2 changes

@@
 On the other hand, gravitational wave detectors can perform high-precision sky and volumetric localization \citep{2016LRR....19....1A,2016arXiv160307333S}.  As GW detector
-networks increase in sensitivity, these localizations will allow statistical and, eventually, unique identification of
+networks increase in number and sensitivity, these localizations will allow statistical and, eventually, unique identification of
 host galaxies directly, even without associated electromagnetic emission.
@@
 
-\section{Cosmological simulations produce two distinct Milky-Way-like galaxies}
+\section{Cosmological simulations}% produce two distinct Milky-Way-like galaxies}
 \label{sec:sims}
@@
 %maybe move the below section to later and/or consolidate
-One simulation we report here, h258,
-involves the formation of a Milky Way-like disk galaxy whose
-progenitors undergo major mergers at $z = 2$ and $z = 0.8$.  This
-simulation has been previously discussed by
-\citet{Governato09,Bellovary10,Bellovary11,Brooks11}; however we have
-re-run the simulation at a factor of two higher in spatial resolution
-and additionally included new physics including a prescription for
-cooling by molecular hydrogen \citet{Christensen12}.
+%One simulation we report here, h258,
+%involves the formation of a Milky Way-like disk galaxy whose
+%progenitors undergo major mergers at $z = 2$ and $z = 0.8$.  This
+%simulation has been previously discussed by
+%\citet{Governato09,Bellovary10,Bellovary11,Brooks11}; however we have
+%re-run the simulation at a factor of two higher in spatial resolution
+%and additionally included new physics including a prescription for
+%cooling by molecular hydrogen \citet{Christensen12}.
 
-We selected our simulated region of interest from a 50 Mpc volume of
+We selected our simulated regions of interest from a volume of
 uniform resolution, and resampled the region at very high
@@
 involved in galaxy evolution in our selected region while still
-including large-scale torques from cosmic structure.  We use
-WMAP3 cosmology \citep{WMAP3} and model the ionizing UV background
-with the prescription from \citet{Haardt96}.  Stars form
+including large-scale torques from cosmic structure.  Our cosmological parameters are $\Omega_0 = 0.24$, $\Omega_{\rm baryon} = 0.04$, $\Lambda = 0.76$, h = 0.73, $\sigma_8 = 0.77$ 
+ \citep{WMAP3} and model the ionizing UV background
+with the prescription from \citet{Haardt96}.
+Our interstellar medium (ISM) model includes the non-equilibrium formation and destruction of H$_2$, which is incorporated in the cooling model along with metal lines \citep{Christensen12}.
+Stars form
 probabilistically from gas particles which meet density ($n_{min} =
-10$ amu cm$^{-3}$) and temperature ($T_{max} = 10^4$ K) thresholds. If a gas
+0.1$ amu cm$^{-3}$) and temperature ($T_{max} = 10^3$ K) thresholds. If a gas
 particle meets these criteria, it has a likelihood of forming a star
@@
 \citep{Kennicutt89};  X$_{\rm H_2}$ is the molecular hydrogen fraction of the gas particle; $m_{star}$ and $m_{gas}$ are the star and gas
-particle masses;\footnote{In our high-resolution simulations, each gas particle starts with a mass
-  $m_{gas,0}=26,676 M_\odot$, gaining mass from feedback and losing it to star formation.  Each star particle, when
-  formed, has $1/3$ of the progenitor mass of the forming gas particle.  See \cite{Christensen10} for a discussion
-of resolution issues in these SPH simulations.} $t_{form}$ is the dynamical time for the gas
+particle masses; %\footnote{In our high-resolution simulations, each gas particle starts with a mass
+%  $m_{gas,0}=26,676 M_\odot$, gaining mass from feedback and losing it to star formation.  Each star particle, when
+%  formed, has $1/3$ of the progenitor mass of the forming gas particle.  See \cite{Christensen10} for a discussion
+%of resolution issues in these SPH simulations.} 
+ $t_{form}$ is the dynamical time for the gas
 particle; and $\Delta t$ is the time between star formation episodes,
-which we set to 1 Myr.  We model supernova feedback using the
+which we set to 1 Myr.
+A detailed study of different interstellar medium (ISM) models and the resulting star formation properties by \citet{Christensen14a} demonstrates that this model allows star formation to occur in dense clumps of gas, in regions that correspond best to star formation in observed galaxies.
+
+We model supernova feedback using the
 blastwave formalism described in \citet{McKee77} and implemented in
@@
 work, we are focusing on the primary (i.e. most massive) galaxy at any
-given redshift, which serves as the progenitor to our $z = 0$ Milky
-Way-like galaxy.
+given redshift.%, which serves as the progenitor to our $z = 0$ Milky
+%Way-like galaxy.
 
@@
 We have also employed the results of detailed simulations for several dwarf galaxies: \DwarfOne{}, \DwarfTwo{}, and others.
+The simulation of h603 consists of a low-mass disk galaxy (qualitatively similar to M33).
+It has a virial mass of $3.4 \times 10^{11} \msun$, stellar mass of $7.8 \times 10^9 \msun$, and maximum circular velocity of 111 km s$^{-1}$.
+We also include a dwarf galaxy, h516, which has a disk with irregularly distributions star formation, with a virial mass of $3.8 \times 10^{10}\msun$, stellar mass $2.5 \times 10^8 \msun$, and maximum circular velocity of 65 km s$^{-1}$.
 
@@
 %% control =?
+
+\begin{figure*}
+\includegraphics[width=\columnwidth]{Figures/dwarf1}
+\includegraphics[width=\columnwidth]{Figures/dwarf1}
+\caption{\label{fig:GalaxyImages}Synthetic SDSS $gri$ images of our two lower-mass galaxies, h603 (left) and h516 (right - placeholder image, need image of h516), created with \textsc{SUNRISE} \citep{Jonsson06}.
+\label{fig:images}
+}
+\end{figure*}
 

### 2016-07-12 paper/paper.tex
Minor changes

--- 2016-07-12 paper/paper.tex
@@
 
-  The simulation h258 (Exciting Galaxy), on the other hand, has a much
+  The simulation h258, on the other hand, has a much
   more active merger history.  At $z = 1$ there is a 1:1 merger event;
@@
   of the metal properties of these galaxies does differ - between 0.5
-  and 6 Gyr, h277 hosts a {\bf modestly} more metal-rich population than
-  h258. \editremark{The difference isn't all that big, I want to address it without sounding foolish.}
+  and 6 Gyr, h277 hosts a \emph{modestly}  more metal-rich population than
+  h258.   For most astrophysical processes, the small metallicity difference illustrated here will have no impact on
+  present-day observables.  However, for binary black holes depend sensitively on all low metallicity star formation
+  over cosmic time; as we show below, these small differences can have an observable impact at present.
 
@@
 %
+For binary black holes forming at metallicities $Z<0.25 Z_\odot$, we adopt the same prescription.  To be qualitatively consistent
+with detailed binary evolution calculations at near-solar metallicity (e.g., \abbrvPSellipticals{} and
+\cite{gwastro-EventPopsynPaper-2016}), for 
+black holes forming at metallicities $Z>0.25 Z_\odot$ we adopt a much more uniform delay time distribution, so 
+coalescing black hole binaries have nearly uniform delay time distribution between $100\unit{Myr}$ and
+$13\unit{Gyr}$\editremark{checkme again - a little hacky}; that said,  our conclusions are not sensitive to this choice.
+%
 For suitable choices of parameter, our phenomenological response function is qualitatively consistent with the results of detailed simulations of binary
@@
 % so the ratio should be a factor of about 7x higher due to this region.
-Therefore, though only a fraction \textbf{XXX} of all star formation occurs in this epoch, by this order of magnitude
+Therefore, because only a fraction of order $10\%$ \textbf{[checkme-JILLIAN?]} of all star formation occurs in this epoch, by this order of magnitude
 argument, the overall number of
-present-day coalescing binary black holes in our two galaxies is expected to differ by as much as a factor of order \textbf{only
-a few percent.}  
+present-day coalescing binary black holes in our two galaxies is expected to differ by of order ten percent.
+% 0.9 + 0.1*7/2
 %
 Using the concrete phenomenological calculations described above, we in fact find
-$r_{D,\BoringGalaxy{}}/r_{D,\ExcitingGalaxy{}}=\textbf{ZZZ}$.
+$(r_{D}/M)_{\BoringGalaxy{}}/(r_{D}/M)_{\ExcitingGalaxy{}}\simeq 0.9$.
 
@@
 with similar present-day mass but different star formation histories could be.   In particular, dwarf galaxies have an
-exceptionally large fraction of low-metallicity star formation in their history \cite{Kirby13}.  The precise details of their chemical
+exceptionally large fraction of low-metallicity star formation in their history \citep{Kirby13}.  The precise details of their chemical
 evolution can modify their present-day binary black hole binary populations by factors of order a few, despite  adopting
@@
 \begin{tabular}{|ll|l|}\hline
- \text{\BoringGalaxy{}} & \text{BHBH} & 1.05 \\
- \text{\ExcitingGalaxy{}} & \text{BHBH} & 1.11 \\
- \text{\DwarfOne} & \text{BHBH} & 3.14 \\
- \text{\DwarfTwo} & \text{BHBH} & 10.3 \\ \hline
- \text{\BoringGalaxy{}} & \text{NSNS} & 0.000425 \\
- \text{\ExcitingGalaxy{}} & \text{NSNS} & 0.000513 \\ \hline
- \text{\BoringGalaxy{}} & \text{BHNS} & 0.00162 \\
- \text{\ExcitingGalaxy{}} & \text{BHNS} & 0.00195 \\
- \text{\DwarfOne} & \text{BHNS} & 0.00217 \\
- \text{\DwarfTwo} & \text{BHNS} & 0.00182\\  \hline
+ \text{\BoringGalaxy} & \text{BHBH} & 0.0996 \\
+ \text{\ExcitingGalaxy} & \text{BHBH} & 0.0912 \\
+ \text{\DwarfOne} & \text{BHBH} & 0.212 \\
+ \text{\DwarfTwo} & \text{BHBH} & 0.76 \\
+ \text{\BoringGalaxy} & \text{BHNS} & 0.000219 \\
+ \text{\ExcitingGalaxy} & \text{BHNS} & 0.000264 \\
+ \text{\DwarfOne} & \text{BHNS} & 0.000275 \\
+ \text{\DwarfTwo} & \text{BHNS} & 0.000235 \\
+ \text{\BoringGalaxy} & \text{NSNS} & 0.0000592 \\
+ \text{\ExcitingGalaxy} & \text{NSNS} & 0.0000715 \\
+\hline
 \end{tabular}

### 2016-07-12 paper/paper.tex
Fixing

@@
 
-  Due to the differences in merger histories, the metallicity
+  Due to the differences in merger histories, the star formation histories and metallicity
   evolution of h258 and h277 also differ at early times.  Figure
-  \ref{fig:TwoGalaxies} shows the history of the mean metallicity of
+  \ref{fig:TwoGalaxies} shows the star formation history (left panel) and metallicity evolution (right panel) of the two galaxies.
+The star formation histories are quite different at early times, where h277 has larger bursts of star formation between 2-4 Gyr, but h258 has a large burst at $\sim 6$ Gyr during a major merger.
+The right panel shows the mean metallicity of
   recently formed stars vs time (thick solid lines), where we define

### 2016-07-12 paper/paper.tex
small changes

@@
 This paper is organized as follows. 
-In \S \ref{sec:sims}, we describe detailed hydrodynamical simulations of  two galaxies.  Though these two
-galaxies are at  present similar to the Milky Way, we
+In \S \ref{sec:sims}, we describe detailed hydrodynamical simulations of  several galaxies, including two of Milky Way-mass and two dwarfs.
+Though the two Milky Way-like galaxies are morphologically similar at $z = 0$, we
 show that their star formation and chemical evolution history have subtle but important differences due to their
@@
 rate, we have chosen two simulations which are extremely similar at $z
-= 0$ but differ strongly in their merger histories; see Figure \ref{fig:GalaxyImages}.
+= 0$ but differ strongly in their merger histories; see Figure \ref{fig:images}.
 
@@
 We also include a dwarf galaxy, h516, which has a disk with irregularly distributions star formation, with a virial mass of $3.8 \times 10^{10}\msun$, stellar mass $2.5 \times 10^8 \msun$, and maximum circular velocity of 65 km s$^{-1}$.
+Images of these galaxies are shown in Figure \ref{fig:dwarfimages}.
+\jillianremark{ {\bf Put SFH and metal hist in Figure 4.
+Discuss.}}
 
@@
 \caption{\label{fig:GalaxyImages}Synthetic SDSS $gri$ images of our two lower-mass galaxies, h603 (left) and h516 (right - placeholder image, need image of h516), created with \textsc{SUNRISE} \citep{Jonsson06}.
-\label{fig:images}
+\label{fig:dwarfimages}
 }
@@
 JB acknowledges generous support  from the Helen Gurley Brown Trust.
+
+A portion of this work was performed at the Aspen Center for Physics, which is supported by National Science Foundation grant PHY-1066293.
 \end{acknowledgements}

### 2016-07-12 paper/paper.tex
blah

@@
 \begin{document}
-\title{Details matter: Similar host galaxies can harbor different merging compact binary populations} 
+%\title{Details matter: Similar host galaxies can harbor different merging compact binary populations} 
+\title{The effects of host galaxy properties on merging compact binaries detectable by LIGO}
 \author{ J. Bellovary}
@@
 % - existence proof by example .. not an attempt to solve the general problem we raise
-Galaxy formation
-simulations can reproduce present-day galaxies with notably different assembly and star formation histories.  
+Cosmological simulations of galaxy formation can produce present-day galaxies with a large range assembly and star formation histories.
+A detailed study of the metallicity evolution and star formation history of such simulations can assist in predicting LIGO-detectable compact object binary mergers.
 Recent simulations of compact binary evolution suggest the compact object merger rate depends
@@
 compact binary populations.  As an example, we demonstrate how the coalescing binary black hole population can differ by
-factors of order  unity, and even binary neutron star populations differ by tens of percent.  
+factors of order  unity, and even binary neutron star populations differ by tens of percent.  \jillianremark{add sentence about mass dependence (more in dwarfs).}
 We discuss the implications for transient multimessenger astronomy with compact binary sources. 

### 2016-07-12 paper/paper.tex
Updating

@@
 \begin{document}
+%<<<<<<< Updated upstream
 %\title{Details matter: Similar host galaxies can harbor different merging compact binary populations} 
 \title{The effects of host galaxy properties on merging compact binaries detectable by LIGO}
+\author{R.\ O'Shaughnessy}
+\affiliation{Center for Computational Relativity and Gravitation, Rochester Institute of Technology, Rochester, NY 14623, USA}
+\email{oshaughn@mail.rit.edu}
 \author{ J. Bellovary}
@@
 \email{jbellovary@qcc.cuny.edu}
-\author{R.\ O'Shaughnessy}
-\affiliation{Center for Computational Relativity and Gravitation, Rochester Institute of Technology, Rochester, NY 14623, USA}
-\email{oshaughn@mail.rit.edu}
 \begin{abstract}
@@
 Recent simulations of compact binary evolution suggest the compact object merger rate depends
-sensitively on the progenitor's metallicity, to the extent that rare low-metallicity star formation during galaxy
+sensitively on the progenitor's metallicity.  Rare low-metallicity star formation during galaxy
 assembly can produce more detected compact binaries than typical star formation.   
@@
 compact binary populations.  As an example, we demonstrate how the coalescing binary black hole population can differ by
-factors of order  unity, and even binary neutron star populations differ by tens of percent.  \jillianremark{add sentence about mass dependence (more in dwarfs).}
+factors of order  unity, and even binary neutron star populations differ by tens of percent.  
+%
+We also demonstrate by concrete example the extent to which dwarf galaxies overabundantly produce compact binary
+mergers, particularly binary black holes. 
 We discuss the implications for transient multimessenger astronomy with compact binary sources. 
@@
 
+%\editremark{Jillian}: Add me but note conflict \cite{Somerville15}, etc or \cite{2015ARAA..53...51S}
+
 %\editremark{We will be very careful to specify how SFR and metallicity are measured, backtracking}
@@
 %Add me: \cite{Kirby13}
-\editremark{Jillian}: Add me but note conflict \cite{Somerville15}, etc or \cite{2015ARAA..53...51S}
 
@@
 %     ... which will enable new physics
-Gravitational waves have been detected from  coalescing  black hole binaries \citep{DetectionPaper,LIGO-O1-BBH}. 
+Gravitational waves have been detected from  coalescing  black hole binaries \citep{DiscoveryPaper,LIGO-O1-BBH}. 
 Over the next few years, ground-based gravitational wave detectors like LIGO 
@@
 histories, which may result in differences in compact object merger
-rates.  To investigate whether galaxy history affects the GRB event
+rates.  To investigate whether galaxy history affects the compact binary event
 rate, we have chosen two simulations which are extremely similar at $z
@@
   h258.   For most astrophysical processes, the small metallicity difference illustrated here will have no impact on
-  present-day observables.  However, for binary black holes depend sensitively on all low metallicity star formation
+  present-day observables.  However,  the population of binary black holes  depends sensitively on all low metallicity star formation
   over cosmic time; as we show below, these small differences can have an observable impact at present.
@@
 Our goal in this work is to estimate the \emph{ratio} of compact binaries that should be merging, at present, in the two
-simulated galaxies described above.
+simulated Milky-Way analog galaxies described above.
 
@@
 detection in an individual galaxy, motivated by
-the detailed studies of  \abbrvPSgrb{} and \abbrvPSellipticals; \jillianremark{this is first mention of PSG and PSE, define} similar approaches have been used by
+the detailed studies of  \abbrvPSgrb{} (\cite{PSgrbs-popsyn}) and \abbrvPSellipticals{} (\cite{PSellipticals});  similar approaches have been used by
 \cite{2016arXiv160508783L} and others.
@@
 evolution calculations presented in \cite{popsyn-LowMetallicityImpact2-StarTrackRevised-2012} and
-\cite{popsyn-LowMetallicityImpact2c-StarTrackRevised-2014}; see, e.g., their Table 1 and Figures 5-7.    For neutron
+\cite{popsyn-LowMetallicityImpact2c-StarTrackRevised-2014}.  For neutron
 stars, we adopt a fiducial neutron star mass of $1.4 M_\odot$ at all metallicities.  For BH-NS binaries, we adopt a
-highly simplified model: the black hole masses are uniformly \editremark{fixme?} drawn from $5 M_\odot$ to the maximum 
+highly simplified model: the black hole masses are uniformly  drawn from $5 M_\odot$ to the maximum 
 black hole mass $M_{max}(Z)$ allowed by
@@
 vary slightly as $Z/Z_\odot$ decreases, from a lower limit of $3 M_\odot$ near solar metallicity to an upper limit of
-$4.3 M_\odot$ in low-metallicity environments.  Finally, for binary black holes, we assume  comparable-mass binaries
+$4.3 M_\odot$ in low-metallicity environments.  Not least because the average chirp mass for BH-NS simply cannot vary
+dramatically, given the functional form of $\mc$, our results do not depend sensitively on the choice of black hole mass
+distribution.  Finally, for binary black holes, we assume  comparable-mass binaries
 form ($m_1=m_2$), with the distribution of component masses chosen to be $\propto m_1^{-p}$ 
@@
  (see, e.g.\cite{popsyn-LIGO-SFR-2008}, \abbrvKBLowZa).  For the purposes of illustration, we adopt a  concrete scale
-factor  $
-\lambda_0 = 10^{-3}/M_\odot $,  a typical value suitable for neutron star compact binaries (see \abbrvPSgrb{}, \abbrvPSellipticals, and \abbrvKBLowZa).
+factor  $\lambda_0 = 10^{-3}/M_\odot $,  a typical value suitable for neutron star compact binaries (see \abbrvPSgrb{},
+\abbrvPSellipticals, and \abbrvKBLowZa).
+% DOCUMENTATION FOR CHOICE
+%    - classic figures on event rate vs metallicity from Dominik #1.5  (see WVU talk slide 16)
+%        2012-11-WVU/2012-11-WVU-Keynote.key 
+%      Based on event rate changing by x10^4 over 1 order of magnitude. This includes both mass factor and
+%      intrinsic factor.  Mass factor changes by x10, so intrinsic factor is x10^3 over x10 in Z, so a=3 is better.
+%    - saturation will occur after a factor of 10^4
+%    - Can also calibrate to change in event rate from Z sun to 0.1Zsun (i.e., a factor of 10 for model B)
+%      a=1.  This is MUCH BETTER DOCUMENTED and MORE CONSERVATIVE.
+To calibrate the exponent, based on Tables 2 and 3 of
+\cite{popsyn-LowMetallicityImpact2-StarTrackRevised-2012} (model B), for binary black holes and black hole-neutron star
+binaries, we adopt $a=1$, while for binary neutron stars we adopt $a=0$; see, e.g., their Table 1 and Figures
+5-7.\footnote{This choice of exponent provides an extremely conservative assessment of the impact of low Z
+\cite[see,e.g.][]{2012CQGra..29n5011O,gwastro-EventPopsynPaper-2016}. } 
 %
@@
 %
-For binary black holes forming at metallicities $Z<0.25 Z_\odot$, we adopt the same prescription.  To be qualitatively consistent
-with detailed binary evolution calculations at near-solar metallicity (e.g., \abbrvPSellipticals{} and
+For binary black holes forming at metallicities $Z<0.25 Z_\odot$, we adopt the same prescription.  
+For binary black holes formed near solar metallicity, the delay time distribution can favor long delays between birth
+and merger, as demonstrated in Figures 9 and 10 of \abbrvPSellipticals{}.  [Figure 2 of  \cite{2016arXiv160508783L} is
+  an extreme example of this well-known trend.] 
+To be qualitatively consistent with detailed binary evolution calculations at near-solar metallicity (e.g., \abbrvPSellipticals{} and
 \cite{gwastro-EventPopsynPaper-2016}), for 
@@
 
-For binary black holes formed near solar metallicity, the delay time distribution can favor long delays between birth
-and merger, as demonstrated in Figures 9 and 10 of \abbrvPSellipticals{}.  [Figure 2 of  \cite{2016arXiv160508783L} is
-  an extreme example of this well-known trend.]  In practice, however, binary black holes produced near solar
-metallicity correspond to a relatively small proportion of the overall population; we therefore neglect this
-effect\footnote{may want to change}.
-
 % POINT: Net effect
@@
 \begin{eqnarray}
- r_D \propto  \int d\log Z  \int _{13 \unit{Gyr}}^0dt  V(Z) \lambda(Z) \frac{dP}{dt}(t) \dot{M} p(\log Z|t)
+ r_D \propto  \int d\log Z  \int _{13 \unit{Gyr}}^0dt  V(Z) \lambda(Z) \frac{dP_t}{dt}(t) \dot{M} p(\log Z|t)
 \end{eqnarray}
@@
 \begin{tabular}{|ll|l|}\hline
- \text{\BoringGalaxy} & \text{BHBH} & 0.0996 \\
- \text{\ExcitingGalaxy} & \text{BHBH} & 0.0912 \\
- \text{\DwarfOne} & \text{BHBH} & 0.212 \\
- \text{\DwarfTwo} & \text{BHBH} & 0.76 \\
+ \text{\BoringGalaxy} & \text{BHBH} & 0.012 \\
+ \text{\ExcitingGalaxy} & \text{BHBH} & 0.0116 \\
+ \text{\DwarfOne} & \text{BHBH} & 0.0207 \\
+ \text{\DwarfTwo} & \text{BHBH} & 0.0524 \\
  \text{\BoringGalaxy} & \text{BHNS} & 0.000219 \\
@@
  \text{\DwarfTwo} & \text{BHNS} & 0.000235 \\
- \text{\BoringGalaxy} & \text{NSNS} & 0.0000592 \\
- \text{\ExcitingGalaxy} & \text{NSNS} & 0.0000715 \\
-\hline
+ \text{\BoringGalaxy} & \text{NSNS} & 0.000206 \\
+ \text{\ExcitingGalaxy} & \text{NSNS} & 0.000228 \\\hline
 \end{tabular}

### 2016-07-12 python/sfr_to_rate_nobins_BBH.py
Updating results table, code with new choice for exponent (with documentation), documentation for exponent, etc

@@ -198,9 +198,9 @@ def time_function(time_exp):
 
 
 if opts.type_bbh:
-    opts.Z_exponent = 2
+    opts.Z_exponent = 1
 if not opts.type_bbh and not opts.type_bhns:
-    opts.Z_exponent =0   # checkme
+    opts.Z_exponent =1   # checkme
 if opts.type_bhns:
     opts.Z_exponent =0   # checkme
 

### 2016-07-12 paper/paper.tex
Pushing updated

@@
 form ($m_1=m_2$), with the distribution of component masses chosen to be $\propto m_1^{-p}$ 
- between $3 M_\odot$ and $M_{max}(Z)$ and zero otherwise, adopting a fiducial exponent $p=2$; see, e.g.,
+ between $5 M_\odot$ and $M_{max}(Z)$ and zero otherwise, adopting a fiducial exponent $p=2$; see, e.g.,
 \cite{popsyn-LowMetallicityImpact2b-StarTrackRevised-2013}.    For binary black holes, this means  the
@@
 binaries, we adopt $a=1$, while for binary neutron stars we adopt $a=0$; see, e.g., their Table 1 and Figures
-5-7.\footnote{This choice of exponent provides an extremely conservative assessment of the impact of low Z
-\cite[see,e.g.][]{2012CQGra..29n5011O,gwastro-EventPopsynPaper-2016}. } 
+5-7. This choice of exponent provides an extremely conservative assessment of the impact of low Z
+\cite[see,e.g.,][]{2012CQGra..29n5011O,gwastro-EventPopsynPaper-2016}. 
+%% Detailed calculations suggest the exponent varies
+%% smoothly with metallicity, such that $d\ln \lambda/d\ln Z$ is convex.
+%%  } 
 %
@@
   histories can easily produce factors of order unity difference in galaxies with otherwise indistinguishable
-  present-day properties.\editremark{do we have another example}
+  present-day properties.
 
@@
 %  2014arXiv1407.3796S : implications for nucleosynthesis
-\cite{2013ApJ...776...18F,2014ARAA..52...43B}. 
+\citep{2013ApJ...776...18F,2014ARAA..52...43B}. 
 On the other hand, particularly during the epoch of galaxy formation, galaxies are well-mixed: stars and adjacent gas generally do not have
@@
 %
-For example, in several cases the metallicity of gas neighboring a long GRB (\citet{ 2008AJ....135.1136M}; \citet{2010AJ....140.1557L}
-\editremark{links}), short GRB (\editremark{XXX}), or SN has been directly measured.
+For example, in several cases the metallicity of gas neighboring a long GRB (\citet{ 2008AJ....135.1136M};
+\citet{2010AJ....140.1557L}) has been directly measured.  % , short GRB (\editremark{XXX}), or SN has been directly measured.
 %
@@
 %
-Finally,  on a host-by-host basis, the delay time between birth and merger has been constrained for long GRBs (\editremark{XXX}), short GRBs \citep{2010ApJ...725.1202L}, and
-  SN Ia \citep{2011MNRAS.412.1508M}.  
+Finally,  on a host-by-host basis, the delay time between birth and merger has been constrained for
+% long GRBs (\editremark{XXX}), 
+short GRBs \citep{2010ApJ...725.1202L}
+ and
+  SN Ia \citep{2011MNRAS.412.1508M}; see, e.g., the review in  \cite{2014ARAA..52...43B}.
 %

### 2016-07-12 python/sfr_to_rate_nobins_BBH.py

@@ -40,6 +40,8 @@ opts = parser.parse_args()
 if not opts.starmetal_file:
     print "  Please specify an SFR file "
 
+Mbh_min= 5 # minimum mass of black holes, as allowed in the text
+
 
 # Maximum mass information (single BH)
 
@@ -85,8 +87,8 @@ def average_func(func,input_probability_distribution):
 def make_uniform_func(metal_now):
     MmaxNow = maxbh_of_Z(metal_now)
 #    print MmaxNow
-    nm = 1./(MmaxNow - 3)  # normalization
-    return lambda x, Nm = nm, A = MmaxNow: np.where( np.logical_and(x<A , x > 3), nm* np.ones(len(x)), np.zeros(len(x)))
+    nm = 1./(MmaxNow - Mbh_min)  # normalization
+    return lambda x, Nm = nm, A = MmaxNow: np.where( np.logical_and(x<A , x > Mbh_min), nm* np.ones(len(x)), np.zeros(len(x)))
 
 
 def make_power_func(metal_now,mass_exponent=2):
@@ -94,7 +96,7 @@ def make_power_func(metal_now,mass_exponent=2):
     ret, err = quad( lambda x: np.power(x,-1*mass_exponent),3,MmaxNow)
     nm  =ret
 #    print metal_now, MmaxNow, nm
-    return lambda x, Nm = nm, A = MmaxNow,p=mass_exponent: np.where( np.logical_and(x<A , x > 3), nm* np.power(x,-1.*p), np.zeros(len(x)))
+    return lambda x, Nm = nm, A = MmaxNow,p=mass_exponent: np.where( np.logical_and(x<A , x > Mbh_min), nm* np.power(x,-1.*p), np.zeros(len(x)))
 
 def Vaveraged_bns(Z):
     mc_av =mc(1.4, 1.4)

### 2016-07-12 paper/paper.tex
UPDATE updates

--- 2016-07-12 paper/paper.tex
@@
 Using detailed simulations of galaxy and chemical evolution, we demonstrate by example that galaxies with similar present-day appearance can host distinctly different
-compact binary populations.  As an example, we demonstrate how the coalescing binary black hole population can differ by
+compact binary populations \jillianremark{ UPDATE}.  As an example, we demonstrate how the coalescing binary black hole population can differ by
 factors of order  unity, and even binary neutron star populations differ by tens of percent.  
@@
 The host galaxies of gravitational wave sources will be identified, either directly or statistically.  
-On the one hand, addition to the strong gravitational wave signal, mergers of neutron stars are expected to  frequently be accompanied by detectable
-electromagnetic radiation  via a number of  mechanisms, including a strong but tightly beamed
-ultrarelativistic jet and weakly-beamed but more isotropic thermal radiation from an expanding hot shell
-\citep[see,e.g.,][and references therein]{2013PhRvL.111r1101C,short-grb-GWCoincidenceEM-MetzgerBerger2011}.  
+If the event is a merger of at least one neutron star, it is expected to be accompanied by detectable
+electromagnetic radiation  via a number of  mechanisms \citep[see][and references therein]{Metzger16} in addition to the strong gravitational wave signal. % including a strong but tightly beamed
+%ultrarelativistic jet and weakly-beamed but more isotropic thermal radiation from an expanding hot shell
+%\citep[see,e.g.,][and references therein]{2013PhRvL.111r1101C,short-grb-GWCoincidenceEM-MetzgerBerger2011}.  
 % People we can't afford the space to cite, alas:
@@
 %    - Shibata group/Koutarou
-In addition to providing a wealth of information about the merger event itself, a multimessenger detection will pin down
-the sky position and therefore approximate birthplace of each merging binary.    
+%  In addition to providing a wealth of information about the merger event itself, 
+A multimessenger detection will pin down
+the sky position and therefore approximate birthplace of each merging binary \cite{Nissanke13}.    
 %
-On the other hand, gravitational wave detectors can perform high-precision sky and volumetric localization \citep{2016LRR....19....1A,2016arXiv160307333S}.  As GW detector
+Even in the absence of well-identified electromagnetic counterparts, host galaxy information is still available from gravitational wave localization alone \citep{2016LRR....19....1A,2016arXiv160307333S}.
+As GW detector
 networks increase in number and sensitivity, these localizations will allow statistical and, eventually, unique identification of
@@
 can depend sensitively on the galaxy's assembly history, in a manner which is far from apparent from its present-day
-properties.    We also demonstrate that even the coalescence rates of binary neutron stars (NSNS) and black hole-neutron
+properties. \jillianremark{ UPDATE}   We also demonstrate that even the coalescence rates of binary neutron stars (NSNS) and black hole-neutron
 star (BH-NS) binaries also depend surprisingly sensitively on the assembly history of each galaxy. 
@@
 can depend sensitively on mass; for example, for binary black holes, the ratio of  $(\lambda V)_{\BoringGalaxy{}}/(\lambda
-V)_{\ExcitingGalaxy{}} \simeq 7$.    However, in this same epoch, the star formation rate in the \ExcitingGalaxy{} (low-metallicity)
+V)_{\ExcitingGalaxy{}} \simeq 7$.    \jillianremark{ UPDATE} However, in this same epoch, the star formation rate in the \ExcitingGalaxy{} (low-metallicity)
 galaxy is smaller, by a factor of roughly 2.
@@
 
-The close agreement between the two galaxies' binary black hole populations  is entirely a
+The close agreement between the two galaxies' binary black hole populations \jillianremark{ UPDATE} is entirely a
 a numerical coincdence between the specific star formation rate and metallicities in these two galaxies.  The effects described here
@@
 
-For binary black hole mergers in particular, we show that the present-day binary black hole coalescence rate can vary by factors of several in otherwise
+For binary black hole mergers in particular, we show that the present-day binary black hole coalescence rate can vary by factors of several \jillianremark{ UPDATE} in otherwise
 similar present-day environments.   Our calculations support and extend prior investigations which demonstrated both

### 2016-07-12 paper/paper.tex
Pushing

@@
 can depend sensitively on mass; for example, for binary black holes, the ratio of  $(\lambda V)_{\BoringGalaxy{}}/(\lambda
-V)_{\ExcitingGalaxy{}} \simeq 7$.    \jillianremark{ UPDATE} However, in this same epoch, the star formation rate in the \ExcitingGalaxy{} (low-metallicity)
+V)_{\ExcitingGalaxy{}} \simeq 3$.\footnote{Adopting a more extreme exponent for the metallicity dependence ($a=2$) only
+  changes this ratio by of order $2$.}   However, in this same epoch, the star formation rate in the \ExcitingGalaxy{} (low-metallicity)
 galaxy is smaller, by a factor of roughly 2.
-% 1e-3:  V = 276, lambda= 400   
-% 2e-3:  V= 152.657625157, lambda = 100
+% 1e-3:  V = 475, lambda= 20   
+% 2e-3:  V= 318, lambda = 10
 % so the ratio should be a factor of about 7x higher due to this region.
@@
 
-The close agreement between the two galaxies' binary black hole populations \jillianremark{ UPDATE} is entirely a
+The close agreement between the two galaxies' binary black hole populations, determined by the anticorrelation between
+star formation rate and metallicity, may be a single example of a broad trend.  This anticorrelation could cause
+galaxies with similar present-day properties to always have similar present-day binary black hole populations,
+regardless of their detailed assembly histories.
+However, it is also possible that this close agreement is entirely a
 a numerical coincdence between the specific star formation rate and metallicities in these two galaxies.  The effects described here
@@
   histories can easily produce factors of order unity difference in galaxies with otherwise indistinguishable
-  present-day properties.
+  present-day properties.   \editremark{Do we have more examples?}
 

### 2016-07-12 paper/paper.tex
redo sect. 5

--- 2016-07-12 paper/paper.tex
@@
 To characterize the frequency of different star-forming conditions, we use our cosmological simulations of Milky Way-like galaxies, which provide each galaxy's star formation rate
-$\dot{M}_*$ and star formation metallicity distribution $p(\log Z|t)$ over time.
+$\dot{M}_*$ and metallicity distribution $p(\log Z|t)$ over time.
 
@@
 \begin{eqnarray}
- r_D \propto  \int d\log Z  \int _{13 \unit{Gyr}}^0dt  V(Z) \lambda(Z) \frac{dP_t}{dt}(t) \dot{M} p(\log Z|t)
+ r_D \propto  \int d\log Z  \int _{13 \unit{Gyr}}^0dt  V(Z) \lambda(Z) \frac{dP_t}{dt}(t) \dot{M}_* p(\log Z|t)
 \end{eqnarray}
@@
 %\editremark{recheck numbers: we are tweaking things, and Zsun is seemingly inconsistent in the two approaches }
- Our two galaxies have extremely similar star formation histories and metallicity evolution, particularly at late
+ Our two Milky Way-like galaxies have extremely similar star formation histories and metallicity evolution, particularly at late
  times.  
@@
 can depend sensitively on mass; for example, for binary black holes, the ratio of  $(\lambda V)_{\BoringGalaxy{}}/(\lambda
-V)_{\ExcitingGalaxy{}} \simeq 7$.    \jillianremark{ UPDATE} However, in this same epoch, the star formation rate in the \ExcitingGalaxy{} (low-metallicity)
+V)_{\ExcitingGalaxy{}} \simeq 7$.    \jillianremark{ UPDATE} However, in this same epoch, the star formation rate in the \ExcitingGalaxy{} (lower-metallicity)
 galaxy is smaller, by a factor of roughly 2.
@@
 
-Our calculations suggest that because of the often-long delays between formation and merger, combined with the
-propensity of low-metallicity gas to play an exceptionally significant role, unusually detailed information about each host galaxy could be required to realize the full
-potential of  associations between gravitational wave sources and their candidate host galaxies.
-%
-Fortunately,  with the advent of
-IFUs and position-resolved spectroscopy, observers can now probe the star formation history and metallicity of
-individual gas packets at different points in a galaxy.  
-%
-These highly-detailed probes will be essential tools to develop a comprehensive model of the galaxy's merger and
-chemical evolution history.
-
-Even when electromagnetic counterparts are available, the long delay times between binary formation and merger limit
-the prospects of detailed electromagnetic followup of individual event. 
-The metallicity of stars and gas adjacent to a specific merger event provides
-few direct, unambiguous clues to a compact binary merger's progenitors.  
+While a gravitational wave detection provides detailed information about merging objects (i.e.
+masses, spins, distance), we need further knowledge to understand the actual origins of the progenitors.
+Even when electromagnetic counterparts are available, the long delay times between binary formation and merger limit the prospects of examining the environment where the binary first formed.
 On the one hand, compact binaries are kicked by supernovae, moving substantially away from their birth position
-%  2014arXiv1407.3796S : implications for nucleosynthesis
 \cite{2013ApJ...776...18F,2014ARAA..52...43B}. 
-On the other hand, particularly during the epoch of galaxy formation, galaxies are well-mixed: stars and adjacent gas generally do not have
-similar chemical composition.  
-% POINT: Host tracer gas --we are optimistically assuming the metallicity 
-%  can be measured.  A seperate question is whether you can measure Z in the local environment at all.
-These mixing effects have been previously recognized as an obstacle to interpreting transient event spectra.  For
+On the other hand, particularly during the epoch of galaxy formation, galaxies are well-mixed: stars and adjacent gas generally do not have similar chemical composition.
+These mixing effects have been previously recognized as an obstacle to interpreting transient event spectra.
+For
 example,   \cite{2010MNRAS.402.1523P} previously demonstrated that absorbing gas neighboring transient events (there, long GRBs)
@@
 metallicities (there, using damped Lyman $\alpha$ absorbers in the host) do not tightly constrain the metallicity
-distribution of the progenitor; see, e.g., their Fig 3.
+distribution of the progenitor; see, e.g., their Fig 3.  Thus, the metallicity of stars and gas adjacent to a specific merger event provides
+few direct, unambiguous clues to a compact binary merger's progenitors.
+
+%Our calculations suggest that because of the often-long delays between formation and merger, combined with the
+%propensity of low-metallicity gas to play an exceptionally significant role, unusually detailed information about each host galaxy could be required to realize the full
+%potential of  associations between gravitational wave sources and their candidate host galaxies.
+%
+Fortunately,  with the advent of
+IFUs and position-resolved spectroscopy, observers can now probe the star formation history and metallicity of
+individual gas packets at different points in a galaxy.  
+These highly-detailed probes will be essential tools to develop a comprehensive model of the galaxy's merger and
+chemical evolution history.
+
+%Even when electromagnetic counterparts are available, the long delay times between binary formation and merger limit
+%the prospects of detailed electromagnetic followup of individual event. 
+%The metallicity of stars and gas adjacent to a specific merger event provides
+%few direct, unambiguous clues to a compact binary merger's progenitors.
+
+% POINT: Host tracer gas --we are optimistically assuming the metallicity 
+%  can be measured.  A seperate question is whether you can measure Z in the local environment at all.
+
 %
@@
 % POINT: 
-Despite the challenges involved in obtaining sufficient statistics, possibly requiring third-generation instruments to
+Thus, despite the challenges involved in obtaining sufficient statistics, possibly requiring third-generation instruments to
 obtain sufficiently many associations, past experience suggests  host galaxy associations

### 2016-07-12 paper/paper.tex

--- 2016-07-12 paper/paper.tex
@@
 \begin{document}
-%<<<<<<< Updated upstream
 %\title{Details matter: Similar host galaxies can harbor different merging compact binary populations} 
@@
 
-Our calculations suggest that because of the often-long delays between formation and merger, combined with the
-propensity of low-metallicity gas to play an exceptionally significant role, unusually detailed information about each host galaxy could be required to realize the full
-potential of  associations between gravitational wave sources and their candidate host galaxies.
-%
-Fortunately,  with the advent of
-IFUs and position-resolved spectroscopy, observers can now probe the star formation history and metallicity of
-individual gas packets at different points in a galaxy.  
-%
-These highly-detailed probes will be essential tools to develop a comprehensive model of the galaxy's merger and
-chemical evolution history.
-
-Even when electromagnetic counterparts are available, the long delay times between binary formation and merger limit
-the prospects of detailed electromagnetic followup of individual event. 
-The metallicity of stars and gas adjacent to a specific merger event provides
-few direct, unambiguous clues to a compact binary merger's progenitors.  
+While a gravitational wave detection provides detailed information about merging objects (i.e.
+masses, spins, distance), we need further knowledge to understand the actual origins of the progenitors.
+Even when electromagnetic counterparts are available, the long delay times between binary formation and merger limit the prospects of examining the environment where the binary first formed.
 On the one hand, compact binaries are kicked by supernovae, moving substantially away from their birth position
-%  2014arXiv1407.3796S : implications for nucleosynthesis
-\citep{2013ApJ...776...18F,2014ARAA..52...43B}. 
-On the other hand, particularly during the epoch of galaxy formation, galaxies are well-mixed: stars and adjacent gas generally do not have
-similar chemical composition.  
-% POINT: Host tracer gas --we are optimistically assuming the metallicity 
-%  can be measured.  A seperate question is whether you can measure Z in the local environment at all.
-These mixing effects have been previously recognized as an obstacle to interpreting transient event spectra.  For
+\cite{2013ApJ...776...18F,2014ARAA..52...43B}. 
+On the other hand, particularly during the epoch of galaxy formation, galaxies are well-mixed: stars and adjacent gas generally do not have similar chemical composition.
+These mixing effects have been previously recognized as an obstacle to interpreting transient event spectra.
+For
 example,   \cite{2010MNRAS.402.1523P} previously demonstrated that absorbing gas neighboring transient events (there, long GRBs)

### 2016-07-12 paper/paper.tex
Fixing abstract, intro

@@
 assembly can produce more detected compact binaries than typical star formation.   
-Using detailed simulations of galaxy and chemical evolution, we demonstrate by example that galaxies with similar present-day appearance can host distinctly different
-compact binary populations \jillianremark{ UPDATE}.  As an example, we demonstrate how the coalescing binary black hole population can differ by
-factors of order  unity, and even binary neutron star populations differ by tens of percent.  
+Using detailed simulations of galaxy and chemical evolution, we determine how sensitively the compact binary populations
+of galaxies   with similar
+present-day appearance depend on the details of their assembly.
+%% demonstrate by example that galaxies with similar present-day appearance can host distinctly different
+%% compact binary populations \jillianremark{ UPDATE}.  As an example, we demonstrate how the coalescing binary black hole population can differ by
+%% factors of order  unity, and even binary neutron star populations differ by tens of percent.  
 %
@@
 metallicity-dependent  phenomenological model to calculate the present-day rate and mass distribution of compact binary
-mergers from  a galaxy's known history.   In \S \ref{sec:results:BBH}, we use this model to demonstrate the binary black
-hole (BH-BH) coalescence rate
-can depend sensitively on the galaxy's assembly history, in a manner which is far from apparent from its present-day
-properties. \jillianremark{ UPDATE}   We also demonstrate that even the coalescence rates of binary neutron stars (NSNS) and black hole-neutron
-star (BH-NS) binaries also depend surprisingly sensitively on the assembly history of each galaxy. 
+mergers from  a galaxy's known history.   In \S \ref{sec:results:BBH}, we use this model to investigate  the compact
+binary  coalescence rate
+dependence on the galaxy's assembly history.   
+%% We also demonstrate that even the coalescence rates of binary neutron stars (NSNS) and black hole-neutron
+%% star (BH-NS) binaries also depend surprisingly sensitively on the assembly history of each galaxy. 
 In \S~\ref{sec:Discussion} we discuss the implications of our study for the interpretation of host galaxy associations

### 2016-07-12 paper/paper.tex
Pushgin

@@
 
-For binary black hole mergers in particular, we show that the present-day binary black hole coalescence rate can vary by factors of several \jillianremark{ UPDATE} in otherwise
-similar present-day environments.   Our calculations support and extend prior investigations which demonstrated both
+For binary black hole mergers in particular, we show that the present-day binary black hole coalescence rate for our two
+Milky-Way like galaxies is nearly identical, independent of their highly distinctive early-time formation histories.   
+This result comes as somewhat of a surprise. 
+%% can vary by factors of several \jillianremark{ UPDATE} in otherwise
+%% similar present-day environments. 
+Our calculations adopt the same framework as  prior investigations, which demonstrated 
 that black hole merger rates depend sensitively on low-metallicitiy environments
@@
 %% so system changes significantly from assembly conditions
+Nonetheless, the apparent anticorrelation between the star formation rate and metallicity evolution of our galaxies has
+led to similar late-time populations, despite substantial differences early on.
 

### 2016-07-13 paper/paper.tex
paper format
Push
Jillian's maybe last updates

@@
 We also demonstrate by concrete example the extent to which dwarf galaxies overabundantly produce compact binary
-mergers, particularly binary black holes. 
+mergers, particularly binary black holes, relative to more massive galaxies. 
 We discuss the implications for transient multimessenger astronomy with compact binary sources. 
@@
 A multimessenger detection will pin down
-the sky position and therefore approximate birthplace of each merging binary \cite{Nissanke13}.    
+the sky position and therefore approximate birthplace of each merging binary \citep{Nissanke13}.    
 %
@@
 and chemical evolution histories  \citep[see,e.g.][]{2009MNRAS.396..462K,2014MNRAS.444..336C,
-  Dalcanton09,Williams11,CALIFA}.  
+CALIFA,CALIFA2}.  
 % POINT: But is it useful?
@@
 distinctive merger histories.   To demonstrate
-these differences have a significant practical impact,  in \S \ref{sec:model}, we introduce a simple,
+these differences have a practical impact,  in \S \ref{sec:model}, we introduce a simple,
 metallicity-dependent  phenomenological model to calculate the present-day rate and mass distribution of compact binary
@@
 spatially and temporally resolved star formation, and determine not
-only the metallicity history of compact object progenitors, but also
-their dynamical evolution.  
+only the metallicity history of compact object progenitors.%, but also their dynamical evolution.  
 %maybe move the below section to later and/or consolidate
@@
 \citep{Kennicutt89};  X$_{\rm H_2}$ is the molecular hydrogen fraction of the gas particle; $m_{star}$ and $m_{gas}$ are the star and gas
-particle masses; %\footnote{In our high-resolution simulations, each gas particle starts with a mass
-%  $m_{gas,0}=26,676 M_\odot$, gaining mass from feedback and losing it to star formation.  Each star particle, when
-%  formed, has $1/3$ of the progenitor mass of the forming gas particle.  See \cite{Christensen10} for a discussion
-%of resolution issues in these SPH simulations.} 
+particle masses; \footnote{Gas particles start with a set mass
+ and may gain mass from feedback and lose it to star formation.  Each star particle, when
+  formed, has $1/3$ of the progenitor mass of the forming gas particle.  See \cite{Christensen10} for a discussion
+of resolution issues in SPH simulations.} 
  $t_{form}$ is the dynamical time for the gas
@@
 number of observed relations such as the mass-metallicity relation
-\citep{Brooks07,Kirby13}, the Tully-Fisher relation \citep{Governato09}, and
+\citep{Brooks07}, % JB: removed Kirby citation
+ the Tully-Fisher relation \citep{Governato09}, and
 the size-luminosity relation \citep{Brooks11}, as well as reproduce
@@
 \citep{Gill04,Knollmann09}, which identifies halos based on an
-overdensity criterion for a flat universe \citep{Gross97}.  For this
-work, we are focusing on the primary (i.e. most massive) galaxy at any
-given redshift.%, which serves as the progenitor to our $z = 0$ Milky
+overdensity criterion for a flat universe \citep{Gross97}.
+In each simulation, we are focusing on the stars which make up the primary (i.e.
+most massive) galaxy at $z = 0$.%, which serves as the progenitor to our $z = 0$ Milky
 %Way-like galaxy.
@@
 rates.  To investigate whether galaxy history affects the compact binary event
-rate, we have chosen two simulations which are extremely similar at $z
+rate, we have chosen two simulations which are morphologically similar at $z
 = 0$ but differ strongly in their merger histories; see Figure \ref{fig:images}.
@@
 \citep{Munshi13}, halo properties \citep{Zolotov09,Zolotov10}, and
-disk properties \citep{Brooks11}.  It has a virial mass of $M_{vir} =
+disk structure \citep{Brooks11}.  It has a virial mass of $M_{vir} =
 6.79 \times 10^{11} \msun$, stellar mass $M_* = 4.24 \times 10^{10}
@@
   progenitor galaxies actually experiences its own additional major
-  merger events around $z = 2$.  The combination of
+  merger events around $z = 3$.  The combination of
   the series of major mergers, plus a number of minor interactions and
@@
   evolution of h258 and h277 also differ at early times.  Figure
-  \ref{fig:TwoGalaxies} shows the star formation history (left panel) and metallicity evolution (right panel) of the two galaxies.
+  \ref{fig:TwoGalaxies} shows the star formation history (left panel) and metallicity evolution (right panel) of h277 (black) and h258 (red).
 The star formation histories are quite different at early times, where h277 has larger bursts of star formation between 2-4 Gyr, but h258 has a large burst at $\sim 6$ Gyr during a major merger.
@@
 
-We have also employed the results of detailed simulations for several dwarf galaxies: \DwarfOne{}, \DwarfTwo{}, and others.
+We have also employed the results of detailed simulations for two dwarf galaxies: \DwarfOne{} and \DwarfTwo{}.
 The simulation of h603 consists of a low-mass disk galaxy (qualitatively similar to M33).
 It has a virial mass of $3.4 \times 10^{11} \msun$, stellar mass of $7.8 \times 10^9 \msun$, and maximum circular velocity of 111 km s$^{-1}$.
-We also include a dwarf galaxy, h516, which has a disk with irregularly distributions star formation, with a virial mass of $3.8 \times 10^{10}\msun$, stellar mass $2.5 \times 10^8 \msun$, and maximum circular velocity of 65 km s$^{-1}$.
-Images of these galaxies are shown in Figure \ref{fig:dwarfimages}.
-\jillianremark{ {\bf Put SFH and metal hist in Figure 4.
-Discuss.}}
+The structure and star formation of this galaxy has been extensively studied by \citet{Christensen14b}.
+We also include a bulgeless dwarf galaxy, h516, which has a disk with irregularly distributions star formation, with a virial mass of $3.8 \times 10^{10}\msun$, stellar mass $2.5 \times 10^8 \msun$, and maximum circular velocity of 65 km s$^{-1}$.
+Images of these galaxies are shown in Figure \ref{fig:dwarfimages}, and we show their star formation history and metallitity evolution in  Figure \ref{fig:TwoDwarfGalaxies}.
+Note that these galaxies have quite different masses, and are not meant to be directly comparable.
+The more massive h603 has a much more active star formation history and an overall increasing metallicity with time, whereas the less massive h516 is characterized by small bursts of star formation and a fairly flat metallicity evolution.
 
@@
 
+\begin{figure*}
+\includegraphics[width=\columnwidth]{Figures/sfh_dwarf}
+\includegraphics[width=\columnwidth]{Figures/dwarf_zvst}
+\caption{\label{fig:TwoDwarfGalaxies}\textbf{Star formation and metallicity versus time}:  \emph{Left panel}: Star formation history $\dot{M}_{*}$
+  versus time.  Black corresponds to h603 and red to h516.  
+\emph{Right panel}: A plot of the  metallicity $Z$ of recently-formed stars versus time.  Solid red and black lines show
+the mean metallicity; dotted lines correspond to  90\% of newly-born stars have lower metallicity,   or 10\% of
+newly-born stars have greater metallicity.  %When these two galaxies are $2-3\unit{Gyr}$ old, prior to the first major
+%merger of  near the peak of their
+%star-forming history, newly-born stars are created with significantly different metallicity.  Additionally, prior to the
+%second major merger of galaxy B at $\simeq 6\unit{Gyr}$, stars form in the \ExcitingGalaxy{} galaxy at a systematically lower
+%metallicity than in the \BoringGalaxy{} counterpart.
+}
+\end{figure*}
+
 \section{Detection-weighted compact binary formation}
@@
 Our goal in this work is to estimate the \emph{ratio} of compact binaries that should be merging, at present, in the two
-simulated Milky-Way analog galaxies described above.
+simulated Milky-Way analog galaxies described above as well as the dwarfs.
 
@@
 
-Binary evolution calculations suggest the binary compact object formation rate rate depends sensitively on the assumed metallicity, in conjunction
+Binary evolution calculations suggest the binary compact object formation rate depends sensitively on the assumed metallicity, in conjunction
 with other parameters \citep[see,\,e.g.][and references
@@
 To characterize the frequency of different star-forming conditions, we use our cosmological simulations of Milky Way-like galaxies, which provide each galaxy's star formation rate
-$\dot{M}_*$ and metallicity distribution $p(\log Z|t)$ over time.
+$\dot{M}_*$ and metallicity distribution $p(\log Z|t)$ over time (see Eqn. \ref{eqn:rate}).
 
@@
 galaxies  can be calculated via
-\begin{eqnarray}
+\begin{eqnarray}\label{eqn:rate}
  r_D \propto  \int d\log Z  \int _{13 \unit{Gyr}}^0dt  V(Z) \lambda(Z) \frac{dP_t}{dt}(t) \dot{M}_* p(\log Z|t)
@@
 ($Z\simeq 0.8 \times10^{-3}$) compared
-to the \BoringGalaxy{} galaxy ($Z\simeq 2\times 10^{-3}$).  In this reigme, the formation efficiency $\lambda$ and sensitive volume $V$
+to the \BoringGalaxy{} galaxy ($Z\simeq 2\times 10^{-3}$).  In this regime, the formation efficiency $\lambda$ and sensitive volume $V$
 can depend sensitively on mass; for example, for binary black holes, the ratio of  $(\lambda V)_{\BoringGalaxy{}}/(\lambda
@@
 described above.   These calculations show just how dramatically different the compact binary populations of galaxies
-with similar present-day mass but different star formation histories could be.   In particular, dwarf galaxies have an
+with different present-day masses %but different star formation histories 
+could be.   In particular, dwarf galaxies have an
 exceptionally large fraction of low-metallicity star formation in their history \citep{Kirby13}.  The precise details of their chemical
@@
 \begin{centering}
-\begin{tabular}{|ll|l|}\hline
- \text{\BoringGalaxy} & \text{BHBH} & 0.012 \\
- \text{\ExcitingGalaxy} & \text{BHBH} & 0.0116 \\
- \text{\DwarfOne} & \text{BHBH} & 0.0207 \\
- \text{\DwarfTwo} & \text{BHBH} & 0.0524 \\
- \text{\BoringGalaxy} & \text{BHNS} & 0.000219 \\
- \text{\ExcitingGalaxy} & \text{BHNS} & 0.000264 \\
- \text{\DwarfOne} & \text{BHNS} & 0.000275 \\
- \text{\DwarfTwo} & \text{BHNS} & 0.000235 \\
- \text{\BoringGalaxy} & \text{NSNS} & 0.000206 \\
- \text{\ExcitingGalaxy} & \text{NSNS} & 0.000228 \\\hline
+\begin{tabular}{llllc}\hline
+\text{Simulation}  &  \text{BHBH} &  \text{BHNS}  & \text{NSNS} & M$_* (\msun)$\\
+\hline
+\hline
+ \text{\BoringGalaxy} & 0.012  &0.000219 & 0.000206 & $4.24 \times 10^{10}$ \\
+ \text{\ExcitingGalaxy}  & 0.0116 & 0.000264 &   0.000228 & $4.46 \times 10^{10}$ \\
+ \text{\DwarfOne} & 0.0207  & 0.000275 &  & $7.8 \times 10^9$ \\
+ \text{\DwarfTwo}  & 0.0524 & 0.000235  &  & $2.5 \times 10^8$ \\
+\hline
 \end{tabular}
@@
 \caption{\label{tab:Results}\textbf{Event rates per unit mass $r_D/M$, arbitrary units}, for the three different types of binaries
-  discussed.  
+  discussed, along with the stellar mass of each galaxy.  
 }
@@
 On the one hand, compact binaries are kicked by supernovae, moving substantially away from their birth position
-\cite{2013ApJ...776...18F,2014ARAA..52...43B}. 
-On the other hand, particularly during the epoch of galaxy formation, galaxies are well-mixed: stars and adjacent gas generally do not have similar chemical composition.
+\citep{2013ApJ...776...18F,2014ARAA..52...43B}. 
+On the other hand, particularly during the early epoch of galaxy formation, galaxies are well-mixed: stars and adjacent gas generally do not have similar chemical composition.
 These mixing effects have been previously recognized as an obstacle to interpreting transient event spectra.
 For
-example,   \cite{2010MNRAS.402.1523P} previously demonstrated that absorbing gas neighboring transient events (there, long GRBs)
+example,   \citet{2010MNRAS.402.1523P} previously demonstrated that absorbing gas neighboring transient events (there, long GRBs)
 would generally have high metallicity, even for low-metallicity progenitors.   
@@
 Fortunately,  with the advent of
-IFUs and position-resolved spectroscopy, observers can now probe the star formation history and metallicity of
-individual gas packets at different points in a galaxy.  
-These highly-detailed probes will be essential tools to develop a comprehensive model of the galaxy's merger and
-chemical evolution history.
+IFUs and position-resolved spectroscopy, observers can now probe the star formation history and metallicity of individual gas packets at different points in a galaxy.  
+These highly-detailed probes will be essential tools to develop a comprehensive model of the galaxy's merger and chemical evolution history.
+Obtaining the galaxy-wide evolutionary history can help us infer compact binary formation conditions by identifying the lowest-metallicity formation events using stellar archaeological techniques.
 
@@
   SN Ia \citep{2011MNRAS.412.1508M}; see, e.g., the review in  \cite{2014ARAA..52...43B}.
+\jillianremark{RICHARD THIS LAST PARAGRAPH IS STILL SUPER CONFUSE TO ME SORRY.
+I think you need to call me and tell me about this response function so I can reword into normalpeople language}
 %
@@
  We demonstrate that
-galaxies which appear similar at $z = 0$ but have differing merger histories will have substantially different
+galaxies which appear similar at $z = 0$ but have differing merger histories will have somewhat different
 detection-weighted compact binary
-coalescence rates rates.
+coalescence rates.
 
@@
 Milky-Way like galaxies is nearly identical, independent of their highly distinctive early-time formation histories.   
-This result comes as somewhat of a surprise. 
+This result perhaps comes as somewhat of a surprise, considering the early differences in stellar and chemical evolution.
 %% can vary by factors of several \jillianremark{ UPDATE} in otherwise
@@
 led to similar late-time populations, despite substantial differences early on.
+%
+Further investigation is critical to assess whether this similarity is retained for more generic galaxy assembly
+histories and binary formation models.
+\jillianremark{ new, important!}  Now that we have introduced this method as a proof-of-concept here, it can be applied to large volume simulations, such as Illustris, EAGLE, or Romulus, in order to examine large numbers of galaxies and thus obtain statistically significant results.
 

### 2016-07-13 paper/paper.tex
Updating results

@@
 coalescing black hole binaries have nearly uniform delay time distribution between $100\unit{Myr}$ and
-$13\unit{Gyr}$\editremark{checkme again - a little hacky}; that said,  our conclusions are not sensitive to this choice.
+$13\unit{Gyr}$; that said,  our conclusions are not sensitive to this choice.
 %
@@
   histories can easily produce factors of order unity difference in galaxies with otherwise indistinguishable
-  present-day properties.   \editremark{Do we have more examples?}
+  present-day properties.  \editremark{but: do more examples show dramatic differences, or comparable changes}
 
@@
 \hline
- \text{\BoringGalaxy} & 0.012  &0.000219 & 0.000206 & $4.24 \times 10^{10}$ \\
- \text{\ExcitingGalaxy}  & 0.0116 & 0.000264 &   0.000228 & $4.46 \times 10^{10}$ \\
- \text{\DwarfOne} & 0.0207  & 0.000275 &  & $7.8 \times 10^9$ \\
- \text{\DwarfTwo}  & 0.0524 & 0.000235  &  & $2.5 \times 10^8$ \\
+ \text{\BoringGalaxy} & 0.0224 & 0.000247 & 0.000206  & $4.24 \times 10^{10}$ \\
+ \text{\ExcitingGalaxy}  &0.0216 & 0.000297 & 0.000228 & $4.46 \times 10^{10}$ \\
+ \text{\DwarfOne} &  0.0381 & 0.000308 & 0.000441& $7.8 \times 10^9$ \\
+ \text{\DwarfTwo}  & 0.0949 & 0.000257 & 0.000884& $2.5 \times 10^8$ \\
+ \text{h239}  &  0.023 &X & 0.000268 & \\
+ \text{h285} &  0.0236 & X & 0.000241 & \\
 \hline
@@
 IFUs and position-resolved spectroscopy, observers can now probe the star formation history and metallicity of individual gas packets at different points in a galaxy.  
-These highly-detailed probes will be essential tools to develop a comprehensive model of the galaxy's merger and chemical evolution history.
-Obtaining the galaxy-wide evolutionary history can help us infer compact binary formation conditions by identifying the lowest-metallicity formation events using stellar archaeological techniques.
+These highly-detailed probes will be essential tools to develop a comprehensive model of the galaxy's merger and
+chemical evolution history.    Obtaining the galaxy-wide evolutionary history can help us infer compact binary formation
+conditions by identifying the lowest-metallicity formation events using stellar archaeological techniques.  
+These techniques have been applied with great success to other transient events. 
+For example, in several cases the metallicity of gas neighboring a long GRB (\citet{ 2008AJ....135.1136M};
+\citet{2010AJ....140.1557L}) has been directly measured.  % , short GRB (\editremark{XXX}), or SN has been directly measured.
+%
+The precise host offset can be compared to the distribution of light and star formation  \citep{2010ApJ...708....9F}.
+%
+Finally,  on a host-by-host basis, the delay time between birth and merger has been constrained for
+% long GRBs (\editremark{XXX}), 
+short GRBs \citep{2010ApJ...725.1202L}
+ and
+  SN Ia \citep{2011MNRAS.412.1508M}; see, e.g., the review in  \cite{2014ARAA..52...43B}.
 
@@
 %
-For example, in several cases the metallicity of gas neighboring a long GRB (\citet{ 2008AJ....135.1136M};
-\citet{2010AJ....140.1557L}) has been directly measured.  % , short GRB (\editremark{XXX}), or SN has been directly measured.
-%
-The precise host offset can be compared to the distribution of light and star formation  \citep{2010ApJ...708....9F}.
-%
-Finally,  on a host-by-host basis, the delay time between birth and merger has been constrained for
-% long GRBs (\editremark{XXX}), 
-short GRBs \citep{2010ApJ...725.1202L}
- and
-  SN Ia \citep{2011MNRAS.412.1508M}; see, e.g., the review in  \cite{2014ARAA..52...43B}.
-\jillianremark{RICHARD THIS LAST PARAGRAPH IS STILL SUPER CONFUSE TO ME SORRY.
-I think you need to call me and tell me about this response function so I can reword into normalpeople language}
+ %% \jillianremark{RICHARD THIS LAST PARAGRAPH IS STILL SUPER CONFUSE TO ME SORRY.  I think you need to call me and tell me about this response function so I can reword into normalpeople language}
 %
@@
 \begin{acknowledgements}
-ROS acknowledges support from NSF award AST-1412449, via subcontract from the University of Wisconsin-Milwaukee.
+ROS acknowledges support from NSF award AST-1412449, via subcontract from the University of Wisconsin-Milwaukee, and PHY-1505629.
 %

### 2016-07-13 python/analyze_me.sh

@@ -18,6 +18,14 @@ mkdir dwarf2; cd dwarf2
     ln -sf ${HERE}/mass_max_of_z.dat .
   python ${HERE}/sfr_to_rate_nobins_BBH.py --starmetal-file ~/PersonalJBArchive/Dwarf2/dwarf2.z0.1.starmetal.dat --type-bbh > my.log
    cd ..
+ mkdir h239; cd h239
+    ln -sf ${HERE}/mass_max_of_z.dat .
+  python ${HERE}/sfr_to_rate_nobins_BBH.py --starmetal-file ~/PersonalJBArchive/h239/z0.starmetal.dat --type-bbh > my.log
+ cd ..
+ mkdir h285; cd h285
+    ln -sf ${HERE}/mass_max_of_z.dat .
+  python ${HERE}/sfr_to_rate_nobins_BBH.py --starmetal-file ~/PersonalJBArchive/h285/z0.starmetal.dat --type-bbh > my.log
+ cd ..
 cd ..
 
 # BHNS
@@ -37,6 +45,14 @@ mkdir dwarf2; cd dwarf2
     ln -sf ${HERE}/mass_max_of_z.dat .
   python ${HERE}/sfr_to_rate_nobins_BBH.py --starmetal-file ~/PersonalJBArchive/Dwarf2/dwarf2.z0.1.starmetal.dat --type-bhns > my.log
    cd ..
+ mkdir h239; cd h239
+    ln -sf ${HERE}/mass_max_of_z.dat .
+  python ${HERE}/sfr_to_rate_nobins_BBH.py --starmetal-file ~/PersonalJBArchive/h239/z0.starmetal.dat --type-bhns > my.log
+ cd ..
+ mkdir h285; cd h285
+    ln -sf ${HERE}/mass_max_of_z.dat .
+  python ${HERE}/sfr_to_rate_nobins_BBH.py --starmetal-file ~/PersonalJBArchive/h285/z0.starmetal.dat --type-bhns > my.log
+ cd ..
 
 cd ..
 
@@ -50,4 +66,20 @@ do
   python ${HERE}/sfr_to_rate_nobins_BBH.py --starmetal-file ~/PersonalJBArchive/${my_type}-galaxy/z0.016.starmetal.dat  > my.log
   cd ..
 done
+mkdir dwarf1; cd dwarf1
+    ln -sf ${HERE}/mass_max_of_z.dat .
[…]

### 2016-07-13 paper/paper.tex
Text

@@
 \end{abstract}
+% DCC: 
+% arxiv:
+% DOI:
 
@@
 \abbrvPSgrb{}: for a star-forming parcel of mass $\Delta M$ the number of binaries born at time $0$ which
-are coalescing now is $\lambda \Delta M dP/dt$, where $\lambda$ is an overall efficiency per unit mass and $P(<t|Z)$ is
+are coalescing now is $\lambda \Delta M dP_t/dt$, where $\lambda$ is an overall efficiency per unit mass and $P_t(<t|Z)$ is
 a metallicity-dependent delay time distribution.\footnote{For simplicity, we assume the mass and delay time
@@
   histories can easily produce factors of order unity difference in galaxies with otherwise indistinguishable
-  present-day properties.  \editremark{but: do more examples show dramatic differences, or comparable changes}
+  present-day properties.  That said, two other Milky-Way-like  galaxies (h239 and h285) also show very
+  similar binary black hole coalescence rates $r_D/M$; see Table \ref{tab:Results} . \editremark{but: do more examples show dramatic differences, or comparable changes}
 
@@
 histories and binary formation models.
-\jillianremark{ new, important!}  Now that we have introduced this method as a proof-of-concept here, it can be applied to large volume simulations, such as Illustris, EAGLE, or Romulus, in order to examine large numbers of galaxies and thus obtain statistically significant results.
+Now that we have introduced this method as a proof-of-concept here, it can be applied to large volume simulations, such as Illustris, EAGLE, or Romulus, in order to examine large numbers of galaxies and thus obtain statistically significant results.
 

### 2016-07-13 paper/paper.tex
table 1 masses
new galaxy brief descriptions

@@
 
-\subsection{Two Milky-Way-like galaxies with distinct histories }
+\subsection{Milky-Way-like galaxies with distinct histories }
 
@@
 rates.  To investigate whether galaxy history affects the compact binary event
-rate, we have chosen two simulations which are morphologically similar at $z
+rate, we have chosen four simulations which are morphologically similar at $z
 = 0$ but differ strongly in their merger histories; see Figure \ref{fig:images}.
@@
 6.79 \times 10^{11} \msun$, stellar mass $M_* = 4.24 \times 10^{10}
-\msun$, and maximum circular velocity $v_{circ} = 235$ km s$^{-1}$.
+\msun$, and maximum circular velocity $v_{\rm circ} = 235$ km s$^{-1}$.
 
@@
   \times 10^{11} \msun$, stellar mass $M_* = 4.46 \times 10^{10}
-  \msun$, and maximum circular velocity $v_{circ} = 242$ km s$^{-1}$.  %\editremark{Might we want to show the images of these galaxies?}
+  \msun$, and maximum circular velocity $v_{\rm circ} = 242$ km s$^{-1}$.  %\editremark{Might we want to show the images of these galaxies?}
+
+We include two additional Milky Way simulations with similar $z = 0$ properties, which have evolutionary histories that fall in between the extremes of the two described above.
+The galaxy h239 has a total virial mass of $M_{vir} = 9.3 \times 10^{11}\msun$, stellar mass $M_* = 4.50 \times 10^{10}
+\msun$, and maximum circular velocity $v_{\rm circ} = \jillianremark{XXX}$ km s$^{-1}$.
+The galaxy h285 has a total virial mass of $M_{vir} = 8.82 \times 10^{11}\msun$, stellar mass $M_* = 4.56 \times 10^{10} \msun$, and maximum circular velocity $v_{\rm circ} = \jillianremark{XXX}$ km s$^{-1}$.
+These galaxies are described in detail in \jillianremark{\bf references}.
 
@@
  \text{\ExcitingGalaxy}  &0.0216 & 0.000297 & 0.000228 & $4.46 \times 10^{10}$ \\
+  \text{h239}  &  0.023 &X & 0.000268 & $4.50 \times 10^{10}$\\
+ \text{h285} &  0.0236 & X & 0.000241 & $4.56 \times 10^{10}$ \\
  \text{\DwarfOne} &  0.0381 & 0.000308 & 0.000441& $7.8 \times 10^9$ \\
  \text{\DwarfTwo}  & 0.0949 & 0.000257 & 0.000884& $2.5 \times 10^8$ \\
- \text{h239}  &  0.023 &X & 0.000268 & \\
- \text{h285} &  0.0236 & X & 0.000241 & \\
 \hline

### 2016-07-13 paper/paper.tex
paper: minor changes to intro to better suit new scope

@@
 CALIFA,CALIFA2}.  
+%
+However, unlike short GRBs and supernovae (SN), present-day compact  binary populations can depend sensitively on rare low metallicity
+star formation.
 % POINT: But is it useful?
-In this work, we demonstrate by concrete example that detailed analysis of individual galaxies can be essential to
-investigate key physical questions about the origin of compact binary mergers.
+In this work, we assess by concrete example the extent to which detailed analysis of individual galaxies' assembly histories will be essential in
+investigations key physical questions about the origin of compact binary mergers.
 
 This paper is organized as follows. 
-In \S \ref{sec:sims}, we describe detailed hydrodynamical simulations of  several galaxies, including two of Milky Way-mass and two dwarfs.
-Though the two Milky Way-like galaxies are morphologically similar at $z = 0$, we
+In \S \ref{sec:sims}, we describe detailed hydrodynamical simulations of  several galaxies, including four of Milky Way-mass and two dwarfs.
+Though the four Milky Way-like galaxies are morphologically similar at $z = 0$, we
 show that their star formation and chemical evolution history have subtle but important differences due to their
@@
   which looks remarkably similar to the Milky Way and to the other
-  simulation, h277.  Prior to the $z = 1$ merger, each of the two
+  simulation, h277.  Prior to the $z = 1$ merger, each of the four
   progenitor galaxies actually experiences its own additional major
@@
 \includegraphics[width=\columnwidth]{Figures/exciting}
-\caption{\label{fig:GalaxyImages}Synthetic SDSS $gri$ images of our two Milky Way-type galaxies, h277 (left) and h258 (right), created with \textsc{SUNRISE} \citep{Jonsson06}.
+\caption{\label{fig:GalaxyImages}Synthetic SDSS $gri$ images of two of our Milky Way-type galaxies, h277 (left) and h258 (right), created with \textsc{SUNRISE} \citep{Jonsson06}.
 \label{fig:images}
@@
 $4.3 M_\odot$ in low-metallicity environments.  Not least because the average chirp mass for BH-NS simply cannot vary
-dramatically, given the functional form of $\mc$, our results do not depend sensitively on the choice of black hole mass
+dramatically, given the functional form of $\mc$, our results for the BH-NS coalescence rate per unit galaxy mass do not depend sensitively on the choice of black hole mass
 distribution.  Finally, for binary black holes, we assume  comparable-mass binaries
@@
 % so the ratio should be a factor of about 7x higher due to this region.
-Therefore, because only a fraction of order $10\%$ \textbf{[checkme-JILLIAN?]} of all star formation occurs in this epoch, by this order of magnitude
+Therefore, because only a fraction of order $10\%$  of all star formation occurs in this epoch, by this order of magnitude
 argument, the overall number of
@@
   present-day properties.  That said, two other Milky-Way-like  galaxies (h239 and h285) also show very
-  similar binary black hole coalescence rates $r_D/M$; see Table \ref{tab:Results} . \editremark{but: do more examples show dramatic differences, or comparable changes}
+  similar binary black hole coalescence rates $r_D/M$; see Table \ref{tab:Results}. % \editremark{but: do more examples show dramatic differences, or comparable changes}
 
@@
  \text{\ExcitingGalaxy}  &0.0216 & 0.000297 & 0.000228 & $4.46 \times 10^{10}$ \\
-  \text{h239}  &  0.023 &X & 0.000268 & $4.50 \times 10^{10}$\\
- \text{h285} &  0.0236 & X & 0.000241 & $4.56 \times 10^{10}$ \\
+  \text{h239}  &  0.023 & 0.000354 & 0.000268 & $4.50 \times 10^{10}$\\
+ \text{h285} &  0.0236 & 0.000284 & 0.000241 & $4.56 \times 10^{10}$ \\ \hline
  \text{\DwarfOne} &  0.0381 & 0.000308 & 0.000441& $7.8 \times 10^9$ \\

### 2016-07-13 paper/paper.tex
refs
Commenting out blue text for galaxy circular velocities

@@
 The galaxy h239 has a total virial mass of $M_{vir} = 9.3 \times 10^{11}\msun$, stellar mass $M_* = 4.50 \times 10^{10}
-\msun$, and maximum circular velocity $v_{\rm circ} = \jillianremark{XXX}$ km s$^{-1}$.
-The galaxy h285 has a total virial mass of $M_{vir} = 8.82 \times 10^{11}\msun$, stellar mass $M_* = 4.56 \times 10^{10} \msun$, and maximum circular velocity $v_{\rm circ} = \jillianremark{XXX}$ km s$^{-1}$.
-These galaxies are described in detail in \jillianremark{\bf references}.
+\msun$.%, and maximum circular velocity $v_{\rm circ} = \jillianremark{XXX}$ km s$^{-1}$.  
+The galaxy h285 has a total virial mass of $M_{vir} = 8.82 \times 10^{11}\msun$, stellar mass $M_* = 4.56 \times 10^{10}
+\msun$.%, %and maximum circular velocity $v_{\rm circ} = \jillianremark{XXX}$ km s$^{-1}$.  
+These galaxies are also described \citet{Munshi13,Bellovary14}.
 

### 2016-07-13 paper/paper.tex
velocities

@@
 The galaxy h239 has a total virial mass of $M_{vir} = 9.3 \times 10^{11}\msun$, stellar mass $M_* = 4.50 \times 10^{10}
-\msun$.%, and maximum circular velocity $v_{\rm circ} = \jillianremark{XXX}$ km s$^{-1}$.  
-The galaxy h285 has a total virial mass of $M_{vir} = 8.82 \times 10^{11}\msun$, stellar mass $M_* = 4.56 \times 10^{10}
-\msun$.%, %and maximum circular velocity $v_{\rm circ} = \jillianremark{XXX}$ km s$^{-1}$.  
+\msun$, and maximum circular velocity $v_{\rm circ} = 250$ km s$^{-1}$.
+The galaxy h285 has a total virial mass of $M_{vir} = 8.82 \times 10^{11}\msun$, stellar mass $M_* = 4.56 \times 10^{10} \msun$, and maximum circular velocity $v_{\rm circ} = 248$ km s$^{-1}$.
 These galaxies are also described \citet{Munshi13,Bellovary14}.

### 2016-07-28 paper/mnras/paper.tex
add mnras stuff

--- 2016-07-13 paper/paper.tex
@@
 %        */bhmetals   : paper.tex, paper-shorter.tex
-\documentclass[nofootinbib,twocolumn,prd]{emulateapj}
+\documentclass[a4paper,fleqn,usenatbib]{mnras}
 \usepackage{hyperref}
@@
 \usepackage[normalem]{ulem}
+\bibliographystyle{mnras}
+\usepackage{natbib}
 %\usepackage{eps2pdf}
+
+%%% MNRAS stuff  %%%
+\usepackage{newtxtext,newtxmath}
+\usepackage[T1]{fontenc}
+\usepackage{ae,aecompl}
+\usepackage{amssymb}	% Extra maths symbols
 
@@
 
+%\begin{document}
+%\title{Details matter: Similar host galaxies can harbor different merging compact binary populations} 
+\title[Effects of galaxy properties on LIGO binaries]{The effects of host galaxy properties on merging compact binaries detectable by LIGO}
+%\author{R.\ O'Shaughnessy}
+%\affiliation{Center for Computational Relativity and Gravitation, Rochester Institute of Technology, Rochester, NY 14623, USA}
+%\email{oshaughn@mail.rit.edu}
+%\author{ J. Bellovary}
+%\affiliation{Department of Physics, Queensborough Community College, Bayside, NY 11364}
+%\email{jbellovary@qcc.cuny.edu}
+%\author{C. Christensen}
+%\affiliation{Department of Physics, Grinnell College, Grinnell, IA, 50112}
+%\author{ F. Governato}
+%\affiliation{Department of Astronomy, University of Washington, Seattle, WA 98195}
+%\author{ S. Shen}
+%\affiliation{Cambridge or maybe Oslo}
+
+\author[R. O'Shaughnessy et al.]{R. O'Shaughnessy,$^1$\thanks{E-mail: oshaughn@mail.rit.edu}
+J. M. Bellovary,$^2$ 
+C. R. Christensen,$^3$ 
+S. Shen,$^4$ 
+F. Governato,$^5$ 
+A. Brooks$^6$\\
+%
+%
+%% List of institutions
+$^1$Center for Computational Relativity and Gravitation, Rochester Institute of Technology, Rochester, NY 14623, USA  \\
+$^2$Department of Physics, Queensborough Community College, Bayside, NY 11364, USA\\
+$^3$Department of Physics, Grinnell College, Grinnell, IA, 50112, USA\\
+$^4$Cambridge or Oslo?\\
+$^5$Department of Astronomy, University of Washington, Seattle, WA 98195, USA\\
+$^6$Rutgers, New Jersey
+ }
+
+% These dates will be filled out by the publisher
+\date{Accepted XXX. Received YYY; in original form ZZZ}
+
+% Enter the current year, for the copyright statements etc.
+\pubyear{2016}
+
+% Don't change these lines
 \begin{document}
-%\title{Details matter: Similar host galaxies can harbor different merging compact binary populations} 
-\title{The effects of host galaxy properties on merging compact binaries detectable by LIGO}
-\author{R.\ O'Shaughnessy}
-\affiliation{Center for Computational Relativity and Gravitation, Rochester Institute of Technology, Rochester, NY 14623, USA}
-\email{oshaughn@mail.rit.edu}
-\author{ J. Bellovary}
-\affiliation{Department of Physics, Queensborough Community College, Bayside, NY 11364}
-\email{jbellovary@qcc.cuny.edu}
+\label{firstpage}
+\pagerange{\pageref{firstpage}--\pageref{lastpage}}
+\maketitle
+
+%\email{fabio@astro.washington.edu}
 \begin{abstract}
@@
 present-day appearance depend on the details of their assembly.
-%% demonstrate by example that galaxies with similar present-day appearance can host distinctly different
-%% compact binary populations \jillianremark{ UPDATE}.  As an example, we demonstrate how the coalescing binary black hole population can differ by
-%% factors of order  unity, and even binary neutron star populations differ by tens of percent.  
-%
 We also demonstrate by concrete example the extent to which dwarf galaxies overabundantly produce compact binary
@@
 We discuss the implications for transient multimessenger astronomy with compact binary sources.
-%\jillianremark{Add quantifiable stuff when we have it.}
-%% Present and future observations of  merging compact binaries can provide valuable constraints on their birthrate
-%%  and formation scenarios.  However, recent binary evolution simulations suggest the compact binary merger rate depends
-%% sensitively on the progentior's metallicity, to the extent that rare low-metallicity star formation during galaxy
-%% assembly can produce more detected compact binaries than typical star formation.    Additionally, galaxy formation
-%% simulations can reproduce present-day galaxies with notably different assembly and star formation histories, with
-%% corresponding different present-day merger rates.  
-%% % POINT 0: Gasoline + popsyn: real work was done
-%% Using existing simulations of the assembly,  chemical evolution, and compact-object formation rate of a single halo
-%% Milky Way-like galaxy with Gasoline, we construct present-day compact binary merger rates using a simple semianalytic
-%% compact binary formation model ($dP/dt \propto Z^\alpha/t $) motivated by detailed calculations in the literature. 
-%% % POINT 1: Observations
-%% %   - difficult to reconstruct f
-%% %   - local particle far away
-%% As expected, we show the present-day galactic state can be only weakly correlated with the dominant compact binary
-%% fomation rate: the galaxy could form in several ways, including epochs of low-metallicity star formation through major
-%% mergers; and present-day mergers rarely occur near gas with their progenitor metallicity, even when not kicked.  
-%% %  - but the galaxy 
-%% By contrast,  detailed studies which reconstruct the galaxy's star formation history and metallicity evolution could,
-%% when stacked, pinpoint the dominant formation process \editremark{need more than handwaving}.
-% POINT 2: Revised merger rates
-%% Averaging over the cosmological star formation history and galaxy mass-metallicity relation, we demonstrate low
-%% metallicity star formation can produce much of the detected population of short GRBs and nearly all gravitatational-wave
-%% sources. 
-%% % POINT 3: Challenge for observations
-%% Therefore,  though a potentially large fraction of binaries formed from low-metallicity gas,  their birth metallicity
-%% cannot be identified directly, even with spatially resolved observations. 
-%% %
-%% We discuss the extent to which observations can distinguish between different scenarios for  low-metallicity compact
-%% binary formation.
-%
-%\textbf{say something using GRBs in paragraph; perhaps mention relative bias in $p(M_g|GRB)$ relative to prior?}
-%% \textbf{say something about different SFR histories making present galaxies -- can do more if we can distinguish history
-%% of the galaxy}
 
 \end{abstract}
-% DCC: 
-% arxiv:
-% DOI:
 
-%% absolutely critical vs optional
-%
-% critical
-%  -write paper as is, minmal
-% optional
-%  - add dwarfs. They are important
-%  - add ems counterparts. They are important
-%  - discussion of multimessenger astro
+% Select between one and six entries from the list of approved keywords.
+% Don't make up new ones.
+\begin{keywords}
+keyword1 -- keyword2 -- keyword3
+\end{keywords}
 
-\maketitle
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-%\editremark{Jillian}: Add me but note conflict \cite{Somerville15}, etc or \cite{2015ARAA..53...51S}
-
-%\editremark{We will be very careful to specify how SFR and metallicity are measured, backtracking}
-
-%Add me: \cite{Kirby13}
-
-%Add me: \citet{Madau14}  % not necessary, we are not doing a synthetic universe
-
-%Add me: Hopkins et al  \cite{2016arXiv160508783L} (in context of similar model, building off my prior work)
+%%%%%%%%%%%%%%%%% BODY OF PAPER %%%%%%%%%%%%%%%%%%
 
@@
 The galaxy h285 has a total virial mass of $M_{vir} = 8.82 \times 10^{11}\msun$, stellar mass $M_* = 4.56 \times 10^{10} \msun$, and maximum circular velocity $v_{\rm circ} = 248$ km s$^{-1}$.
-These galaxies are also described \citet{Munshi13,Bellovary14}.
+These galaxies are also described in \citet{Munshi13,Bellovary14}.
 
@@
 \includegraphics[width=\columnwidth]{Figures/dwarf1}
-\includegraphics[width=\columnwidth]{Figures/dwarf1}
+\includegraphics[width=\columnwidth]{Figures/h516}
 \caption{\label{fig:GalaxyImages}Synthetic SDSS $gri$ images of our two lower-mass galaxies, h603 (left) and h516 (right - placeholder image, need image of h516), created with \textsc{SUNRISE} \citep{Jonsson06}.
@@
 
-\begin{widetext}
+%%%\begin{widetext}
 % POINT:  Model
@@
 
-\end{widetext}
+%%%\end{widetext}
 
@@
 
-\begin{acknowledgements}
+\section*{Acknowledgements}
 ROS acknowledges support from NSF award AST-1412449, via subcontract from the University of Wisconsin-Milwaukee, and PHY-1505629.
@@
 JB acknowledges generous support  from the Helen Gurley Brown Trust.
-
 A portion of this work was performed at the Aspen Center for Physics, which is supported by National Science Foundation grant PHY-1066293.
-\end{acknowledgements}
+%\end{acknowledgements}
 

### 2016-07-28 paper/mnras/paper.tex
british spellings

@@
 %\begin{document}
-%\title{Details matter: Similar host galaxies can harbor different merging compact binary populations} 
-\title[Effects of galaxy properties on LIGO binaries]{The effects of host galaxy properties on merging compact binaries detectable by LIGO}
+%\title{Details matter: Similar host galaxies can harbour different merging compact binary populations} 
+\title[Effects of host galaxy properties on LIGO binaries]{The effects of host galaxy properties on merging compact binaries detectable by LIGO}
 %\author{R.\ O'Shaughnessy}
@@
 \begin{keywords}
-keyword1 -- keyword2 -- keyword3
+black hole physics -- gravitational waves -- galaxies: evolution
 \end{keywords}
@@
 %One simulation we report here, h258,
-%involves the formation of a Milky Way-like disk galaxy whose
+%involves the formation of a Milky Way-like disc galaxy whose
 %progenitors undergo major mergers at $z = 2$ and $z = 0.8$.  This
@@
 We identify individual galaxies using the halo finder $AHF$
-\citep{Gill04,Knollmann09}, which identifies halos based on an
+\citep{Gill04,Knollmann09}, which identifies haloes based on an
 overdensity criterion for a flat universe \citep{Gross97}.
@@
 \citep{Munshi13}, halo properties \citep{Zolotov09,Zolotov10}, and
-disk structure \citep{Brooks11}.  It has a virial mass of $M_{vir} =
+disc structure \citep{Brooks11}.  It has a virial mass of $M_{vir} =
 6.79 \times 10^{11} \msun$, stellar mass $M_* = 4.24 \times 10^{10}
@@
   more active merger history.  At $z = 1$ there is a 1:1 merger event;
-  a gas disk rapidly reforms following the collision (see
-  \citet{Governato09}), resulting in a massive disk galaxy at $z = 0$
+  a gas disc rapidly reforms following the collision (see
+  \citet{Governato09}), resulting in a massive galaxy at $z = 0$
   which looks remarkably similar to the Milky Way and to the other
@@
 We have also employed the results of detailed simulations for two dwarf galaxies: \DwarfOne{} and \DwarfTwo{}.
-The simulation of h603 consists of a low-mass disk galaxy (qualitatively similar to M33).
+The simulation of h603 consists of a low-mass disc galaxy (qualitatively similar to M33).
 It has a virial mass of $3.4 \times 10^{11} \msun$, stellar mass of $7.8 \times 10^9 \msun$, and maximum circular velocity of 111 km s$^{-1}$.
 The structure and star formation of this galaxy has been extensively studied by \citet{Christensen14b}.
-We also include a bulgeless dwarf galaxy, h516, which has a disk with irregularly distributions star formation, with a virial mass of $3.8 \times 10^{10}\msun$, stellar mass $2.5 \times 10^8 \msun$, and maximum circular velocity of 65 km s$^{-1}$.
+We also include a bulgeless dwarf galaxy, h516, which has a disc with irregularly distributions star formation, with a virial mass of $3.8 \times 10^{10}\msun$, stellar mass $2.5 \times 10^8 \msun$, and maximum circular velocity of 65 km s$^{-1}$.
 Images of these galaxies are shown in Figure \ref{fig:dwarfimages}, and we show their star formation history and metallitity evolution in  Figure \ref{fig:TwoDwarfGalaxies}.
@@
 \includegraphics[width=\columnwidth]{Figures/h516}
-\caption{\label{fig:GalaxyImages}Synthetic SDSS $gri$ images of our two lower-mass galaxies, h603 (left) and h516 (right - placeholder image, need image of h516), created with \textsc{SUNRISE} \citep{Jonsson06}.
+\caption{\label{fig:GalaxyImages}Synthetic SDSS $gri$ images of our two lower-mass galaxies, h603 (left) and h516, created with \textsc{SUNRISE} \citep{Jonsson06}.
 \label{fig:dwarfimages}
@@
 
-To explore plausible binary detection scenarios, we adopt a parameterized formalism for binary evolution and event
+To explore plausible binary detection scenarios, we adopt a parametrized formalism for binary evolution and event
 detection in an individual galaxy, motivated by
@@
 For
-example,   \citet{2010MNRAS.402.1523P} previously demonstrated that absorbing gas neighboring transient events (there, long GRBs)
+example,   \citet{2010MNRAS.402.1523P} previously demonstrated that absorbing gas neighbouring transient events (there, long GRBs)
 would generally have high metallicity, even for low-metallicity progenitors.   
@@
 These techniques have been applied with great success to other transient events. 
-For example, in several cases the metallicity of gas neighboring a long GRB (\citet{ 2008AJ....135.1136M};
+For example, in several cases the metallicity of gas neighbouring a long GRB (\citet{ 2008AJ....135.1136M};
 \citet{2010AJ....140.1557L}) has been directly measured.  % , short GRB (\editremark{XXX}), or SN has been directly measured.

### 2016-07-31 paper/mnras/paper.tex
brooks comments

@@
 $^3$Department of Physics, Grinnell College, Grinnell, IA, 50112, USA\\
-$^4$Cambridge or Oslo?\\
+$^4$Institute of Astronomy, University of Cambridge, Cambridge CB3 OHA, UK\\
 $^5$Department of Astronomy, University of Washington, Seattle, WA 98195, USA\\
-$^6$Rutgers, New Jersey
+$^6$Department of Physics and Astronomy, Rutgers University, Piscataway, New Jersey, 08854, USA
  }
@@
 % - existence proof by example .. not an attempt to solve the general problem we raise
-Cosmological simulations of galaxy formation can produce present-day galaxies with a large range assembly and star formation histories.
+Cosmological simulations of galaxy formation can produce present-day galaxies with a large range of assembly and star formation histories.
 A detailed study of the metallicity evolution and star formation history of such simulations can assist in predicting LIGO-detectable compact object binary mergers.
@@
 In this work, we assess by concrete example the extent to which detailed analysis of individual galaxies' assembly histories will be essential in
-investigations key physical questions about the origin of compact binary mergers.
+investigating key physical questions about the origin of compact binary mergers.
 
@@
 In \S \ref{sec:sims}, we describe detailed hydrodynamical simulations of  several galaxies, including four of Milky Way-mass and two dwarfs.
-Though the four Milky Way-like galaxies are morphologically similar at $z = 0$, we
+Though the four Milky Way-mass galaxies are morphologically similar at $z = 0$, we
 show that their star formation and chemical evolution history have subtle but important differences due to their
@@
 \citep{Stadel01,Wadsley04}.  These simulations allow us to analyze both
-spatially and temporally resolved star formation, and determine not
-only the metallicity history of compact object progenitors.%, but also their dynamical evolution.  
+spatially and temporally resolved star formation, and determine the metallicity history of compact object progenitors.%, but also their dynamical evolution.  
 %maybe move the below section to later and/or consolidate
@@
 including large-scale torques from cosmic structure.  Our cosmological parameters are $\Omega_0 = 0.24$, $\Omega_{\rm baryon} = 0.04$, $\Lambda = 0.76$, h = 0.73, $\sigma_8 = 0.77$ 
- \citep{WMAP3} and model the ionizing UV background
+ \citep{WMAP3} and we model the ionizing UV background
 with the prescription from \citet{Haardt96}.
@@
 probabilistically from gas particles which meet density ($n_{min} =
-0.1$ amu cm$^{-3}$) and temperature ($T_{max} = 10^3$ K) thresholds. If a gas
+0.1$ amu cm$^{-3}$) and temperature ($T_{max} = 10^3$ K) thresholds, though since star formation also depends on the H$_{\rm 2}$ content of a particle (see below) the densities are nearly always much higher than this threshold.
+If a gas
 particle meets these criteria, it has a likelihood of forming a star
 particle (representing a simple stellar population with a Kroupa IMF
-\citep{Kroupa}) which is given by
+\citep{Kroupa93}) which is given by
 
@@
 which we set to 1 Myr.
-A detailed study of different interstellar medium (ISM) models and the resulting star formation properties by \citet{Christensen14a} demonstrates that this model allows star formation to occur in dense clumps of gas, in regions that correspond best to star formation in observed galaxies.
+A detailed study of different ISM models and the resulting star formation properties by \citet{Christensen14a} demonstrates that this model allows star formation to occur in clumps of dense gas, comparable to giant molecular clouds.
 
@@
 allowed to cool for the duration of the blastwave, mimicking the
-snowplow phase of a supernova explosion.  Previous works have found
+adiabatic expansion phase of a supernova explosion.  Previous works have found
 that this set of parameters results in realistic galaxies which obey a
@@
 \citep{Brooks07}, % JB: removed Kirby citation
- the Tully-Fisher relation \citep{Governato09}, and
+ the Tully-Fisher relation \citep{Christensen16}, and
 the size-luminosity relation \citep{Brooks11}, as well as reproduce
 the detailed characteristics of bulgeless dwarf galaxies
-\citep{Governato10} and the Milky Way \citep{Guedes11}.
+\citep{Governato10,Governato12}, low-mass disk galaxies with bulges \citep{Christensen14b}, and the Milky Way \citep{Guedes11}.
 
@@
 In each simulation, we are focusing on the stars which make up the primary (i.e.
-most massive) galaxy at $z = 0$.%, which serves as the progenitor to our $z = 0$ Milky
+most massive) galaxy within the zoomed-in high resolution region at $z = 0$.%, which serves as the progenitor to our $z = 0$ Milky
 %Way-like galaxy.
@@
 rate, we have chosen four simulations which are morphologically similar at $z
-= 0$ but differ strongly in their merger histories; see Figure \ref{fig:images}.
+= 0$  (see Figure \ref{fig:images}) but differ strongly in their merger histories.
 
@@
 \citep{Loebman12,Loebman14,Kassin14}, baryon fraction
-\citep{Munshi13}, halo properties \citep{Zolotov09,Zolotov10}, and
-disc structure \citep{Brooks11}.  It has a virial mass of $M_{vir} =
+\citep{Munshi13}, and satellite properties \citep{Zolotov12,Brooks14}.  It has a virial mass of $M_{vir} =
 6.79 \times 10^{11} \msun$, stellar mass $M_* = 4.24 \times 10^{10}
@@
 The galaxy h285 has a total virial mass of $M_{vir} = 8.82 \times 10^{11}\msun$, stellar mass $M_* = 4.56 \times 10^{10} \msun$, and maximum circular velocity $v_{\rm circ} = 248$ km s$^{-1}$.
-These galaxies are also described in \citet{Munshi13,Bellovary14}.
+These galaxies are also described in \citet{Bellovary14,Sloane16}.
 
@@
 \begin{figure*}
-\includegraphics[width=\columnwidth]{Figures/boring}
-\includegraphics[width=\columnwidth]{Figures/exciting}
+\includegraphics[width=\columnwidth]{boring}
+\includegraphics[width=\columnwidth]{exciting}
 \caption{\label{fig:GalaxyImages}Synthetic SDSS $gri$ images of two of our Milky Way-type galaxies, h277 (left) and h258 (right), created with \textsc{SUNRISE} \citep{Jonsson06}.
@@
 \begin{figure*}
-\includegraphics[width=\columnwidth]{Figures/sfh}
-\includegraphics[width=\columnwidth]{Figures/zvst}
+\includegraphics[width=\columnwidth]{sfh}
+\includegraphics[width=\columnwidth]{zvst}
 \caption{\label{fig:TwoGalaxies}\textbf{Star formation and metallicity versus time}:  \emph{Left panel}: Star formation history $\dot{M}_{*}$
@@
 \emph{Right panel}: A plot of the  metallicity $Z$ of recently-formed stars versus time.  Solid red and black lines show
-the mean metallicity; dotted lines correspond to  90\% of newly-born stars have lower metallicity,   or 10\% of
-newly-born stars have greater metallicity.  When these two galaxies are $2-3\unit{Gyr}$ old, prior to the first major
-merger of  near the peak of their
-star-forming history, newly-born stars are created with significantly different metallicity.  Additionally, prior to the
-second major merger of galaxy B at $\simeq 6\unit{Gyr}$, stars form in the \ExcitingGalaxy{} galaxy at a systematically lower
+the mean metallicity; dotted lines correspond to  90\% of newly-born stars with lower metallicity,   or 10\% of
+newly-born stars with greater metallicity.  When these two galaxies are $2-3\unit{Gyr}$ old, prior to the first major
+merger, newly-born stars are created with significantly different metallicity.  Additionally, prior to the
+second major merger of h258 at $\simeq 6\unit{Gyr}$, stars form in the \ExcitingGalaxy{} galaxy at a systematically lower
 metallicity than in the \BoringGalaxy{} counterpart.
@@
 The structure and star formation of this galaxy has been extensively studied by \citet{Christensen14b}.
-We also include a bulgeless dwarf galaxy, h516, which has a disc with irregularly distributions star formation, with a virial mass of $3.8 \times 10^{10}\msun$, stellar mass $2.5 \times 10^8 \msun$, and maximum circular velocity of 65 km s$^{-1}$.
-Images of these galaxies are shown in Figure \ref{fig:dwarfimages}, and we show their star formation history and metallitity evolution in  Figure \ref{fig:TwoDwarfGalaxies}.
+We also include a bulgeless dwarf galaxy, h516, which has a disc with irregularly distributed star formation, with a virial mass of $3.8 \times 10^{10}\msun$, stellar mass $2.5 \times 10^8 \msun$, and maximum circular velocity of 65 km s$^{-1}$.
+Images of these galaxies are shown in Figure \ref{fig:dwarfimages}, and we show their star formation history and metallicity evolution in  Figure \ref{fig:TwoDwarfGalaxies}.
 Note that these galaxies have quite different masses, and are not meant to be directly comparable.
@@
 \begin{figure*}
-\includegraphics[width=\columnwidth]{Figures/dwarf1}
-\includegraphics[width=\columnwidth]{Figures/h516}
+\includegraphics[width=\columnwidth]{dwarf1}
+\includegraphics[width=\columnwidth]{h516}
 \caption{\label{fig:GalaxyImages}Synthetic SDSS $gri$ images of our two lower-mass galaxies, h603 (left) and h516, created with \textsc{SUNRISE} \citep{Jonsson06}.
@@
 \begin{figure*}
-\includegraphics[width=\columnwidth]{Figures/sfh_dwarf}
-\includegraphics[width=\columnwidth]{Figures/dwarf_zvst}
+\includegraphics[width=\columnwidth]{sfh_dwarf}
+\includegraphics[width=\columnwidth]{dwarf_zvst}
 \caption{\label{fig:TwoDwarfGalaxies}\textbf{Star formation and metallicity versus time}:  \emph{Left panel}: Star formation history $\dot{M}_{*}$
-  versus time.  Black corresponds to h603 and red to h516.  
+  versus time.  Red corresponds to h603 and black to h516.  
 \emph{Right panel}: A plot of the  metallicity $Z$ of recently-formed stars versus time.  Solid red and black lines show
-the mean metallicity; dotted lines correspond to  90\% of newly-born stars have lower metallicity,   or 10\% of
-newly-born stars have greater metallicity.  %When these two galaxies are $2-3\unit{Gyr}$ old, prior to the first major
+the mean metallicity; dotted lines correspond to  90\% of newly-born stars with lower metallicity,   or 10\% of
+newly-born stars with greater metallicity.  %When these two galaxies are $2-3\unit{Gyr}$ old, prior to the first major
 %merger of  near the peak of their
@@
 \end{eqnarray}
-\abbrvPSgrb{} and \abbrvPSellipticals{} show this distribution is reasonable approximations to compact binary delay
+\abbrvPSgrb{} and \abbrvPSellipticals{} show this distribution is a reasonable approximation to compact binary delay
 time distributions.\footnote{Simulations suggest the delay time distribution varies from model to model and with mass.
@@
 regardless of their detailed assembly histories.
-However, it is also possible that this close agreement is entirely a
-a numerical coincdence between the specific star formation rate and metallicities in these two galaxies.  The effects described here
+However, it is also possible that this close agreement is entirely a numerical coincidence between the specific star formation rate and metallicities in these two galaxies.  The effects described here
   are well within the scatter around the mass-metallicity relation.  Marginally different realizations of these
@@
 \end{centering}
-\caption{\label{tab:Results}\textbf{Event rates per unit mass $r_D/M$, arbitrary units}, for the three different types of binaries
-  discussed, along with the stellar mass of each galaxy.  
+\caption{\label{tab:Results}Event rates per unit mass $r_D/M$, arbitrary units, for the three different types of binaries discussed, along with the stellar mass of each galaxy.  
 }
@@
 \citep{2013ApJ...776...18F,2014ARAA..52...43B}. 
-On the other hand, particularly during the early epoch of galaxy formation, galaxies are well-mixed: stars and adjacent gas generally do not have similar chemical composition.
+On the other hand, particularly during the early epoch of galaxy formation, gas in galaxies is well-mixed: stars and adjacent gas generally do not have similar chemical composition.
 These mixing effects have been previously recognized as an obstacle to interpreting transient event spectra.

### 2016-08-02 paper/mnras/paper.tex
small changes

@@
 J. M. Bellovary,$^2$ 
-C. R. Christensen,$^3$ 
-S. Shen,$^4$ 
-F. Governato,$^5$ 
-A. Brooks$^6$\\
+A. Brooks$^3$
+C. R. Christensen,$^4$ 
+S. Shen,$^5$ 
+F. Governato,$^6$ \\
 %
@@
 $^2$Department of Physics, Queensborough Community College, Bayside, NY 11364, USA\\
-$^3$Department of Physics, Grinnell College, Grinnell, IA, 50112, USA\\
-$^4$Institute of Astronomy, University of Cambridge, Cambridge CB3 OHA, UK\\
-$^5$Department of Astronomy, University of Washington, Seattle, WA 98195, USA\\
-$^6$Department of Physics and Astronomy, Rutgers University, Piscataway, New Jersey, 08854, USA
+$^3$Department of Physics and Astronomy, Rutgers University, Piscataway, New Jersey, 08854, USA\\
+$^4$Department of Physics, Grinnell College, Grinnell, IA, 50112, USA\\
+$^5$Institute of Astronomy, University of Cambridge, Cambridge CB3 OHA, UK\\
+$^6$Department of Astronomy, University of Washington, Seattle, WA 98195, USA\\
  }
@@
   evolution of h258 and h277 also differ at early times.  Figure
-  \ref{fig:TwoGalaxies} shows the star formation history (left panel) and metallicity evolution (right panel) of h277 (black) and h258 (red).
-The star formation histories are quite different at early times, where h277 has larger bursts of star formation between 2-4 Gyr, but h258 has a large burst at $\sim 6$ Gyr during a major merger.
+  \ref{fig:TwoGalaxies} shows the star formation history (left panel) and metallicity evolution (right panel) of h277 (black) and h258 (red).\footnote{We choose not to show galaxies h239 and h285 in our figures, as they fall in between the values bracketed by h258 and h277 and add confusion to the plots.}  The star formation histories are quite different at early times, where h277 has larger bursts of star formation between 2-4 Gyr, but h258 has a large burst at $\sim 6$ Gyr during a major merger.
 The right panel shows the mean metallicity of
@@
   present-day observables.  However,  the population of binary black holes  depends sensitively on all low metallicity star formation
-  over cosmic time; as we show below, these small differences can have an observable impact at present.
+  over cosmic time.%; as we show below, these small differences can have an observable impact at present.
 
@@
 detection in an individual galaxy, motivated by
-the detailed studies of  \abbrvPSgrb{} (\cite{PSgrbs-popsyn}) and \abbrvPSellipticals{} (\cite{PSellipticals});  similar approaches have been used by
+the detailed studies of  \cite[][(hereafter \abbrvPSgrb{})]{PSgrbs-popsyn} and  \citet[][(hereafter \abbrvPSellipticals{})]{PSellipticals};  similar approaches have been used by
 \cite{2016arXiv160508783L} and others.
@@
 %\editremark{recheck numbers: we are tweaking things, and Zsun is seemingly inconsistent in the two approaches }
- Our two Milky Way-like galaxies have extremely similar star formation histories and metallicity evolution, particularly at late
+ Our four Milky Way-like galaxies have extremely similar star formation histories and metallicity evolution, particularly at late
  times.  
@@
 Using the concrete phenomenological calculations described above, we in fact find
-$(r_{D}/M)_{\BoringGalaxy{}}/(r_{D}/M)_{\ExcitingGalaxy{}}\simeq 0.9$.
+$(r_{D}/M)_{\BoringGalaxy{}}/(r_{D}/M)_{\ExcitingGalaxy{}}\simeq 0.9$.    \jillianremark{\bf RICHARD this is 0.1 in my calcuations}
 

### 2016-08-03 paper/mnras/paper.tex
last referee comments

@@
 J. M. Bellovary,$^2$ 
-A. Brooks$^3$
-C. R. Christensen,$^4$ 
-S. Shen,$^5$ 
-F. Governato,$^6$ \\
+A. Brooks,$^3$
+S. Shen,$^4$ 
+F. Governato,$^5$ 
+C. R. Christensen$^6$ \\
 %
@@
 $^3$Department of Physics and Astronomy, Rutgers University, Piscataway, New Jersey, 08854, USA\\
-$^4$Department of Physics, Grinnell College, Grinnell, IA, 50112, USA\\
-$^5$Institute of Astronomy, University of Cambridge, Cambridge CB3 OHA, UK\\
-$^6$Department of Astronomy, University of Washington, Seattle, WA 98195, USA\\
+$^4$Institute of Astronomy, University of Cambridge, Cambridge CB3 OHA, UK\\
+$^5$Department of Astronomy, University of Washington, Seattle, WA 98195, USA\\
+$^6$Department of Physics, Grinnell College, Grinnell, IA, 50112, USA\\
  }
@@
 In \S \ref{sec:sims}, we describe detailed hydrodynamical simulations of  several galaxies, including four of Milky Way-mass and two dwarfs.
-Though the four Milky Way-mass galaxies are morphologically similar at $z = 0$, we
-show that their star formation and chemical evolution history have subtle but important differences due to their
-distinctive merger histories.   To demonstrate
-these differences have a practical impact,  in \S \ref{sec:model}, we introduce a simple,
+Though the four Milky Way-like galaxies are morphologically similar at $z = 0$, their star formation and chemical evolution history have subtle differences due to their
+distinctive merger histories.   To demonstrate the practical impact of
+these differences as well as that of halo mass,  in \S \ref{sec:model}, we introduce a simple,
 metallicity-dependent  phenomenological model to calculate the present-day rate and mass distribution of compact binary
@@
 binary  coalescence rate
-dependence on the galaxy's assembly history.   
+dependence on each galaxy's assembly history and mass.   
 %% We also demonstrate that even the coalescence rates of binary neutron stars (NSNS) and black hole-neutron
@@
 with the prescription from \citet{Haardt96}.
-Our interstellar medium (ISM) model includes the non-equilibrium formation and destruction of H$_2$, which is incorporated in the cooling model along with metal lines \citep{Christensen12}.
+Our interstellar medium (ISM) model includes the non-equilibrium formation and destruction of H$_2$, which is incorporated in the cooling model along with metal lines, along with shielding of HI and H$_2$ \citep{Christensen12}.
 Stars form
@@
 
+We wish to point out that these simulations do not include the effects of supermassive black holes (SMBHs).
+These galaxies are at the mass where feedback from SMBH accretion is thought to affect star formation, and adding these effects may add additional scatter to the stellar and metal evolution of each galaxy, which could alter the binary black hole merger history as well.
+
 \begin{figure*}
@@
 the mean metallicity; dotted lines correspond to  90\% of newly-born stars with lower metallicity,   or 10\% of
-newly-born stars with greater metallicity.  When these two galaxies are $2-3\unit{Gyr}$ old, prior to the first major
+newly-born stars with greater metallicity.  The shaded region represents one standard deviation.  When these two galaxies are $2-3\unit{Gyr}$ old, prior to the first major
 merger, newly-born stars are created with significantly different metallicity.  Additionally, prior to the
 second major merger of h258 at $\simeq 6\unit{Gyr}$, stars form in the \ExcitingGalaxy{} galaxy at a systematically lower
-metallicity than in the \BoringGalaxy{} counterpart.
+metallicity than in the \BoringGalaxy{} counterpart.  Even from 8-13 Gyr, h258 has a slightly lower metallicity than h277.
 }
@@
 Note that these galaxies have quite different masses, and are not meant to be directly comparable.
-The more massive h603 has a much more active star formation history and an overall increasing metallicity with time, whereas the less massive h516 is characterized by small bursts of star formation and a fairly flat metallicity evolution.
+The more massive h603 has a much more active star formation history and an overall increasing metallicity with time, whereas the less massive h516 is characterized by small bursts of star formation and a fairly flat metallicity evolution, perhaps due to its substantial outflows.
 
@@
 the mean metallicity; dotted lines correspond to  90\% of newly-born stars with lower metallicity,   or 10\% of
-newly-born stars with greater metallicity.  %When these two galaxies are $2-3\unit{Gyr}$ old, prior to the first major
+newly-born stars with greater metallicity.  The shaded region represents one standard deviation.%When these two galaxies are $2-3\unit{Gyr}$ old, prior to the first major
 %merger of  near the peak of their
@@
 
-Our goal in this work is to estimate the \emph{ratio} of compact binaries that should be merging, at present, in the two
+Our goal in this work is to estimate the \emph{ratio} of compact binaries that should be merging, at present, in the four
 simulated Milky-Way analog galaxies described above as well as the dwarfs.
@@
 Using the concrete phenomenological calculations described above, we in fact find
-$(r_{D}/M)_{\BoringGalaxy{}}/(r_{D}/M)_{\ExcitingGalaxy{}}\simeq 0.9$.    \jillianremark{\bf RICHARD this is 0.1 in my calcuations}
+$(r_{D}/M)_{\BoringGalaxy{}}/(r_{D}/M)_{\ExcitingGalaxy{}}\simeq 0.9$.
 
@@
 regardless of their detailed assembly histories.
-However, it is also possible that this close agreement is entirely a numerical coincidence between the specific star formation rate and metallicities in these two galaxies.  The effects described here
+If low metallicity star formation makes up a small fraction of the total stellar mass, which is the case for each Milky Way-like galaxy we study here, then the quantity $V(Z) \lambda(Z) \dot{M}_* p(\log Z|t)$ must differ by about an order of magnitude for the binary black hole merger rates to differ strongly.
+Such a scenario is possible if we alter our conservative choice of the exponent $a$ in the $\lambda(Z)$ function, but nonetheless is rather unlikely that galaxies in this mass range will undergo drastically different early evolution.
+%However, it is also possible that this close agreement is entirely a numerical coincidence between the specific star formation rate and metallicities in these two galaxies.  
+The effects described here
   are well within the scatter around the mass-metallicity relation.  Marginally different realizations of these
   histories can easily produce factors of order unity difference in galaxies with otherwise indistinguishable
-  present-day properties.  That said, two other Milky-Way-like  galaxies (h239 and h285) also show very
-  similar binary black hole coalescence rates $r_D/M$; see Table \ref{tab:Results}. % \editremark{but: do more examples show dramatic differences, or comparable changes}
+  present-day properties.  %That said, two other Milky-Way-like  galaxies (h239 and h285) also show very
+ % similar binary black hole coalescence rates $r_D/M$; see Table \ref{tab:Results}. % \editremark{but: do more examples show dramatic differences, or comparable changes}
 
 More broadly, Table \ref{tab:Results} shows the results of our calculations for the three types of compact binaries
-described above.   These calculations show just how dramatically different the compact binary populations of galaxies
-with different present-day masses %but different star formation histories 
-could be.   In particular, dwarf galaxies have an
-exceptionally large fraction of low-metallicity star formation in their history \citep{Kirby13}.  The precise details of their chemical
+described above.   These calculations show just how dramatically {\em different} the compact binary populations of galaxies
+with different present-day {\em masses} %but different star formation histories 
+could be.   The dwarf galaxies have an
+exceptionally large fraction of low-metallicity star formation in their history \citep{Kirby13} relative to the more massive galaxies.  The precise details of their chemical
 evolution can modify their present-day binary black hole binary populations by factors of order a few, despite  adopting
 the conservative choices described above for the dependence of rate on metallicity.
+The progenitors and electromagnetic counterparts of future gravitational wave events are overall much more likely to be located in nearby dwarf galaxies with a large population of low metallicity stars.
 
@@
 histories and binary formation models.
-Now that we have introduced this method as a proof-of-concept here, it can be applied to large volume simulations, such as Illustris, EAGLE, or Romulus, in order to examine large numbers of galaxies and thus obtain statistically significant results.
+Now that we have introduced this method as a proof-of-concept here, it can be applied to large volume simulations, such as Illustris, EAGLE, or Romulus \citep{Illustris,EAGLE,Tremmel16}, in order to examine large numbers of galaxies and thus obtain statistically significant results.
 

### 2016-08-03 paper/mnras/paper.tex
Fix

@@
 evolution can modify their present-day binary black hole binary populations by factors of order a few, despite  adopting
-the conservative choices described above for the dependence of rate on metallicity.
-The progenitors and electromagnetic counterparts of future gravitational wave events are overall much more likely to be located in nearby dwarf galaxies with a large population of low metallicity stars.
+the conservative choices described above for the dependence of rate on metallicity.  The progenitors (and, if present,
+electromagnetic counterparts) of future binary black hole gravitational wave events are overall much more likely to be located in nearby dwarf galaxies with a large population of low metallicity stars.
 

### 2016-08-29 paper/mnras/paper.tex
Updating

@@
 %%% MNRAS stuff  %%%
-\usepackage{newtxtext,newtxmath}
+%\usepackage{newtxtext,newtxmath}
 \usepackage[T1]{fontenc}
@@
 
-Also included in our simulations is a scheme for turbulent metal
-diffusion \citep{Shen10}.  Metals are created in supernova explosions
+Metals are created in supernova explosions
 and deposited directly to the gas within the blast radius.  Stellar
@@
 supernova, with metal yields derived from \citet{Weaver93} and
-\citet{Thielemann86} respectively.  From this point onwards metals
+\citet{Thielemann86} respectively. {\bf Richard:
+ We adopt a fiducial Salpeter IMF.   We do not
+ self-consistently evolve our population of compact binaries and metallicity: for simplicity and consistent with common
+ practice, our model for chemical evolution is derived from isolated stars.  
+ As described in ZZZ [PROBABLY NEED A PLOT], the  derived cosmological metal evolution and star formation rate history derived using this
+ procedure is broadly consistent with the cosmological star formation history and metallicity evolution of the universe.
+ In particular, our procedure in bulk is broadly consistent with previous work on star formation over cosmic time,
+ including  phenomenological models for cosmological
+ metal evolution and star formation history overall  \cite{2016MNRAS.461.3877D}; the mass-metallicity relationship; and
+ the mass-metallicity-SFR correlation
+ \cite{2010MNRAS.408.2115M,2016MNRAS.tmp.1187H} NEED MORE REPRESENTATIVE CITATIONS BESIDES THE ONE THE REFEREE WANTS.  Our procedure also yields scatter in metallicity between galaxies,
+ consistent with the observed dispersion in the mass-metallicity relation (ZZZ; Panter?) and observation of DLAs
+ \cite{2015MNRAS.452L..36D}; see YYY for comparison.
+}
+
+Also included in our simulations is a scheme for turbulent metal
+diffusion \citep{Shen10}.   Once created,  metals
 diffuse through the surrounding gas, according to 
@@
 tensor, and $C_{diff}$ is a dimensionless constant which we set to a conservative value of 0.03.  
+{\bf Combined with infall, this procedure produces a range of metallicities within each galaxy.  
+}
 
@@
 
+\subsection{Mass-metallicity-SFR relation}
+
+{\bf
+
+Simulations and observations suggest that galaxies only  exist with a relatively narrow range of possible masses,
+metallicities, and star formation rates; see, e.g., \citet{2010MNRAS.408.2115M,2016MNRAS.tmp.1187H}.   For example,  
+\cite{2016MNRAS.tmp.1187H} suggest a correlation beteween mass, metallicity, and star formation rate
+\begin{eqnarray}
+12+\log [O/H] = -0.14 log (SFR) + 0.37 log (M_*) + 4.82
+\end{eqnarray}
+In particular, taking this expression at face value, the star formation rate and metallicity are anticorrelated: a high
+star formation rate can occur only at low metallicity.  
+Figure XXXX shows the trajectories of our fiducial simulations' median $Z$ and star formation rate, using this
+diagnostic.  ARE THEY REASONABLE?
+
+}
+
 \section{Detection-weighted compact binary formation}
@@
 \cite{2016arXiv160508783L} and others.
+{\bf 
+Since prior population synthesis investigations  extend relatively smoothly to very metallicity, we do not introduce a
+distinct, special group of low-metallicity Population III stars.
+}
 
@@
 
+{\bf In our investigation, we have neglected the impact of population III stars.
+Previous studies suggest the first generation of stars may contribute a small but nonzero fraction of detectable events,
+potentially with distinctively high black hole masses
+\cite{2016MNRAS.460L..74H,2016PhRvL.117f1101S,2014MNRAS.442.2963K}.  
+% http://adsabs.harvard.edu/abs/2004ApJ...612..597W
+}
+
 In short, in this work we have demonstrated that  the confounding effects of host galaxy assembly history can in the

### 2016-08-29 paper/paper.tex
paper
paper.tex: add reminder with DCC number
add Fabio Governato to author list
add author
add Sijing
Updating

@@
 \email{jbellovary@qcc.cuny.edu}
+\author{C. Christensen}
+\affiliation{Department of Physics, Grinnell College, Grinnell, IA, 50112}
+\author{ F. Governato}
+\affiliation{Department of Astronomy, University of Washington, Seattle, WA 98195}
+\author{ S. Shen}
+\affiliation{Cambridge or maybe Oslo}
+
+%\email{fabio@astro.washington.edu}
 \begin{abstract}
@@
 \end{abstract}
-% DCC: 
+% DCC:   P1600229
 % arxiv:
@@
 supernova, with metal yields derived from \citet{Weaver93} and
-\citet{Thielemann86} respectively.  From this point onwards metals
+\citet{Thielemann86} respectively.  {\bf Richard:
+ We adopt a fiducial Salpeter IMF.  We do not introduce a special group of Population III stars (??).
+ As described in ZZZ, the  derived cosmological metal evolution and star formation rate history derived using this
+ procedure is broadly consistent with the cosmological star formation history and metallicity evolution of the universe.
+ In particular, our procedure is broadly consistent with one of the \cite{2016MNRAS.461.3877D} models
+}
+
+Also included in our simulations is a scheme for turbulent metal
+diffusion \citep{Shen10}.   Once created,  metals
 diffuse through the surrounding gas, according to 

### 2016-09-13 paper/mnras/paper.tex
updates

@@
 %%% MNRAS stuff  %%%
-%\usepackage{newtxtext,newtxmath}
+\usepackage{newtxtext,newtxmath}
 \usepackage[T1]{fontenc}
@@
 including large-scale torques from cosmic structure.  Our cosmological parameters are $\Omega_0 = 0.24$, $\Omega_{\rm baryon} = 0.04$, $\Lambda = 0.76$, h = 0.73, $\sigma_8 = 0.77$ 
- \citep{WMAP3} and we model the ionizing UV background
+ \citep{WMAP3}.
+\footnote{Since we are simulating individual galaxy environments rather than large populations of halos, the selection of cosmological parameters provides a negligible contribution to the variance in the overall evolutionary history of galaxies in our simulations.
+} We model the ionizing UV background
 with the prescription from \citet{Haardt96}.
@@
 number of observed relations such as the mass-metallicity relation
-\citep{Brooks07}, % JB: removed Kirby citation
+\citep{Brooks07,Christensen16}, % JB: removed Kirby citation
  the Tully-Fisher relation \citep{Christensen16}, and
@@
 stars more massive than 8 M$_\odot$ are able to undergo a Type II
-supernova.  We follow metal enrichment from both Type II and Type 1a
-supernova, with metal yields derived from \citet{Weaver93} and
-\citet{Thielemann86} respectively. {\bf Richard:
- We adopt a fiducial Salpeter IMF.   We do not
- self-consistently evolve our population of compact binaries and metallicity: for simplicity and consistent with common
- practice, our model for chemical evolution is derived from isolated stars.  
- As described in ZZZ [PROBABLY NEED A PLOT], the  derived cosmological metal evolution and star formation rate history derived using this
- procedure is broadly consistent with the cosmological star formation history and metallicity evolution of the universe.
- In particular, our procedure in bulk is broadly consistent with previous work on star formation over cosmic time,
- including  phenomenological models for cosmological
- metal evolution and star formation history overall  \cite{2016MNRAS.461.3877D}; the mass-metallicity relationship; and
- the mass-metallicity-SFR correlation
- \cite{2010MNRAS.408.2115M,2016MNRAS.tmp.1187H} NEED MORE REPRESENTATIVE CITATIONS BESIDES THE ONE THE REFEREE WANTS.  Our procedure also yields scatter in metallicity between galaxies,
- consistent with the observed dispersion in the mass-metallicity relation (ZZZ; Panter?) and observation of DLAs
- \cite{2015MNRAS.452L..36D}; see YYY for comparison.
-}
+supernova.  \jillianremark{  For Type II supernovae, iron and oxygen are produced according to the analytic fits used in \citet{Raiteri96} using the yields from \citet{Woosley95}:
+
+\begin{equation}
+M_{\rm Fe} = 2.802 \times 10^{-4} M_*^{1.864}
+\end{equation}
+\begin{equation}
+M_{\rm O} = 4.586 \times 10^{-4} M_*^{2.721}.
+\end{equation}
+
+Feedback from Type Ia supernovae also follows \citet{Raiteri96}.
+Each supernova produces $0.63\msun$ iron and $0.13 \msun$ oxygen \citet{Thielemann86}.
+Metal production from stellar winds is also included; we implement stellar wind feedback based on \citet{Kennicutt94} and the returned mass fraction is derived using a function by \citet{Weidemann87}.
+The returned gas has the same metallicity as the star particle.
+
+We do not include specific prescriptions for metal distribution based on initial metallicity (such as for Population III stars) or variations in IMF.  }
+
+%{\bf Richard:
+% We adopt a fiducial Salpeter IMF.   We do not
+% self-consistently evolve our population of compact binaries and metallicity: for simplicity and consistent with common
+% practice, our model for chemical evolution is derived from isolated stars.  
+% As described in ZZZ [PROBABLY NEED A PLOT], the  derived cosmological metal evolution and star formation rate history derived using this
+% procedure is broadly consistent with the cosmological star formation history and metallicity evolution of the universe.
+% In particular, our procedure in bulk is broadly consistent with previous work on star formation over cosmic time,
+% including  phenomenological models for cosmological
+% metal evolution and star formation history overall  \cite{2016MNRAS.461.3877D}; the mass-metallicity relationship; and
+% the mass-metallicity-SFR correlation
+% \cite{2010MNRAS.408.2115M,2016MNRAS.tmp.1187H} NEED MORE REPRESENTATIVE CITATIONS BESIDES THE ONE THE REFEREE WANTS.  Our procedure also yields scatter in metallicity between galaxies,
+% consistent with the observed dispersion in the mass-metallicity relation (ZZZ; Panter?) and observation of DLAs
+% \cite{2015MNRAS.452L..36D}; see YYY for comparison.
+%}
 

### 2016-09-14 paper/mnras/paper.tex
update

@@
 
-We do not include specific prescriptions for metal distribution based on initial metallicity (such as for Population III stars) or variations in IMF.  }
+We do not include specific prescriptions for metal distribution based on initial metallicity (such as for Population III stars) or variations in IMF.
+We cannot thus discuss Population III contributions to the gravitational wave background; however, studies by  \citet{Hartwig16}  and \citet{Dvorkin16} suggest that this contribution is fairly negligible.
+We have shown that our scheme for metal production and distribution produces galaxies which match the mass-metallicity relation at $z \sim 3$ \citep{Brooks07} as well as in the local universe \citep{Christensen16}.
+At higher redshifts, there is a very large spread in the metal distributions of damped Lyman alpha systems \citep{Dvorkin15}, suggesting that global galaxy metallicities depend on a wide range of parameter space.
+Recently \citet{Hunt16a,Hunt16b} has presented {\bf depictions} of the mass-metallicity-star formation rate fundamental plane, which demonstrates an evolutionary relationship between these quantities.
+{\bf we agree with the stuff}
+}
 

### 2016-09-14 paper/mnras/paper.tex
update

--- 2016-09-13 paper/mnras/paper.tex
@@
 stars more massive than 8 M$_\odot$ are able to undergo a Type II
-supernova.  \jillianremark{  For Type II supernovae, iron and oxygen are produced according to the analytic fits used in \citet{Raiteri96} using the yields from \citet{Woosley95}:
+supernova.    For Type II supernovae, iron and oxygen are produced according to the analytic fits used in \citet{Raiteri96} using the yields from \citet{Woosley95}:
 
@@
 The returned gas has the same metallicity as the star particle.
-
-We do not include specific prescriptions for metal distribution based on initial metallicity (such as for Population III stars) or variations in IMF.  }
 
@@
 tensor, and $C_{diff}$ is a dimensionless constant which we set to a conservative value of 0.03.  
-{\bf Combined with infall, this procedure produces a range of metallicities within each galaxy.  
-}
+Combined with infall, this procedure produces a range of metallicities within each galaxy.
+
+We do not include specific prescriptions for metal distribution based on initial metallicity (such as for Population III stars) or variations in IMF.
+We cannot thus discuss Population III contributions to the gravitational wave background; however, studies by  \citet{Hartwig16}  and \citet{Dvorkin16} suggest that this contribution is fairly negligible.
+We have shown that our scheme for metal production and distribution produces galaxies which match the mass-metallicity relation at $z \sim 3$ \citep{Brooks07} as well as in the local universe \citep{Christensen16}.
+At higher redshifts, there is a very large spread in the metal distributions of damped Lyman alpha systems \citep{Dvorkin15}; manifestly, other features in the galaxy evolutionary history play a role in its present day metallicity.
+Recently \citet{Hunt16a,Hunt16b} has demonstrated a relationship between of the mass, metallicity, and star formation rate, which demonstrates an evolutionary relationship between these quantities.
+As we will discuss in future work, we have verified that our evolutionary prescriptions are also qualitatively consistent with this relation.
 
@@
 
-\subsection{Mass-metallicity-SFR relation}
-
-{\bf
-
-Simulations and observations suggest that galaxies only  exist with a relatively narrow range of possible masses,
-metallicities, and star formation rates; see, e.g., \citet{2010MNRAS.408.2115M,2016MNRAS.tmp.1187H}.   For example,  
-\cite{2016MNRAS.tmp.1187H} suggest a correlation beteween mass, metallicity, and star formation rate
-\begin{eqnarray}
-12+\log [O/H] = -0.14 log (SFR) + 0.37 log (M_*) + 4.82
-\end{eqnarray}
-In particular, taking this expression at face value, the star formation rate and metallicity are anticorrelated: a high
-star formation rate can occur only at low metallicity.  
-Figure XXXX shows the trajectories of our fiducial simulations' median $Z$ and star formation rate, using this
-diagnostic.  ARE THEY REASONABLE?
-
-}
+%\subsection{Mass-metallicity-SFR relation}
+%
+%{\bf
+%
+%Simulations and observations suggest that galaxies only  exist with a relatively narrow range of possible masses,
+%metallicities, and star formation rates; see, e.g., \citet{2010MNRAS.408.2115M,2016MNRAS.tmp.1187H}.   For example,  
+%\cite{2016MNRAS.tmp.1187H} suggest a correlation beteween mass, metallicity, and star formation rate
+%\begin{eqnarray}
+%12+\log [O/H] = -0.14 log (SFR) + 0.37 log (M_*) + 4.82
+%\end{eqnarray}
+%In particular, taking this expression at face value, the star formation rate and metallicity are anticorrelated: a high
+%star formation rate can occur only at low metallicity.  
+%Figure XXXX shows the trajectories of our fiducial simulations' median $Z$ and star formation rate, using this
+%diagnostic.  ARE THEY REASONABLE?
+%
+%
+%}
 
@@
 the detailed studies of  \cite[][(hereafter \abbrvPSgrb{})]{PSgrbs-popsyn} and  \citet[][(hereafter \abbrvPSellipticals{})]{PSellipticals};  similar approaches have been used by
-\cite{2016arXiv160508783L} and others.
-{\bf 
-Since prior population synthesis investigations  extend relatively smoothly to very metallicity, we do not introduce a
+\cite{2016arXiv160508783L} and others.  Since prior population synthesis investigations  extend relatively smoothly to very metallicity, we do not introduce a
 distinct, special group of low-metallicity Population III stars.
-}
 
@@
 
-{\bf In our investigation, we have neglected the impact of population III stars.
+In our investigation, we have neglected the impact of population III stars.
 Previous studies suggest the first generation of stars may contribute a small but nonzero fraction of detectable events,
 potentially with distinctively high black hole masses
-\cite{2016MNRAS.460L..74H,2016PhRvL.117f1101S,2014MNRAS.442.2963K}.  
+\citep{2016MNRAS.460L..74H,2016PhRvL.117f1101S,2014MNRAS.442.2963K}.  
 % http://adsabs.harvard.edu/abs/2004ApJ...612..597W
-}
 
